---
title: "Parental social support in GUS"
output:
  html_document:
    toc: true
    toc_float: true
    keep_md: true
---

## Parental social support as a protective factor

Trajectories of SDQ with parental support to investigate whether parental social support could be protective.
  
"MdSNsp01" - Overall, how do you feel about the amount of support or help you get from friends or family living elsewhere?  
  1: I get enough help  
  2: I don't get enough help  
  3: I don't get any help  
  4: I don't need any help  

Coded as a binary variable of "Enough" vs "Not Enough". "Do not need help" is removed too.


```{r, setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, results = "asis")
library(here)
i_am("ANALYSIS/GUS/GUS_Social.Rmd")
source(here("FUNS", "packages.R"))
source(here("FUNS", "mods.R"))
source(here("FUNS", "plot.R"))
```

```{r read data}
dat = readRDS("G://users/eileen/Food_Ins/DATA/GUS_long_FS.rds")
```

# Full sample {.tabset}

```{r}
sdq = c("conduct" = "Dsdco1", "emot" = "Dsdem1","hyper"= "Dsdhy1","peer"= "Dsdpr1")
modtypes = c("conduct"="cubic","emot" ="cubic","hyper"= "linear","peer"= "quartic")

modfits = map2(sdq, modtypes, 
               \(x, y) fit_lmer(dat = dat, outcome = x, age = "age.cent",
                  id = "Idnumber", wt = dat$WTbth2, modType = y,
                  grp = "help_bin"))

modguide = data.frame("Outcome" = c("conduct", "emot", "hyper", "peer"))
fullsamp.fitstats = get_fitstats(modfits, modguide = modguide)
fullsamp.est = get_ests(modfits)
outcome = data.frame("Outcome" = c(rep("conduct", 8), rep("emot", 8), 
                                   rep("hyper", 4), rep("peer", 10)))
fullsamp.est = cbind(outcome, fullsamp.est) |> relocate(Outcome)
```

## Conduct

```{r results='asis'}
sjPlot::tab_model(modfits$conduct$fit)
print(modfits$conduct$diagnostics)

plotdat = plot_dfs(dat = dat, obj = modfits$conduct, sw = "sweep",
                   age_y = "Age")

emmeans.plot = traj_plot(plotdat, colour = "help_bin") + 
  xlab("Age") + ylab("SDQ Conduct")

emmeans.plot
```


## Emotional

```{r results='asis'}
sjPlot::tab_model(modfits$emot$fit)
print(modfits$emot$diagnostics)

plotdat = plot_dfs(dat = dat, obj = modfits$emot, sw = "sweep",
                   age_y = "Age")

emmeans.plot = traj_plot(plotdat, colour = "help_bin") + 
  xlab("Age") + ylab("SDQ Emotional")

emmeans.plot
```

## Hyperactivity

```{r results='asis'}
sjPlot::tab_model(modfits$hyper$fit)
print(modfits$hyper$diagnostics)

plotdat = plot_dfs(dat = dat, obj = modfits$hyper, sw = "sweep",
                   age_y = "Age")

emmeans.plot = traj_plot(plotdat, colour = "help_bin") + 
  xlab("Age") + ylab("SDQ Hyper")

emmeans.plot
```

## Peer Prob

```{r results='asis'}
sjPlot::tab_model(modfits$peer$fit)
print(modfits$peer$diagnostics)

plotdat = plot_dfs(dat = dat, obj = modfits$peer, sw = "sweep",
                   age_y = "Age")

emmeans.plot = traj_plot(plotdat, colour = "help_bin") + 
  xlab("Age") + ylab("SDQ Peer")

emmeans.plot
```

# Males {.tabset}

```{r}
dat.m = dat %>% filter(Sex == "M")
dat.m$age.cent = dat.m$Age - mean(dat.m$Age)

sdq = c("conduct" = "Dsdco1", "emot" = "Dsdem1","hyper"= "Dsdhy1","peer"= "Dsdpr1")
modtypes = c("conduct"="quartic","emot" ="cubic","hyper"= "linear","peer"= "cubic")

modfits = map2(sdq, modtypes, 
               \(x, y) fit_lmer(dat = dat.m, outcome = x, age = "age.cent",
                  id = "Idnumber", wt = dat.m$WTbth2, modType = y,
                  grp = "help_bin"))

modguide = data.frame("Outcome" = c("conduct", "emot", "hyper", "peer"))
m.fitstats = get_fitstats(modfits, modguide = modguide)
m.est = get_ests(modfits)
outcome = data.frame("Outcome" = c(rep("conduct", 10), rep("emot", 8), 
                                   rep("hyper", 4), rep("peer", 8)))
m.est = cbind(outcome, m.est) |> relocate(Outcome)
```

## Conduct

```{r results='asis'}
sjPlot::tab_model(modfits$conduct$fit)
print(modfits$conduct$diagnostics)

plotdat = plot_dfs(dat = dat.m, obj = modfits$conduct, sw = "sweep",
                   age_y = "Age")

emmeans.plot = traj_plot(plotdat, colour = "help_bin") + 
  xlab("Age") + ylab("SDQ Conduct")

emmeans.plot
```


## Emotional

```{r results='asis'}
sjPlot::tab_model(modfits$emot$fit)
print(modfits$emot$diagnostics)

plotdat = plot_dfs(dat = dat.m, obj = modfits$emot, sw = "sweep",
                   age_y = "Age")

emmeans.plot = traj_plot(plotdat, colour = "help_bin") + 
  xlab("Age") + ylab("SDQ Emotional")

emmeans.plot
```

## Hyperactivity

```{r results='asis'}
sjPlot::tab_model(modfits$hyper$fit)
print(modfits$hyper$diagnostics)

plotdat = plot_dfs(dat = dat.m, obj = modfits$hyper, sw = "sweep",
                   age_y = "Age")

emmeans.plot = traj_plot(plotdat, colour = "help_bin") + 
  xlab("Age") + ylab("SDQ Hyper")

emmeans.plot
```

## Peer Prob

```{r results='asis'}
sjPlot::tab_model(modfits$peer$fit)
print(modfits$peer$diagnostics)

plotdat = plot_dfs(dat = dat.m, obj = modfits$peer, sw = "sweep",
                   age_y = "Age")

emmeans.plot = traj_plot(plotdat, colour = "help_bin") + 
  xlab("Age") + ylab("SDQ Peer")

emmeans.plot
```


# Females {.tabset}

```{r}
dat.f = dat %>% filter(Sex == "F")
dat.f$age.cent = dat.f$Age - mean(dat.f$Age)

sdq = c("conduct" = "Dsdco1", "emot" = "Dsdem1","hyper"= "Dsdhy1","peer"= "Dsdpr1")
modtypes = c("conduct"="cubic","emot" ="quadratic","hyper"= "quadratic","peer"= "quartic")

modfits = map2(sdq, modtypes, 
               \(x, y) fit_lmer(dat = dat.f, outcome = x, age = "age.cent",
                  id = "Idnumber", wt = dat.f$WTbth2, modType = y,
                  grp = "help_bin"))

modguide = data.frame("Outcome" = c("conduct", "emot", "hyper", "peer"))
f.fitstats = get_fitstats(modfits, modguide = modguide)
f.est = get_ests(modfits)
outcome = data.frame("Outcome" = c(rep("conduct", 8), rep("emot", 6), 
                                   rep("hyper", 6), rep("peer", 10)))
f.est = cbind(outcome, f.est) |> relocate(Outcome)
```

## Conduct

```{r results='asis'}
sjPlot::tab_model(modfits$conduct$fit)
print(modfits$conduct$diagnostics)

plotdat = plot_dfs(dat = dat.f, obj = modfits$conduct, sw = "sweep",
                   age_y = "Age")

emmeans.plot = traj_plot(plotdat, colour = "help_bin") + 
  xlab("Age") + ylab("SDQ Conduct")

emmeans.plot
```


## Emotional

```{r results='asis'}
sjPlot::tab_model(modfits$emot$fit)
print(modfits$emot$diagnostics)

plotdat = plot_dfs(dat = dat.f, obj = modfits$emot, sw = "sweep",
                   age_y = "Age")

emmeans.plot = traj_plot(plotdat, colour = "help_bin") + 
  xlab("Age") + ylab("SDQ Emotional")

emmeans.plot
```

## Hyperactivity

```{r results='asis'}
sjPlot::tab_model(modfits$hyper$fit)
print(modfits$hyper$diagnostics)

plotdat = plot_dfs(dat = dat.f, obj = modfits$hyper, sw = "sweep",
                   age_y = "Age")

emmeans.plot = traj_plot(plotdat, colour = "help_bin") + 
  xlab("Age") + ylab("SDQ Hyper")

emmeans.plot
```

## Peer Prob

```{r results='asis'}
sjPlot::tab_model(modfits$peer$fit)
print(modfits$peer$diagnostics)

plotdat = plot_dfs(dat = dat.f, obj = modfits$peer, sw = "sweep",
                   age_y = "Age")

emmeans.plot = traj_plot(plotdat, colour = "help_bin") + 
  xlab("Age") + ylab("SDQ Peer")

emmeans.plot
```


# Save everything

```{r}
results.est = list("All" = fullsamp.est, "Male" = m.est, "Female" = f.est)
results.fitstats = list("All" = fullsamp.fitstats, "Male" = m.fitstats, "Female" = f.fitstats)

openxlsx::write.xlsx(results.est, here("OUTPUT/GUS", "Social_Estimates.xlsx"))
openxlsx::write.xlsx(results.fitstats, here("OUTPUT/GUS", "Social_FitStats.xlsx"))
```

