---
title: "GUS SDQ trajectories (age only)"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
editor_options: 
  chunk_output_type: inline
---

Identifying which polynomial terms to include in longitudinal models of SDQ domains for the whole sample and for males and females separately. This code fits 4 models for each SDQ domain and performs model comparisons to compare fit metrics e.g. AIC, BIC.\
   
Linear model: SDQ ~ age.cent + (1 + age.cent | ID)\
Quadratic model: SDQ ~ age.cent + age.cent^2 + (1 + age.cent | ID)\
Cubic model:  SDQ ~ age.cent + age.cent^2 + age.cent^3 + (1 + age.cent | ID)\
Quartic model:  SDQ ~ age.cent + age.cent^2 + age.cent^3 + age.cent^4 + (1 + age.cent | ID)\
  
Input data (dat) should be in long format, with the following variables (at minimum):\

- unique participant ID\
- identifier for each timepoint\
- age in years\
- mean-centred age (helpful for reducing convergence issues)\
- sex (could be sex at birth, could be gender identity - in this analysis it's a binary measure)\
- SDQ scores (conduct, emotional problems, hyperactivity, peer problems)\

Optionally, dat can include sample weights too.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
library(here)
i_am("ANALYSIS/GUS/GUS_Age_Only.Rmd")
source(here("FUNS", "packages.R"))
source(here("FUNS", "mods.R"))
source(here("FUNS", "plot.R"))
```

# Full sample {.tabset}

```{r read data, results='asis'}
dat = readRDS(here("DATA", "GUS_long.rds"))

dat = rename(dat, emot = Dsdem1, conduct = Dsdco1, hyper = Dsdhy1, peer = Dsdpr1, WTbth2 = WTbth2)

sumtable = dat %>% group_by(across(sweep)) %>%
          summarise(N = n(),
                    Age_M = m_sd(Age),
                    Age_Myrs = age_ym(mean(Age, na.rm = T)),
                    AgeRange = range_tab(Age, age = TRUE),
                    Conduct = m_sd(conduct),
                    Emot = m_sd(emot),
                    Hyper = m_sd(hyper),
                    Peer = m_sd(peer))

kbl(sumtable) %>%
  kable_styling(full_width = F)

modTypes = c("linear", "quadratic", "cubic", "quartic")
```

## Conduct problems

### Fit models

```{r}
conduct_fits = modTypes |> 
  map(\(x) fit_lmer(dat = dat, outcome ="conduct", age = "age.cent",
                  id = "Idnumber", wt = dat$WTbth2, modType = x)) |> `names<-`(modTypes)

fits = conduct_fits |> list_transpose(template = "fit")  |>  unlist()

deviance = get_fitstats(fitlist = conduct_fits, modguide = modTypes) |> pull(deviance)

conduct = do.call(anova, unname(fits)) |>  as.data.frame() |>  
  `rownames<-`(modTypes) |> cbind(deviance)

conduct |> kbl() |>  kable_styling(full_width = F)
```

### Plot model (Cubic)

```{r}
c.dat = get_preds(dat = dat, obj = conduct_fits$cubic, specs = "age.cent", age_y = "Age")

emmeans.plot = traj_plot(c.dat) + xlab("Age") + ylab("SDQ Conduct")
emmeans.plot
```

## Emotional problems

### Fit models

```{r}
emot_fits = modTypes |> 
  map(\(x) fit_lmer(dat = dat, outcome ="emot", age = "age.cent",
                  id = "Idnumber", wt = dat$WTbth2, modType = x)) |> `names<-`(modTypes)

fits = emot_fits |> list_transpose(template = "fit")  |>  unlist()

deviance = get_fitstats(fitlist = emot_fits, modguide = modTypes) |> pull(deviance)

emot = do.call(anova, unname(fits)) |>  as.data.frame() |>  
  `rownames<-`(modTypes) |> cbind(deviance)
emot |> kbl()  |>  kable_styling(full_width = F)
```

### Plot model (Cubic)

```{r}
e.dat = get_preds(dat = dat, obj = emot_fits$cubic, specs = "age.cent", age_y = "Age")

emmeans.plot = traj_plot(e.dat) + xlab("Age") + ylab("SDQ Emotional")
emmeans.plot
```


## Hyperactivity

### Fit models

```{r}
hyper_fits = modTypes |> 
  map(\(x) fit_lmer(dat = dat, outcome ="hyper", age = "age.cent",
                  id = "Idnumber", wt = dat$WTbth2, modType = x)) |> `names<-`(modTypes)

fits = hyper_fits |> list_transpose(template = "fit")  |>  unlist()

deviance = get_fitstats(fitlist = hyper_fits, modguide = modTypes) |> pull(deviance)

hyper = do.call(anova, unname(fits)) |>  as.data.frame() |>  
  `rownames<-`(modTypes) |> cbind(deviance)

hyper |> kbl()  |>  kable_styling(full_width = F)
```


### Plot model (Linear)

```{r}
h.dat = get_preds(dat = dat, obj = hyper_fits$linear, specs = "age.cent", age_y = "Age")

emmeans.plot = traj_plot(h.dat) + xlab("Age") + ylab("SDQ Hyperactivity")
emmeans.plot
```


## Peer problems

### Fit models

```{r}
peer_fits = modTypes |> 
  map(\(x) fit_lmer(dat = dat, outcome ="peer", age = "age.cent",
                  id = "Idnumber", wt = dat$WTbth2, modType = x)) |> `names<-`(modTypes)

fits = peer_fits |> list_transpose(template = "fit")  |>  unlist()

deviance = get_fitstats(fitlist = peer_fits, modguide = modTypes) |> pull(deviance)

peer = do.call(anova, unname(fits)) |>  as.data.frame() |>  
  `rownames<-`(modTypes) |> cbind(deviance)

peer |> kbl()  |>  kable_styling(full_width = F)
```

### Plot model (Quartic)

```{r}
p.dat = get_preds(dat = dat, obj = peer_fits$quartic, specs = "age.cent", age_y = "Age")

emmeans.plot = traj_plot(p.dat) + xlab("Age") + ylab("SDQ Peer")
emmeans.plot
```

```{r}
save(list = c("c.dat", "e.dat", "h.dat", "p.dat"), file = here("OUTPUT/GUS", "GUS_ageonly_plotdat.rda"))
modcomps = list("conduct" = conduct, "emot" = emot, "hyper" = hyper, "peer" = peer)
openxlsx::write.xlsx(modcomps, file = here("OUTPUT/GUS", "Age_Only_ModComps.xlsx"), row.names = TRUE)
```