---
title: "GUS_Diffs"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, results = "asis")
library(here)
i_am("ANALYSIS/GUS/GUS_FI.Rmd")
source(here("FUNS", "packages.R"))
```

Comparing group differences between the two highest responses to FI proxy question:\ 
"How much does the cost of food affect what you give ^childname to eat?"\ 
1. Not at all\
2. A little\
3. A fair amount\
4. A lot

```{r read data}
gus = readRDS(here("DATA", "GUS_long.rds"))
gus = rename(gus, emot = Dsdem1, conduct = Dsdco1, hyper = Dsdhy1, 
             peer = Dsdpr1, WTbth2 = WTbth2)

FItab = table(gus$sweep, gus$MeFaff04) |> as.matrix()
Agetab = gus |> group_by(across(sweep)) |> 
  summarise(N = n(), Age = age_ym(mean(Age, na.rm = T))) |> as.matrix()
cbind(Agetab, FItab) |> kbl() |> kable_styling(full_width = F)
```

# Compare SDQ scores in each sweep

## De {.tabset}

"A fair amount" and "A lot" differ in conduct problems only

```{r}
De = gus |> filter(sweep=="De")
De |> group_by(MeFaff04) |> 
  summarise(conduct = m_sd(conduct),
            emot = m_sd(emot),
            hyper = m_sd(hyper),
            peer = m_sd(peer)) |> kable()

test = list("conduct"=De$conduct, "emot"=De$emot, 
            "hyper"=De$hyper, "peer"=De$peer) |> 
  map(\(x) pairwise.wilcox.test(x, De$MeFaff04)$p.value) # differences in conduct
```

### Conduct problems

```{r results='asis'}
test[1] |> kable()
```

### Emotional problems

```{r results='asis'}
test[2] |> kable()
```

### Hyperactivity problems

```{r results='asis'}
test[3] |> kable()
```

### Peer problems

```{r results='asis'}
test[4] |> kable()
```

## Df {.tabset}

"A fair amount" and "A lot" differ in conduct problems only

```{r}
Df = gus |> filter(sweep=="Df")
Df |> group_by(MeFaff04) |> 
  summarise(conduct = m_sd(conduct),
            emot = m_sd(emot),
            hyper = m_sd(hyper),
            peer = m_sd(peer)) |> kbl() |> kable_styling()

test = list("conduct"=Df$conduct, "emot"=Df$emot, 
            "hyper"=Df$hyper, "peer"=Df$peer) |> 
  map(\(x) pairwise.wilcox.test(x, Df$MeFaff04)$p.value)
```

### Conduct problems

```{r results='asis'}
test[1] |> kable()
```

### Emotional problems

```{r results='asis'}
test[2] |> kable()
```

### Hyperactivity problems

```{r results='asis'}
test[3] |> kable()
```

### Peer problems

```{r results='asis'}
test[4] |> kable()
```

## Dg {.tabset}

"A fair amount" and "A lot" differ in conduct problems only

```{r}
Dg = gus |> filter(sweep=="Dg")
Dg |> group_by(MeFaff04) |> 
  summarise(conduct = m_sd(conduct),
            emot = m_sd(emot),
            hyper = m_sd(hyper),
            peer = m_sd(peer)) |> kbl() |> kable_styling()

test = list("conduct"=Dg$conduct, "emot"=Dg$emot, 
            "hyper"=Dg$hyper, "peer"=Dg$peer) |> 
  map(\(x) pairwise.wilcox.test(x, Dg$MeFaff04)$p.value)
```

### Conduct problems

```{r results='asis'}
test[1] |> kable()
```

### Emotional problems

```{r results='asis'}
test[2] |> kable()
```

### Hyperactivity problems

```{r results='asis'}
test[3] |> kable()
```

### Peer problems

```{r results='asis'}
test[4] |> kable()
```

## Dh {.tabset}

"A fair amount" and "A lot" don't differ

```{r}
Dh = gus |> filter(sweep=="Dh")
Dh |> group_by(MeFaff04) |> 
  summarise(conduct = m_sd(conduct),
            emot = m_sd(emot),
            hyper = m_sd(hyper),
            peer = m_sd(peer)) |> kbl() |> kable_styling()

test = list("conduct"=Dh$conduct, "emot"=Dh$emot, 
            "hyper"=Dh$hyper, "peer"=Dh$peer) |> 
  map(\(x) pairwise.wilcox.test(x, Dh$MeFaff04)$p.value)
```

### Conduct problems

```{r results='asis'}
test[1] |> kable()
```

### Emotional problems

```{r results='asis'}
test[2] |> kable()
```

### Hyperactivity problems

```{r results='asis'}
test[3] |> kable()
```

### Peer problems

```{r results='asis'}
test[4] |> kable()
```

## Di {.tabset}

"A fair amount" and "A lot" don't differ

```{r}
Di = gus |> filter(sweep=="Di")
Di |> group_by(MeFaff04) |> 
  summarise(conduct = m_sd(conduct),
            emot = m_sd(emot),
            hyper = m_sd(hyper),
            peer = m_sd(peer)) |> kbl() |> kable_styling()

test = list("conduct"=Di$conduct, "emot"=Di$emot, 
            "hyper"=Di$hyper, "peer"=Di$peer) |> 
  map(\(x) pairwise.wilcox.test(x, Di$MeFaff04)$p.value)
```

### Conduct problems

```{r results='asis'}
test[1] |> kable()
```

### Emotional problems

```{r results='asis'}
test[2] |> kable()
```

### Hyperactivity problems

```{r results='asis'}
test[3] |> kable()
```

### Peer problems

```{r results='asis'}
test[4] |> kable()
```

## Dj {.tabset}

"A fair amount" and "A lot" differ in hyperactivity

```{r}
Dj = gus |> filter(sweep=="Dj")
Dj |> group_by(MeFaff04) |> 
  summarise(conduct = m_sd(conduct),
            emot = m_sd(emot),
            hyper = m_sd(hyper),
            peer = m_sd(peer)) |> kbl() |> kable_styling()

test = list("conduct"=Dj$conduct, "emot"=Dj$emot, 
            "hyper"=Dj$hyper, "peer"=Dj$peer) |> 
  map(\(x) pairwise.wilcox.test(x, Dj$MeFaff04)$p.value)
```

### Conduct problems

```{r results='asis'}
test[1] |> kable()
```

### Emotional problems

```{r results='asis'}
test[2] |> kable()
```

### Hyperactivity problems

```{r results='asis'}
test[3] |> kable()
```

### Peer problems

```{r results='asis'}
test[4] |> kable()
```

## Compare covariates

Sex: 

```{r}
table(De$Sex, De$MeFaff04) |> kbl() |> kable_styling()
```

Income:

```{r}
table(De$DeEqv5, De$MeFaff04) |> kbl() |> kable_styling()
```


Maternal MH:

```{r}
De |> group_by(MeFaff04) |> 
  summarise(N = n(), SF12 = m_sd(DeSf12mn)) |> kbl() |> kable_styling()
```

SIMD (1 = least deprived):

```{r}
table(De$ALeSNim2, De$MeFaff04) |> kbl() |> kable_styling()
```

