---
title: "Weighted analyses of SDQ trajectories following FI"
output:
  html_document:
    toc: true
    toc_depth: 2
    code_folding: hide
---


```{r, setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, results = "asis")
library(here)
i_am("ANALYSIS/GUS/GUS_FI.Rmd")
source(here("FUNS", "packages.R"))
source(here("FUNS", "mods.R"))
source(here("FUNS", "plot.R"))
```


```{r read data}
dat = readRDS(here("DATA", "GUS_long.rds"))

# remove ordering of factors
dat = dat |> mutate(
  MeFaff3lvl = factor(MeFaff3lvl, ordered = FALSE) |> relevel(ref = "Not at all"),
  DeEqv5 = factor(DeEqv5, ordered = FALSE) |> relevel(ref = "Highest"),
  ALeSNim2 = factor(ALeSNim2, ordered = FALSE) |> relevel(ref = "1")
)


## setup for emmeans (emm_at)
#list of all categorical predictor levels to estimate. Maternal MH not included here as it's continuous and has a meaningful mean value so we can just get estimates for mean maternal MH score
emm_at = c(make_emm_at(age_y = dat$Age, agevar = "age.cent"), DeEqv5 = levels(dat$DeEqv5), sex = levels(dat$Sex), ALeSNim2 = levels(dat$ALeSNim2)) 

## setup for model covariates
# 4 covariate structures
covars = list(NULL, c("Sex", "DeEqv5"), c("Sex", "DeEqv5", "DeSf12mn"), c("Sex", "DeEqv5", "DeSf12mn", "ALeSNim2"))

plot.unadjusted = list()
plot.adjusted = list()
```

**Mean age: `r mean(dat$Age)` years**

# Conduct problems {.tabset}

```{r}
conductfits = covars |> 
  map(\(x) fit_lmer(dat = dat, outcome ="Dsdco1", age = "age.cent",
                  id = "Idnumber", wt = dat$WTbth2, modType = "cubic",
                  grp = "MeFaff3lvl", covs = x))
```

## No covariates

```{r results='asis'}
sj_tab(conductfits[[1]]$fit)
print(conductfits[[1]]$diagnostics)

c.preds = get_preds(dat = dat, obj = conductfits[[1]], age_y = "Age", 
                    emm_at = emm_at, specs = c("age.cent", "MeFaff3lvl"))

plot.unadjusted[["conduct"]] = traj_plot(c.preds, colour = "MeFaff3lvl") + 
  scale_x_continuous(breaks = seq(6, 18, 3)) + ylab("SDQ Conduct") +
  xlab("Age (years)")

plot.unadjusted[["conduct"]]
```

## Covariates sex and income 

```{r results='asis'}
sj_tab(conductfits[[2]]$fit)
print(conductfits[[2]]$diagnostics)
```

## Covariates sex, income, maternal MH

```{r results='asis'}
sj_tab(conductfits[[3]]$fit)
print(conductfits[[3]]$diagnostics)
```

## Covariates sex, income, maternal MH, SIMD

```{r results='asis'}
sj_tab(conductfits[[4]]$fit)
print(conductfits[[4]]$diagnostics)

c.adj = get_preds(dat = dat, obj = conductfits[[4]], age_y = "Age",
                specs = c("age.cent", "MeFaff3lvl"), emm_at = emm_at,
                weights = "proportional")

plot.adjusted[["conduct"]] = traj_plot(pred.df = c.adj, colour = "MeFaff3lvl") + 
  scale_x_continuous(breaks = seq(6, 18, 3)) + ylab("SDQ Conduct") +
  xlab("Age (years)")

plot.adjusted[["conduct"]]
```

# Emotional problems {.tabset}

```{r}
emotfits = covars |> 
  map(\(x) fit_lmer(dat = dat, outcome ="Dsdem1", age = "age.cent",
                  id = "Idnumber", wt = dat$WTbth2, modType = "cubic",
                  grp = "MeFaff3lvl", covs = x))
```

## No covariates 

```{r results='asis'}
sj_tab(emotfits[[1]]$fit)
print(emotfits[[1]]$diagnostics)

e.preds = get_preds(dat = dat, obj = emotfits[[1]], age_y = "Age", 
                    emm_at = emm_at, specs = c("age.cent", "MeFaff3lvl"))

plot.unadjusted[["emot"]] = traj_plot(e.preds, colour = "MeFaff3lvl") + 
  scale_x_continuous(breaks = seq(6, 18, 3)) + ylab("SDQ Emotional") +
  xlab("Age (years)")

plot.unadjusted[["emot"]]
```

## Covariates sex and income

```{r}
sj_tab(emotfits[[2]]$fit)
print(emotfits[[2]]$diagnostics)
```

## Covariates sex, income, maternal MH

```{r}
sj_tab(emotfits[[3]]$fit)
print(emotfits[[3]]$diagnostics)
```

## Covariates sex, income, maternal MH, SIMD

```{r results='asis'}
sj_tab(emotfits[[4]]$fit)
print(emotfits[[4]]$diagnostics)

e.adj = get_preds(dat = dat, obj = emotfits[[4]], age_y = "Age",
                specs = c("age.cent", "MeFaff3lvl"), emm_at = emm_at,
                weights = "proportional")

plot.adjusted[["emot"]] = traj_plot(pred.df = e.adj, colour = "MeFaff3lvl") + 
  scale_x_continuous(breaks = seq(6, 18, 3)) + ylab("SDQ Emotional") +
  xlab("Age (years)")

plot.adjusted[["emot"]]
```


# Hyperactivity {.tabset}

```{r}
hyperfits = covars |> 
  map(\(x) fit_lmer(dat = dat, outcome ="Dsdhy1", age = "age.cent",
                  id = "Idnumber", wt = dat$WTbth2, modType = "linear",
                  grp = "MeFaff3lvl", covs = x))
```

## No covariates 

```{r results='asis'}
sj_tab(hyperfits[[1]]$fit)
print(hyperfits[[1]]$diagnostics)

h.preds = get_preds(dat = dat, obj = hyperfits[[1]], age_y = "Age", 
                    emm_at = emm_at, specs = c("age.cent", "MeFaff3lvl"))

plot.unadjusted[["hyper"]] = traj_plot(h.preds, colour = "MeFaff3lvl") + 
  scale_x_continuous(breaks = seq(6, 18, 3)) + ylab("SDQ Hyperactivity") +
  xlab("Age (years)")

plot.unadjusted[["hyper"]]
```

## Covariates sex and income

```{r}
sj_tab(hyperfits[[2]]$fit)
print(hyperfits[[2]]$diagnostics)
```

## Covariates sex, income, maternal MH

```{r}
sj_tab(hyperfits[[3]]$fit)
print(hyperfits[[3]]$diagnostics)
```

## Covariates sex, income, maternal MH, SIMD

```{r results='asis'}
sj_tab(hyperfits[[4]]$fit)
print(hyperfits[[4]]$diagnostics)

h.adj = get_preds(dat = dat, obj = hyperfits[[4]], age_y = "Age",
                specs = c("age.cent", "MeFaff3lvl"), emm_at = emm_at,
                weights = "proportional")

plot.adjusted[["hyper"]] = traj_plot(pred.df = h.adj, colour = "MeFaff3lvl") + 
  scale_x_continuous(breaks = seq(6, 18, 3)) + ylab("SDQ Hyperactivity") +
  xlab("Age (years)")

plot.adjusted[["hyper"]]
```

# Peer Problems {.tabset}

```{r}
peerfits = covars |> 
  map(\(x) fit_lmer(dat = dat, outcome ="Dsdpr1", age = "age.cent",
                  id = "Idnumber", wt = dat$WTbth2, modType = "quartic",
                  grp = "MeFaff3lvl", covs = x))
```

## No covariates 

```{r results='asis'}
sj_tab(peerfits[[1]]$fit)
print(peerfits[[1]]$diagnostics)

p.preds = get_preds(dat = dat, obj = peerfits[[1]], age_y = "Age", 
                    emm_at = emm_at, specs = c("age.cent", "MeFaff3lvl"))

plot.unadjusted[["peer"]] = traj_plot(p.preds, colour = "MeFaff3lvl") + 
  scale_x_continuous(breaks = seq(6, 18, 3)) + ylab("SDQ Peer") +
  xlab("Age (years)")

plot.unadjusted[["peer"]]
```

## Covariates sex and income

```{r}
sj_tab(peerfits[[2]]$fit)
print(peerfits[[2]]$diagnostics)
```

## Covariates sex, income, maternal MH

```{r}
sj_tab(peerfits[[3]]$fit)
print(peerfits[[3]]$diagnostics)
```

## Covariates sex, income, maternal MH, SIMD

```{r results='asis'}
sj_tab(peerfits[[4]]$fit)
print(peerfits[[4]]$diagnostics)

p.adj = get_preds(dat = dat, obj = peerfits[[4]], age_y = "Age",
                specs = c("age.cent", "MeFaff3lvl"), emm_at = emm_at,
                weights = "proportional")

plot.adjusted[["peer"]] = traj_plot(pred.df = p.adj, colour = "MeFaff3lvl") + 
  scale_x_continuous(breaks = seq(6, 18, 3)) + ylab("SDQ Peer") +
  xlab("Age (years)")

plot.adjusted[["peer"]]
```


# Extract results dataframes

```{r}
# column with model covariates for renaming
modcovs = data.frame("covars" = covars |> map_chr(\(x) paste(x, collapse = "+")))

sdqmods = list("conduct" = conductfits, "emot" = emotfits, "hyper" = hyperfits, "peer" = peerfits)

results.fitstats = sdqmods |> 
  map(\(x) get_fitstats(fitlist = x, modguide = modcovs))
results.est = sdqmods |> 
  map(\(x) get_ests(x))

openxlsx::write.xlsx(results.est, here("OUTPUT/GUS", "FI_Estimates.xlsx"))
openxlsx::write.xlsx(results.fitstats, here("OUTPUT/GUS", "FI_FitStats.xlsx"))

save(list = c("c.preds", "e.preds", "h.preds", "p.preds"), file = here("OUTPUT/GUS", "GUS_plotdat.rda"))
save(list = c("c.adj", "e.adj", "h.adj", "p.adj"), file = here("OUTPUT/GUS", "GUS_plotdat_adjusted.rda"))
```

```{r}
lapply(results.fitstats, function(x) kable(x, digits= 3))
```


# Fit contrasts

```{r}
# fit contrasts for the fully-adjusted models only
contrmods = list("conduct" = conductfits[[4]], "emot" = emotfits[[4]], "hyper" = hyperfits[[4]], "peer" = peerfits[[4]])

# fit contrasts at age 5, 7, 9, 11, 13, 15
emm_at$age.cent = c(5, 7, 9, 11, 13, 15) - mean(dat$Age)

# get the emmeans output object - has predicted values but also some more stuff
emm.list = contrmods |> 
  map(\(x) get_emm(dat = dat, obj = x, emm_at = emm_at, age_y = "Age", 
                   specs = c("age.cent", "MeFaff3lvl"), weights = "proportional"))

# set contrast grid so that it's always more FI vs less FI
contrast_gus = list(
  "(A little) - Not at all" = c(-1, 1, 0),
  "(A lot/fair amount) - Not at all" = c(-1, 0, 1),
  "(A lot/fair amount) - A little" = c(0, -1, 1)
)

# run the contrasts bit
results.contr = emm.list |> 
  map(\(x) mod_contrasts(emm = x, simple = "MeFaff3lvl", age_m = mean(dat$Age), method = contrast_gus, adjust = "fdr"))

openxlsx::write.xlsx(results.contr, here("OUTPUT/GUS", "FI_Contrasts.xlsx"))

results.scores = emm.list |> 
  map(\(x) broom::tidy(x, conf.int = T)) |> 
  map(\(x) mutate(x, Age = age.cent + mean(dat$Age))) |> 
  map(\(x) relocate(x, Age))

openxlsx::write.xlsx(results.scores, here("OUTPUT/GUS", "FI_Scores.xlsx"))
```

```{r}
lapply(results.contr, function(x) kable(x, digits = 3))
```

```{r}
lapply(results.scores, function(x) kable(x, digits = 3))
```

