---
title: "Weighted analyses of SDQ trajectories following FI"
output:
  html_document:
    toc: true
    toc_float: true
    keep_md: true
---


```{r, setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, results = "asis")
library(here)
i_am("ANALYSIS/GUS/GUS_FI.Rmd")
source(here("FUNS", "packages.R"))
source(here("FUNS", "mods.R"))
source(here("FUNS", "plot.R"))
```


```{r read data}
dat = readRDS("G://users/eileen/Food_Ins/DATA/GUS_long_FS.rds")

## setup for emmeans (emm_at)
#list of all categorical predictor levels to estimate. Maternal MH not included here as it's continuous and has a meaningful mean value so we can just get estimates for mean maternal MH score
emm_at = c(make_emm_at(age_y = dat$Age, agevar = "age.cent"), DeEqv5 = levels(dat$DeEqv5), sex = levels(dat$Sex), ALeSNim2 = levels(dat$ALeSNim2)) 

## setup for model covariates
# 4 covariate structures
covars = list(NULL, c("Sex", "DeEqv5"), c("Sex", "DeEqv5", "DeSf12mn"), c("Sex", "DeEqv5", "DeSf12mn", "ALeSNim2"))
```

# Conduct problems {.tabset}

```{r}
conductfits = covars |> 
  map(\(x) fit_lmer(dat = dat, outcome ="Dsdco1", age = "age.cent",
                  id = "Idnumber", wt = dat$WTbth2, modType = "cubic",
                  grp = "MeFaff3lvl", covs = x))
```

## No covariates

```{r results='asis'}
sjPlot::tab_model(conductfits[[1]]$fit)
print(conductfits[[1]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = conductfits[[1]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)

conduct.plot = traj_plot(plotdat, colour = "MeFaff3lvl") + 
  xlab("Age (years)") + ylab("SDQ Conduct")

conduct.plot

c.pred = plotdat$pred.df
```

## Covariates sex and income 

```{r results='asis'}
sjPlot::tab_model(conductfits[[2]]$fit)
print(conductfits[[2]]$diagnostics)
```

## Covariates sex, income, maternal MH

```{r results='asis'}
sjPlot::tab_model(conductfits[[3]]$fit)
print(conductfits[[3]]$diagnostics)
```

## Covariates sex, income, maternal MH, SIMD {.tabset}

```{r results='asis'}
sjPlot::tab_model(conductfits[[4]]$fit)
print(conductfits[[4]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = conductfits[[4]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)

pred.low = list(raw.df = plotdat$raw.df, 
                pred.df = plotdat$pred.df |>
                  filter(ALeSNim2=="1"&DeEqv5=="1"))
pred.hi = list(raw.df = plotdat$raw.df, 
               pred.df = plotdat$pred.df |>
                 filter(ALeSNim2=="5"&DeEqv5=="5"))
```

### Lowest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.low, colour = "MeFaff3lvl") + 
  xlab("Age (years)") + ylab("SDQ Conduct")

emmeans.plot + facet_wrap(~Sex)
```

### Highest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.hi, colour = "MeFaff3lvl") + 
  xlab("Age (years)") + ylab("SDQ Conduct")

emmeans.plot + facet_wrap(~Sex)
```

# Emotional problems {.tabset}

```{r}
emotfits = covars |> 
  map(\(x) fit_lmer(dat = dat, outcome ="Dsdem1", age = "age.cent",
                  id = "Idnumber", wt = dat$WTbth2, modType = "cubic",
                  grp = "MeFaff3lvl", covs = x))
```

## No covariates 

```{r results='asis'}
sjPlot::tab_model(emotfits[[1]]$fit)
print(emotfits[[1]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = emotfits[[1]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)

emot.plot = traj_plot(plotdat, colour = "MeFaff3lvl") + 
  xlab("Age (years)") + ylab("SDQ Emotional")

emot.plot
e.pred = plotdat$pred.df
```

## Covariates sex and income

```{r}
sjPlot::tab_model(emotfits[[2]]$fit)
print(emotfits[[2]]$diagnostics)
```

## Covariates sex, income, maternal MH

```{r}
sjPlot::tab_model(emotfits[[3]]$fit)
print(emotfits[[3]]$diagnostics)
```

## Covariates sex, income, maternal MH, SIMD {.tabset}

```{r results='asis'}
sjPlot::tab_model(emotfits[[4]]$fit)
print(emotfits[[4]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = emotfits[[4]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)

pred.low = list(raw.df = plotdat$raw.df, 
                pred.df = plotdat$pred.df |>
                  filter(ALeSNim2=="1"&DeEqv5=="1"))
pred.hi = list(raw.df = plotdat$raw.df, 
               pred.df = plotdat$pred.df |>
                 filter(ALeSNim2=="5"&DeEqv5=="5"))
```

### Lowest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.low, colour = "MeFaff3lvl") + 
  xlab("Age (years)") + ylab("SDQ Emotional")

emmeans.plot + facet_wrap(~Sex)
```

### Highest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.hi, colour = "MeFaff3lvl") + 
  xlab("Age (years)") + ylab("SDQ Emotional")

emmeans.plot + facet_wrap(~Sex)
```

# Hyperactivity {.tabset}

```{r}
hyperfits = covars |> 
  map(\(x) fit_lmer(dat = dat, outcome ="Dsdhy1", age = "age.cent",
                  id = "Idnumber", wt = dat$WTbth2, modType = "linear",
                  grp = "MeFaff3lvl", covs = x))
```

## No covariates 

```{r results='asis'}
sjPlot::tab_model(hyperfits[[1]]$fit)
print(hyperfits[[1]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = hyperfits[[1]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)

hyper.plot = traj_plot(plotdat, colour = "MeFaff3lvl") + 
  xlab("Age (years)") + ylab("SDQ Hyperactivity")

hyper.plot
h.pred = plotdat$pred.df
```

## Covariates sex and income

```{r}
sjPlot::tab_model(hyperfits[[2]]$fit)
print(hyperfits[[2]]$diagnostics)
```

## Covariates sex, income, maternal MH

```{r}
sjPlot::tab_model(hyperfits[[3]]$fit)
print(hyperfits[[3]]$diagnostics)
```

## Covariates sex, income, maternal MH, SIMD {.tabset}

```{r results='asis'}
sjPlot::tab_model(hyperfits[[4]]$fit)
print(hyperfits[[4]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = hyperfits[[4]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)

pred.low = list(raw.df = plotdat$raw.df, 
                pred.df = plotdat$pred.df |>
                  filter(ALeSNim2=="1"&DeEqv5=="1"))
pred.hi = list(raw.df = plotdat$raw.df, 
               pred.df = plotdat$pred.df |>
                 filter(ALeSNim2=="5"&DeEqv5=="5"))
```

### Lowest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.low, colour = "MeFaff3lvl") + 
  xlab("Age (years)") + ylab("SDQ Hyperactivity")

emmeans.plot + facet_wrap(~Sex)
```

### Highest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.hi, colour = "MeFaff3lvl") + 
  xlab("Age (years)") + ylab("SDQ Hyperactivity")

emmeans.plot + facet_wrap(~Sex)
```

# Peer Problems {.tabset}

```{r}
peerfits = covars |> 
  map(\(x) fit_lmer(dat = dat, outcome ="Dsdpr1", age = "age.cent",
                  id = "Idnumber", wt = dat$WTbth2, modType = "quartic",
                  grp = "MeFaff3lvl", covs = x))
```

## No covariates 

```{r results='asis'}
sjPlot::tab_model(peerfits[[1]]$fit)
print(peerfits[[1]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = peerfits[[1]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)

peer.plot = traj_plot(plotdat, colour = "MeFaff3lvl") + 
  xlab("Age (years)") + ylab("SDQ Peer")

peer.plot
p.pred  = plotdat$pred.df
```

## Covariates sex and income

```{r}
sjPlot::tab_model(peerfits[[2]]$fit)
print(peerfits[[2]]$diagnostics)
```

## Covariates sex, income, maternal MH

```{r}
sjPlot::tab_model(peerfits[[3]]$fit)
print(peerfits[[3]]$diagnostics)
```

## Covariates sex, income, maternal MH, SIMD {.tabset}

```{r results='asis'}
sjPlot::tab_model(peerfits[[4]]$fit)
print(peerfits[[4]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = peerfits[[4]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)

pred.low = list(raw.df = plotdat$raw.df, 
                pred.df = plotdat$pred.df |>
                  filter(ALeSNim2=="1"&DeEqv5=="1"))
pred.hi = list(raw.df = plotdat$raw.df, 
               pred.df = plotdat$pred.df |>
                 filter(ALeSNim2=="5"&DeEqv5=="5"))
```

### Lowest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.low, colour = "MeFaff3lvl") + 
  xlab("Age (years)") + ylab("SDQ Peer")

emmeans.plot + facet_wrap(~Sex)
```

### Highest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.hi, colour = "MeFaff3lvl") + 
  xlab("Age (years)") + ylab("SDQ Peer")

emmeans.plot + facet_wrap(~Sex)
```


# Extract results dataframes

```{r}
# column with model covariates for renaming
modcovs = data.frame("covars" = covars |> map_chr(\(x) paste(x, collapse = "+")))

sdqmods = list("conduct" = conductfits, "emot" = emotfits, "hyper" = hyperfits, "peer" = peerfits)

results.fitstats = sdqmods |> 
  map(\(x) get_fitstats(fitlist = x, modguide = modcovs))
results.est = sdqmods |> 
  map(\(x) get_ests(x))

openxlsx::write.xlsx(results.est, here("OUTPUT/GUS", "FI_Estimates.xlsx"))
openxlsx::write.xlsx(results.fitstats, here("OUTPUT/GUS", "FI_FitStats.xlsx"))

save(list = c("c.pred", "e.pred", "h.pred", "p.pred"), file = here("OUTPUT/GUS", "GUS_plotdat.rda"))
```


# Fit contrasts

```{r}
# fit contrasts for the fully-adjusted models only
contrmods = list("conduct" = conductfits[[4]], "emot" = emotfits[[4]], "hyper" = hyperfits[[4]], "peer" = peerfits[[4]])

# fit contrasts at age 5, 7, 9, 11, 13, 16
emm_at$age.cent = c(5, 7, 9, 11, 13, 16) - mean(dat$Age)

# get the emmeans output object - has predicted values but also some more stuff
emm.list = contrmods |> 
  map(\(x) get_emm(dat = dat, obj = x, emm_at = emm_at))

# set contrast grid so that it's always more FI vs less FI
contrast_gus = list(
  "A little vs Not at all" = c(-1, 0, 1),
  "A lot/fair amount vs Not at all" = c(-1, 1, 0),
  "A lot/fair amount vs A little" = c(0, 1, -1)
)

# run the contrasts bit
results.contr = emm.list |> 
  map(\(x) mod_contrasts(emm = x, simple = "MeFaff3lvl", age_m = mean(dat$Age), emm_at = emm_at, c_grid = contrast_gus))

openxlsx::write.xlsx(results.contr, here("OUTPUT/GUS", "FI_Contrasts.xlsx"))
```

