---
title: "SDQ trajectories in GUS"
author: "Eileen Xu"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
```

```{r load packages}
library(lme4)
library(lmerTest)
library(tidyverse)
library(performance)
library(emmeans)
library(kableExtra)
emm_options(lmerTest.limit = 20000, pbkrtest.limit = 20000)
```

```{r}
# function to print any singular fit and convergence issues warning messages.
check_fit <- function(m) {
  msg = summary(m)$optinfo$conv$lme4$messages %>% unlist()
  if (any(grepl("isSingular", msg))==T) {
    print("Singular fit")
  } else {print("No singular fit")}
  
  if (any(grepl("failed to converge", msg))==T) {
    print("Failed to converge")
  } else  {print("No convergence issues")}
  } 
```

# Trajectories of SDQ scores in GUS - age only models

Longitiduinal models of SDQ in GUS - fitting models with different polynomial terms (quadratic, cubic etc) for each SDQ domain and running model comparisons to more formally decide on which model best fits the data. 

```{r read data, results='asis'}
dat = readRDS("G://users/eileen/Food_Ins/DATA/wt_GUS_long.rds")

sumtable = dat %>% group_by(across(sweep)) %>%
          summarise(N = n(),
                    age = mean(Age, na.rm = T),
                    ConductM = mean(Dsdco1, na.rm = T),
                    ConductSD = sd(Dsdco1, na.rm = T),
                    EmotM = mean(Dsdem1, na.rm = T),
                    EmotSD = sd(Dsdem1, na.rm = T),
                    HyperM = mean(Dsdhy1, na.rm=T),
                    HyperSD = sd(Dsdhy1, na.rm=T),
                    PeerM = mean(Dsdpr1, na.rm=T),
                    PeerSD = sd(Dsdpr1, na.rm=T)
          )

kbl(sumtable) %>%
  kable_styling(full_width = F)
```

# Full sample {.tabset}

## Conduct problems

In non-weighted analyses it's cubic, now with weights it's quadratic.

### Fit models

```{r}
linfit = lmer(Dsdco1 ~ age.cent + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))


quadfit = lmer(Dsdco1 ~ age.cent + I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))


cubfit = lmer(Dsdco1 ~ age.cent + I(age.cent^2) + I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quartfit = lmer(Dsdco1 ~ age.cent + I(age.cent^2) + I(age.cent^3) +I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
print("Linear model")
check_fit(linfit)
print("Quadratic model")
check_fit(quadfit)
print("Cubic model")
check_fit(cubfit)
print("Quartic model")
check_fit(quartfit)

anova(linfit, quadfit, cubfit, quartfit) %>% as.data.frame() %>% 
  kbl() %>% kable_styling(full_width = F)
```


### Plot model (Quadratic; Cubic model as dashed line)

```{r}
rm(linfit, quartfit)

#---------- make df of original data ----------
df.plot = dat %>%
  group_by(across(sweep)) %>%
  summarise(Age = mean(Age, na.rm = T),
            Phenotype = mean(Dsdco1, na.rm = T),
            SD = sd(Dsdco1, na.rm = T),
            n = sum(!is.na(Dsdco1))) %>%
  mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
         lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))

#---------- plot ---------------
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model

emm = emmeans(quadfit, specs = ~ age.cent + I(age.cent^2) , 
              at = list(age.cent = age_cent), 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#--- original cubic model ----
emm2 = emmeans(cubfit, specs = ~ age.cent + I(age.cent^2) + I(age.cent^3), 
              at = list(age.cent = age_cent), 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred2 = as.data.frame(summary(emm2)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean),
            linewidth = 1.5, na.rm = T, colour = "#0072B2") + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T, fill = "#0072B2") +
  geom_line(data = pred2,
            aes(x = age_vals, y = emmean),
            linewidth = 1, na.rm = T, colour = "black", linetype="dashed") +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Conduct")

emmeans.plot
```


## Emotional problems

### Fit models

```{r}
linfit = lmer(Dsdem1 ~ age.cent + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quadfit = lmer(Dsdem1 ~ age.cent + I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

cubfit = lmer(Dsdem1 ~ age.cent + I(age.cent^2) + I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quartfit = lmer(Dsdem1 ~ age.cent + I(age.cent^2) + I(age.cent^3) +I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

print("Linear model")
check_fit(linfit)
print("Quadratic model")
check_fit(quadfit)
print("Cubic model")
check_fit(cubfit)
print("Quartic model")
check_fit(quartfit)

anova(linfit, quadfit, cubfit, quartfit) %>% as.data.frame() %>% 
  kbl() %>% kable_styling(full_width = F)
```

### Plot model (Cubic)

```{r}
rm(linfit, quadfit, quartfit)

#---------- make df of original data ----------
df.plot = dat %>%
  group_by(across(sweep)) %>%
  summarise(Age = mean(Age, na.rm = T),
            Phenotype = mean(Dsdem1, na.rm = T),
            SD = sd(Dsdem1, na.rm = T),
            n = sum(!is.na(Dsdem1))) %>%
  mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
         lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))

#---------- plot ---------------
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model

emm = emmeans(cubfit, specs = ~ age.cent + I(age.cent^2) + I(age.cent^3), 
              at = list(age.cent = age_cent), 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean),
            linewidth = 1.5, na.rm = T, colour = "#0072B2") + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T, fill = "#0072B2") +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Emotional")

emmeans.plot
```

## Hyperactivity

### Fit models

```{r}
linfit = lmer(Dsdhy1 ~ age.cent + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quadfit = lmer(Dsdhy1 ~ age.cent + I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

cubfit = lmer(Dsdhy1 ~ age.cent + I(age.cent^2) + I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quartfit = lmer(Dsdhy1 ~ age.cent + I(age.cent^2) + I(age.cent^3) +I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

print("Linear model")
check_fit(linfit)
print("Quadratic model")
check_fit(quadfit)
print("Cubic model")
check_fit(cubfit)
print("Quartic model")
check_fit(quartfit)

anova(linfit, quadfit, cubfit, quartfit) %>% as.data.frame() %>% 
  kbl() %>% kable_styling(full_width = F)
```

### Plot model (Linear)


```{r}
rm(quadfit, cubfit, quartfit)
#---------- make df of original data ----------
df.plot = dat %>%
  group_by(across(sweep)) %>%
  summarise(Age = mean(Age, na.rm = T),
            Phenotype = mean(Dsdhy1, na.rm = T),
            SD = sd(Dsdhy1, na.rm = T),
            n = sum(!is.na(Dsdhy1))) %>%
  mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
         lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))

#---------- plot ---------------
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model

emm = emmeans(linfit, specs = ~ age.cent, 
              at = list(age.cent = age_cent), 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean),
            linewidth = 1.5, na.rm = T, colour = "#0072B2") + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T, fill = "#0072B2") +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Hyperactivity")

emmeans.plot
```

## Peer problems

### Fit models

```{r}
linfit = lmer(Dsdpr1 ~ age.cent + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quadfit = lmer(Dsdpr1 ~ age.cent + I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

cubfit = lmer(Dsdpr1 ~ age.cent + I(age.cent^2) + I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quartfit = lmer(Dsdpr1 ~ age.cent + I(age.cent^2) + I(age.cent^3) +I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
print("Linear model")
check_fit(linfit)
print("Quadratic model")
check_fit(quadfit)
print("Cubic model")
check_fit(cubfit)
print("Quartic model")
check_fit(quartfit)

anova(linfit, quadfit, cubfit, quartfit) %>% as.data.frame() %>% 
  kbl() %>% kable_styling(full_width = F)
```

### Plot model (Quartic)


```{r}
rm(linfit, quadfit, cubfit)
#---------- make df of original data ----------
df.plot = dat %>%
  group_by(across(sweep)) %>%
  summarise(Age = mean(Age, na.rm = T),
            Phenotype = mean(Dsdpr1, na.rm = T),
            SD = sd(Dsdpr1, na.rm = T),
            n = sum(!is.na(Dsdpr1))) %>%
  mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
         lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))

#---------- plot ---------------
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model

emm = emmeans(quartfit, specs = ~ age.cent + I(age.cent^2) + I(age.cent^3) + I(age.cent^4), 
              at = list(age.cent = age_cent), 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean),
            linewidth = 1.5, na.rm = T, colour = "#0072B2") + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T, fill = "#0072B2") +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Peer Problems")

emmeans.plot
```


# Male only {.tabset}

```{r subset male}
rm(list = names(which(!unlist(eapply(.GlobalEnv, 
    \(x) inherits(x, what = "function"))))))

dat = readRDS("G://users/eileen/Food_Ins/DATA/wt_GUS_long.rds")
dat = dat %>% filter(Sex == "M")
```

## Conduct problems

### Fit models

```{r}
linfit = lmer(Dsdco1 ~ age.cent + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quadfit = lmer(Dsdco1 ~ age.cent + I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

cubfit = lmer(Dsdco1 ~ age.cent + I(age.cent^2) + I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quartfit = lmer(Dsdco1 ~ age.cent + I(age.cent^2) + I(age.cent^3) +I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

print("Linear model")
check_fit(linfit)
print("Quadratic model")
check_fit(quadfit)
print("Cubic model")
check_fit(cubfit)
print("Quartic model")
check_fit(quartfit)
anova(linfit, quadfit, cubfit, quartfit) %>% as.data.frame() %>% 
  kbl() %>% kable_styling(full_width = F)
```

### Plot model (Quadratic)

```{r}
rm(linfit, cubfit, quartfit)
#---------- make df of original data ----------
df.plot = dat %>%
  group_by(across(sweep)) %>%
  summarise(Age = mean(Age, na.rm = T),
            Phenotype = mean(Dsdco1, na.rm = T),
            SD = sd(Dsdco1, na.rm = T),
            n = sum(!is.na(Dsdco1))) %>%
  mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
         lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))

#---------- plot ---------------
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model

emm = emmeans(quadfit, specs = ~ age.cent + I(age.cent^2), 
              at = list(age.cent = age_cent), 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean),
            linewidth = 1.5, na.rm = T, colour = "#0072B2") + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T, fill = "#0072B2") +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Conduct")

emmeans.plot
```


## Emotional problems

### Fit models

```{r}
linfit = lmer(Dsdem1 ~ age.cent + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quadfit = lmer(Dsdem1 ~ age.cent + I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

cubfit = lmer(Dsdem1 ~ age.cent + I(age.cent^2) + I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quartfit = lmer(Dsdem1 ~ age.cent + I(age.cent^2) + I(age.cent^3) +I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

print("Linear model")
check_fit(linfit)
print("Quadratic model")
check_fit(quadfit)
print("Cubic model")
check_fit(cubfit)
print("Quartic model")
check_fit(quartfit)

anova(linfit, quadfit, cubfit, quartfit) %>% as.data.frame() %>% 
  kbl() %>% kable_styling(full_width = F)

```

### Plot model (Cubic)


```{r}
rm(linfit, quadfit, quartfit)
#---------- make df of original data ----------
df.plot = dat %>%
  group_by(across(sweep)) %>%
  summarise(Age = mean(Age, na.rm = T),
            Phenotype = mean(Dsdem1, na.rm = T),
            SD = sd(Dsdem1, na.rm = T),
            n = sum(!is.na(Dsdem1))) %>%
  mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
         lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))

#---------- plot ---------------
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model

emm = emmeans(cubfit, specs = ~ age.cent + I(age.cent^2) + I(age.cent^3), 
              at = list(age.cent = age_cent), 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean),
            linewidth = 1.5, na.rm = T, colour = "#0072B2") + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T, fill = "#0072B2") +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Emotional")

emmeans.plot
```

## Hyperactivity

Quartic is suggested by LRT, but from BIC the linear model is better (and simpler) so we go with linear.

### Fit models

```{r}
linfit = lmer(Dsdhy1 ~ age.cent + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quadfit = lmer(Dsdhy1 ~ age.cent + I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

cubfit = lmer(Dsdhy1 ~ age.cent + I(age.cent^2) + I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quartfit = lmer(Dsdhy1 ~ age.cent + I(age.cent^2) + I(age.cent^3) +I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
print("Linear model")
check_fit(linfit)
print("Quadratic model")
check_fit(quadfit)
print("Cubic model")
check_fit(cubfit)
print("Quartic model")
check_fit(quartfit)

anova(linfit, quadfit, cubfit, quartfit) %>% as.data.frame() %>% 
  kbl() %>% kable_styling(full_width = F)

```

### Plot model (Linear)


```{r}
rm(cubfit, quadfit, quartfit)
#---------- make df of original data ----------
df.plot = dat %>%
  group_by(across(sweep)) %>%
  summarise(Age = mean(Age, na.rm = T),
            Phenotype = mean(Dsdhy1, na.rm = T),
            SD = sd(Dsdhy1, na.rm = T),
            n = sum(!is.na(Dsdhy1))) %>%
  mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
         lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))

#---------- plot ---------------
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model

emm = emmeans(linfit, specs = ~ age.cent, 
              at = list(age.cent = age_cent), 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean),
            linewidth = 1.5, na.rm = T, colour = "#0072B2") + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T, fill = "#0072B2") +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Hyperactivity")

emmeans.plot
```

## Peer problems

### Fit models

```{r}
linfit = lmer(Dsdpr1 ~ age.cent + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quadfit = lmer(Dsdpr1 ~ age.cent + I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

cubfit = lmer(Dsdpr1 ~ age.cent + I(age.cent^2) + I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quartfit = lmer(Dsdpr1 ~ age.cent + I(age.cent^2) + I(age.cent^3) +I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
print("Linear model")
check_fit(linfit)
print("Quadratic model")
check_fit(quadfit)
print("Cubic model")
check_fit(cubfit)
print("Quartic model")
check_fit(quartfit)

anova(linfit, quadfit, cubfit, quartfit) %>% as.data.frame() %>% 
  kbl() %>% kable_styling(full_width = F)
```

### Plot model (Cubic)

```{r}

rm(linfit, quadfit, quartfit)
#---------- make df of original data ----------
df.plot = dat %>%
  group_by(across(sweep)) %>%
  summarise(Age = mean(Age, na.rm = T),
            Phenotype = mean(Dsdpr1, na.rm = T),
            SD = sd(Dsdpr1, na.rm = T),
            n = sum(!is.na(Dsdpr1))) %>%
  mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
         lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))

#---------- plot ---------------
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model

emm = emmeans(cubfit, specs = ~ age.cent + I(age.cent^2) + I(age.cent^3), 
              at = list(age.cent = age_cent), 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean),
            linewidth = 1.5, na.rm = T, colour = "#0072B2") + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T, fill = "#0072B2") +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Peer Problems")

emmeans.plot
```

# Female only {.tabset}

```{r}
rm(list = names(which(!unlist(eapply(.GlobalEnv, 
    \(x) inherits(x, what = "function"))))))

dat = readRDS("G://users/eileen/Food_Ins/DATA/wt_GUS_long.rds")
dat = dat %>% filter(Sex == "F")
```


## Conduct problems

Weighted analyses suggest quadratic model instead of cubic.

### Fit models

```{r}
linfit = lmer(Dsdco1 ~ age.cent + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quadfit = lmer(Dsdco1 ~ age.cent + I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

cubfit = lmer(Dsdco1 ~ age.cent + I(age.cent^2) + I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quartfit = lmer(Dsdco1 ~ age.cent + I(age.cent^2) + I(age.cent^3) +I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
print("Linear model")
check_fit(linfit)
print("Quadratic model")
check_fit(quadfit)
print("Cubic model")
check_fit(cubfit)
print("Quartic model")
check_fit(quartfit)

anova(linfit, quadfit, cubfit, quartfit) %>% as.data.frame() %>% 
  kbl() %>% kable_styling(full_width = F)
```

### Plot model (Quadratic; Cubic model as dashed line)


```{r}
rm(linfit, quartfit)

#---------- make df of original data ----------
df.plot = dat %>%
  group_by(across(sweep)) %>%
  summarise(Age = mean(Age, na.rm = T),
            Phenotype = mean(Dsdco1, na.rm = T),
            SD = sd(Dsdco1, na.rm = T),
            n = sum(!is.na(Dsdco1))) %>%
  mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
         lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))

#---------- plot ---------------
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model

emm = emmeans(quadfit, specs = ~ age.cent + I(age.cent^2) , 
              at = list(age.cent = age_cent), 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#--- original cubic model ----
emm2 = emmeans(cubfit, specs = ~ age.cent + I(age.cent^2) + I(age.cent^3), 
              at = list(age.cent = age_cent), 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred2 = as.data.frame(summary(emm2)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean),
            linewidth = 1.5, na.rm = T, colour = "#0072B2") + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T, fill = "#0072B2") +
  geom_line(data = pred2,
            aes(x = age_vals, y = emmean),
            linewidth = 1, na.rm = T, colour = "black", linetype="dashed") +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Conduct")

emmeans.plot
```


## Emotional problems

### Fit models

```{r}
linfit = lmer(Dsdem1 ~ age.cent + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quadfit = lmer(Dsdem1 ~ age.cent + I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

cubfit = lmer(Dsdem1 ~ age.cent + I(age.cent^2) + I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quartfit = lmer(Dsdem1 ~ age.cent + I(age.cent^2) + I(age.cent^3) +I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
print("Linear model")
check_fit(linfit)
print("Quadratic model")
check_fit(quadfit)
print("Cubic model")
check_fit(cubfit)
print("Quartic model")
check_fit(quartfit)

anova(linfit, quadfit, cubfit, quartfit) %>% as.data.frame() %>% 
  kbl() %>% kable_styling(full_width = F)
```

### Plot model (Linear)


```{r}
rm(quadfit, cubfit, quartfit)
#---------- make df of original data ----------
df.plot = dat %>%
  group_by(across(sweep)) %>%
  summarise(Age = mean(Age, na.rm = T),
            Phenotype = mean(Dsdem1, na.rm = T),
            SD = sd(Dsdem1, na.rm = T),
            n = sum(!is.na(Dsdem1))) %>%
  mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
         lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))

#---------- plot ---------------
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model

emm = emmeans(linfit, specs = ~ age.cent, 
              at = list(age.cent = age_cent), 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean),
            linewidth = 1.5, na.rm = T, colour = "#0072B2") + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T, fill = "#0072B2") +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Emotional")

emmeans.plot
```

## Hyperactivity

### Fit models

```{r}
linfit = lmer(Dsdhy1 ~ age.cent + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quadfit = lmer(Dsdhy1 ~ age.cent + I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

cubfit = lmer(Dsdhy1 ~ age.cent + I(age.cent^2) + I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quartfit = lmer(Dsdhy1 ~ age.cent + I(age.cent^2) + I(age.cent^3) +I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
print("Linear model")
check_fit(linfit)
print("Quadratic model")
check_fit(quadfit)
print("Cubic model")
check_fit(cubfit)
print("Quartic model")
check_fit(quartfit)
anova(linfit, quadfit, cubfit, quartfit) %>% as.data.frame() %>% 
  kbl() %>% kable_styling(full_width = F)

```

### Plot model (Quadratic)


```{r}
rm(linfit, cubfit, quartfit)
#---------- make df of original data ----------
df.plot = dat %>%
  group_by(across(sweep)) %>%
  summarise(Age = mean(Age, na.rm = T),
            Phenotype = mean(Dsdhy1, na.rm = T),
            SD = sd(Dsdhy1, na.rm = T),
            n = sum(!is.na(Dsdhy1))) %>%
  mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
         lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))

#---------- plot ---------------
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model

emm = emmeans(quadfit, specs = ~ age.cent + I(age.cent^2), 
              at = list(age.cent = age_cent), 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean),
            linewidth = 1.5, na.rm = T, colour = "#0072B2") + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T, fill = "#0072B2") +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Hyperactivity")

emmeans.plot
```

## Peer problems

### Fit models

```{r}
linfit = lmer(Dsdpr1 ~ age.cent + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quadfit = lmer(Dsdpr1 ~ age.cent + I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

cubfit = lmer(Dsdpr1 ~ age.cent + I(age.cent^2) + I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quartfit = lmer(Dsdpr1 ~ age.cent + I(age.cent^2) + I(age.cent^3) +I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
print("Linear model")
check_fit(linfit)
print("Quadratic model")
check_fit(quadfit)
print("Cubic model")
check_fit(cubfit)
print("Quartic model")
check_fit(quartfit)
anova(linfit, quadfit, cubfit, quartfit) %>% as.data.frame() %>% 
  kbl() %>% kable_styling(full_width = F)
```

### Plot model (Quartic)

```{r}
rm(linfit, quadfit, cubfit)
#---------- make df of original data ----------
df.plot = dat %>%
  group_by(across(sweep)) %>%
  summarise(Age = mean(Age, na.rm = T),
            Phenotype = mean(Dsdpr1, na.rm = T),
            SD = sd(Dsdpr1, na.rm = T),
            n = sum(!is.na(Dsdpr1))) %>%
  mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
         lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))

#---------- plot ---------------
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model

emm = emmeans(quartfit, specs = ~ age.cent + I(age.cent^2) + I(age.cent^3) + I(age.cent^4), 
              at = list(age.cent = age_cent), 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean),
            linewidth = 1.5, na.rm = T, colour = "#0072B2") + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T, fill = "#0072B2") +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Peer Problems")

emmeans.plot
```