---
title: "Weighted analyses of SDQ trajectories following FI"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, results = 'asis',
                      fig.width=15, fig.height=10)
library(lme4)
library(lmerTest)
library(kableExtra)
library(tidyverse)
library(emmeans)
emm_options(lmerTest.limit = 20000, pbkrtest.limit = 20000)
```

```{r warning function}
# function to print any singular fit and convergence issues warning messages.
check_fit <- function(m) {
  msg = summary(m)$optinfo$conv$lme4$messages |> unlist()
  if (any(grepl("isSingular", msg))==T) {
    print("Singular fit")
  } else {print("No singular fit")}
  
  if (any(grepl("failed to converge", msg))==T) {
    print("Failed to converge")
  } else  {print("No convergence issues")}
  } 
```

```{r ggplot theme}
pal = c("#E69F00","#56B4E9","#009E73",
        "#F5C710","#0072B2","#D55E00",
        "#CC79A7","#999999","#000000")

# Set default ggplot colour palette to colourblind-friendly Okabe Ito (2008)
options(ggplot2.discrete.colour=pal, ggplot2.discrete.fill=pal)

# Set global theme for ggplot
my_theme <- function(base_size = 12, base_family = ""){
  theme_bw(base_size = base_size, base_family = base_family) %+replace%
    theme(
      panel.background = element_rect(fill = "transparent"),
      plot.background = element_rect(fill = "transparent", color = NA),
      panel.grid.major = element_line(colour = "grey88"),
      panel.grid.minor = element_line(colour = "grey99"),
      legend.background = element_rect(fill = "transparent"),
      legend.box.background = element_rect(fill = "transparent"),
      panel.ontop = FALSE
    )
}

theme_set(my_theme())
```

```{r read data}
dat = readRDS("G://users/eileen/Food_Ins/DATA/wt_GUS_long.rds")

# setup emmeans parameters for plots
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent, DeEqv5 = levels(dat$DeEqv5), Sex = levels(dat$Sex), ALeSNim2 = levels(dat$ALeSNim2))

# setup emmeans parameters for contrasts, using fewer timepoints
age_vals_c = c(mean(dat[dat$sweep == "De",]$Age, na.rm = T), 
               mean(dat[dat$sweep == "Dg",]$Age, na.rm = T), 
               mean(dat[dat$sweep == "Dj",]$Age, na.rm = T))
age_cent_c = age_vals_c - mean(dat$Age, na.rm = T)
at_vals_c = list(age.cent = age_cent_c, DeEqv5 = levels(dat$DeEqv5), Sex = levels(dat$Sex), ALeSNim2 = levels(dat$ALeSNim2))

# set contrast grid so that it's always more FI vs less FI
contrast_grid = list(
  "A little vs Not at all" = c(-1, 0, 1),
  "A lot/fair amount vs Not at all" = c(-1, 1, 0),
  "A lot/fair amount vs A little" = c(0, 1, -1)
)
```

# SDQ Trajectories by 3-level Food Insecurity

Total sample (i.e. unique IDs) = `r length(unique(dat$Idnumber))`

```{r}
sumtable = dat |> 
  rename(SDQ_Emotion=Dsdem1,
         SDQ_Conduct=Dsdco1,
         SDQ_Hyper=Dsdhy1,
         SDQ_Peer=Dsdpr1) |> 
  pivot_longer(SDQ_Conduct:SDQ_Peer, values_to = "SDQ", names_to = "Subscale") |>
  group_by(Subscale,sweep) |> 
  summarise(N = n(),
           mean = mean(SDQ, na.rm = T),
           SD = sd(SDQ, na.rm = T),
           median = median(SDQ, na.rm = T),
           IQR = IQR(SDQ, na.rm = T)
          )

kbl(sumtable, digits = 3) |> kable_styling(full_width = F) |> scroll_box(height="300px")
```

```{r}
table(dat$sweep, dat$MeFaff3lvl) |> kbl() |> kable_styling(full_width = F)
```

## Conduct Problems and FI {.tabset}

```{r conduct descriptive stats}
df.plot = dat |>
          group_by(across(sweep)) |>
          summarise(Age = mean(Age, na.rm = T),
                    Phenotype = mean(Dsdco1, na.rm = T),
                    SD = sd(Dsdco1, na.rm = T),
                    n = sum(!is.na(Dsdco1))) |>
          mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
                 lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))
```

### No covariates

<details>
  <summary><b>Estimates</b></summary>


```{r}
fit = lmer(Dsdco1 ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) |>
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>


<details>
  <summary><b>Contrasts</b></summary>

```{r}
emm_c = emmeans(fit, specs = ~ MeFaff3lvl*age.cent, 
              at = at_vals_c, 
              lmer.df = "satterthwaite")

#fit contrasts between MeFaff3lvl level at 3 timepoints
emm_comparisons = contrast(emm_c, method = contrast_grid, simple = "MeFaff3lvl") |> broom::tidy()

#replace with actual age values
emm_comparisons$Age = c(rep(age_vals_c[1], 3), rep(age_vals_c[2], 3), rep(age_vals_c[3], 3))

emm_comparisons |> relocate(Age) |> select(-age.cent, -term) |> kbl(digits=3) |> 
  kable_styling(full_width = F)
```

</details>

<details>
  <summary><b>Plot</b></summary>

```{r}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) |> cbind(age_vals)

#plot overall model 
emmeans.plot = pred |> ggplot() + 
  geom_line(aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Conduct")

emmeans.plot
```

</details>

### Covariates sex and income

<details>
  <summary><b>Estimates</b></summary>

```{r}
fit = lmer(Dsdco1 ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + Sex + DeEqv5 + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) |>
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>


<details>
  <summary><b>Plot</b></summary>

```{r}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + Sex + DeEqv5, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) |> cbind(age_vals)

#plot overall model 
emmeans.plot = pred |> filter(DeEqv5 == "1") |> ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Conduct")

emmeans.plot + facet_grid(~ Sex)
```

</details>

### Covariates sex, income, maternal MH

<details>
  <summary><b>Estimates</b></summary>

```{r}
fit = lmer(Dsdco1 ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + Sex + DeEqv5 + scale(DeSf12mn) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) |>
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>


<details>
  <summary><b>Plot</b></summary>

```{r}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + Sex + DeEqv5 + scale(DeSf12mn), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) |> cbind(age_vals)


#plot overall model 
emmeans.plot = pred |> filter(DeEqv5 == "1") |> ggplot() + 
  geom_line(aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Conduct")

emmeans.plot + facet_grid(~ Sex)
```

</details>

### Covariates sex, income, maternal MH, SIMD

<details>
  <summary><b>Estimates</b></summary>

```{r}
fit = lmer(Dsdco1 ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + Sex + DeEqv5 + scale(DeSf12mn) + ALeSNim2 + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) |>
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>


<details>
  <summary><b>Contrasts</b></summary>

```{r}
emm_c = emmeans(fit, specs = ~ MeFaff3lvl*age.cent, 
              at = at_vals_c, 
              lmer.df = "satterthwaite")

#fit contrasts between MeFaff3lvl level at 3 timepoints
emm_comparisons = contrast(emm_c, method = contrast_grid, simple = "MeFaff3lvl") |> broom::tidy()

#replace with actual age values
emm_comparisons$Age = c(rep(age_vals_c[1], 3), rep(age_vals_c[2], 3), rep(age_vals_c[3], 3))

emm_comparisons |> relocate(Age) |> select(-age.cent, -term) |> kbl(digits=3) |> 
  kable_styling(full_width = F)
```

</details>


<details>
  <summary><b>Plot: lowest level covariates</b></summary>

```{r}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + Sex + DeEqv5 + ALeSNim2 + scale(DeSf12mn), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) |> cbind(age_vals)

#plot overall model 
emmeans.plot = pred |> filter(DeEqv5 == "1", ALeSNim2 == "1") |> ggplot() + 
  geom_line(aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Conduct") + 
  ggtitle("Lowest income and SIMD")

emmeans.plot + facet_grid(~ Sex)
```

</details>

<details>
  <summary><b>Plot: Highest level covariates</b></summary>

```{r}
emmeans.plot = pred |> filter(DeEqv5 == "5", ALeSNim2 == "5") |> ggplot() + 
  geom_line(aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Conduct") + 
  ggtitle("Highest income and SIMD")

emmeans.plot + facet_grid(~ Sex)
```

</details>

## Emotional Problems and FI {.tabset}

```{r emotional descriptive stats}
df.plot = dat |>
          group_by(across(sweep)) |>
          summarise(Age = mean(Age, na.rm = T),
                    Phenotype = mean(Dsdem1, na.rm = T),
                    SD = sd(Dsdem1, na.rm = T),
                    n = sum(!is.na(Dsdem1))) |>
          mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
                 lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))
```


### No covariates

<details>
  <summary><b>Estimates</b></summary>

```{r}
fit = lmer(Dsdem1 ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) |>
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>


<details>
  <summary><b>Contrasts</b></summary>

```{r}
emm_c = emmeans(fit, specs = ~ MeFaff3lvl*age.cent, 
              at = at_vals_c, 
              lmer.df = "satterthwaite")

#fit contrasts between MeFaff3lvl level at 3 timepoints
emm_comparisons = contrast(emm_c, method = contrast_grid, simple = "MeFaff3lvl") |> broom::tidy()

#replace with actual age values
emm_comparisons$Age = c(rep(age_vals_c[1], 3), rep(age_vals_c[2], 3), rep(age_vals_c[3], 3))

emm_comparisons |> relocate(Age) |> select(-age.cent, -term) |> kbl(digits=3) |> 
  kable_styling(full_width = F)
```

</details>

<details>
  <summary><b>Plot</b></summary>

```{r}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) |> cbind(age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Emotional")

emmeans.plot
```


</details>

### Covariates sex and income

<details>
  <summary><b>Estimates</b></summary>

```{r}
fit = lmer(Dsdem1 ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + Sex + DeEqv5 + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) |>
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>


<details>
  <summary><b>Plot</b></summary>

```{r}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + Sex + DeEqv5, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) |> cbind(age_vals)

#plot overall model 
emmeans.plot = pred |> filter(DeEqv5 == "1") |> ggplot() + 
  geom_line(aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Emotional")

emmeans.plot + facet_grid(~ Sex)
```

</details>

### Covariates sex, income, maternal MH

<details>
  <summary><b>Estimates</b></summary>

```{r}
fit = lmer(Dsdem1 ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + Sex + DeEqv5 + scale(DeSf12mn) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) |>
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>


<details>
  <summary><b>Plot</b></summary>

```{r}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + Sex + DeEqv5 + scale(DeSf12mn), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) |> cbind(age_vals)

#plot overall model 
emmeans.plot = pred |> filter(DeEqv5 == "1") |> ggplot() + 
  geom_line(aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Emotional")

emmeans.plot + facet_grid(~ Sex)
```


</details>

### Covariates sex, income, maternal MH, SIMD {.tabset}

<details>
  <summary><b>Estimates</b></summary>

```{r}
fit = lmer(Dsdem1 ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + Sex + DeEqv5 + scale(DeSf12mn) + ALeSNim2 + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) |>
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>


<details>
  <summary><b>Contrasts</b></summary>

```{r}
emm_c = emmeans(fit, specs = ~ MeFaff3lvl*age.cent, 
              at = at_vals_c, 
              lmer.df = "satterthwaite")

#fit contrasts between MeFaff3lvl level at 3 timepoints
emm_comparisons = contrast(emm_c, method = contrast_grid, simple = "MeFaff3lvl") |> broom::tidy()

#replace with actual age values
emm_comparisons$Age = c(rep(age_vals_c[1], 3), rep(age_vals_c[2], 3), rep(age_vals_c[3], 3))

emm_comparisons |> relocate(Age) |> select(-age.cent, -term) |> kbl(digits=3) |> 
  kable_styling(full_width = F)
```

</details>

<details>
  <summary><b>Plot: Lowest level covariates</b></summary>

```{r}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + Sex + DeEqv5 + ALeSNim2 + scale(DeSf12mn), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) |> cbind(age_vals)

#plot overall model 
emmeans.plot = pred |> filter(DeEqv5 == "1", ALeSNim2 == "1") |> ggplot() + 
  geom_line(aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Emotional") + 
  ggtitle("Lowest income and SIMD")

emmeans.plot + facet_grid(~ Sex)
```

</details>

<details>
  <summary><b>Plot: Highest level covariates</b></summary>

```{r}
#plot overall model 
emmeans.plot = pred |> filter(DeEqv5 == "5", ALeSNim2 == "5") |> ggplot() + 
  geom_line(aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Emotional") + 
  ggtitle("Highest income and SIMD")

emmeans.plot + facet_grid(~ Sex)
```

</details>

## Hyperactivity and FI {.tabset}

```{r hyperactivity descriptive stats}
df.plot = dat |>
          group_by(across(sweep)) |>
          summarise(Age = mean(Age, na.rm = T),
                    Phenotype = mean(Dsdhy1, na.rm = T),
                    SD = sd(Dsdhy1, na.rm = T),
                    n = sum(!is.na(Dsdhy1))) |>
          mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
                 lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))
```

### No covariates

<details>
  <summary><b>Estimates</b></summary>

```{r}
fit = lmer(Dsdhy1 ~ age.cent*MeFaff3lvl + 
             (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) |>
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>


<details>
  <summary><b>Contrasts</b></summary>

```{r}
emm_c = emmeans(fit, specs = ~ MeFaff3lvl*age.cent, 
              at = at_vals_c, 
              lmer.df = "satterthwaite")

#fit contrasts between MeFaff3lvl level at 3 timepoints
emm_comparisons = contrast(emm_c, method = contrast_grid, simple = "MeFaff3lvl") |> broom::tidy()

#replace with actual age values
emm_comparisons$Age = c(rep(age_vals_c[1], 3), rep(age_vals_c[2], 3), rep(age_vals_c[3], 3))

emm_comparisons |> relocate(Age) |> select(-age.cent, -term) |> kbl(digits=3) |> 
  kable_styling(full_width = F)
```

</details>

<details>
<summary><b>Plot</b></summary>

```{r}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) |> cbind(age_vals)

#plot overall model 
emmeans.plot = pred |> ggplot() + 
  geom_line(
            aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(
              aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Hyperactivity")

emmeans.plot
```

</details>

### Covariates sex and income

<details>
  <summary><b>Estimates</b></summary>

```{r}
fit = lmer(Dsdhy1 ~ age.cent*MeFaff3lvl +
             Sex + DeEqv5 + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) |>
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>


<details>
<summary><b>Plot</b></summary>

```{r}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + 
                Sex + DeEqv5, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) |> cbind(age_vals)

#plot overall model 
emmeans.plot = pred |> filter(DeEqv5 == "1") |> ggplot() + 
  geom_line(aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Hyperactivity")

emmeans.plot + facet_grid(~ Sex)
```

</details>

### Covariates sex, income, maternal MH

<details>
  <summary><b>Estimates</b></summary>

```{r}
fit = lmer(Dsdhy1 ~ age.cent*MeFaff3lvl + 
             Sex + DeEqv5 + scale(DeSf12mn) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) |>
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>


<details>
<summary><b>Plot</b></summary>

```{r}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + 
                Sex + DeEqv5 + scale(DeSf12mn), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) |> cbind(age_vals)


#plot overall model 
emmeans.plot =  pred |> filter(DeEqv5 == "1") |> ggplot() + 
  geom_line(aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Hyperactivity")

emmeans.plot + facet_grid(~ Sex)
```

</details>

### Covariates sex, income, maternal MH, SIMD

<details>
  <summary><b>Estimates</b></summary>

```{r}
fit = lmer(Dsdhy1 ~ age.cent*MeFaff3lvl + 
             Sex + DeEqv5 + scale(DeSf12mn) + ALeSNim2 + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) |>
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>


<details>
  <summary><b>Contrasts</b></summary>

```{r}
emm_c = emmeans(fit, specs = ~ MeFaff3lvl*age.cent, 
              at = at_vals_c, 
              lmer.df = "satterthwaite")

#fit contrasts between MeFaff3lvl level at 3 timepoints
emm_comparisons = contrast(emm_c, method = contrast_grid, simple = "MeFaff3lvl") |> broom::tidy()

#replace with actual age values
emm_comparisons$Age = c(rep(age_vals_c[1], 3), rep(age_vals_c[2], 3), rep(age_vals_c[3], 3))

emm_comparisons |> relocate(Age) |> select(-age.cent, -term) |> kbl(digits=3) |> 
  kable_styling(full_width = F)
```

</details>

<details>
  <summary><b>Plot: Lowest level covariates</b></summary>

```{r}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl +
                Sex + DeEqv5 + ALeSNim2 + scale(DeSf12mn), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) |> cbind(age_vals)

#plot overall model 
low.plot = pred |> filter(DeEqv5 == "1", ALeSNim2 == "1") |> ggplot() + 
  geom_line(
            aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(
              aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Hyperactivity") + 
  ggtitle("Lowest income and SIMD")

low.plot + facet_grid(~ Sex)
```

</details>


<details>
  <summary><b>Plot: Highest level covariates</b></summary>
  
```{r}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl +
                Sex + DeEqv5 + ALeSNim2 + scale(DeSf12mn), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) |> cbind(age_vals)

#plot overall model 
high.plot = pred |> filter(DeEqv5 == "5", ALeSNim2 == "5") |> ggplot() + 
  geom_line(
            aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(
              aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Hyperactivity") + 
  ggtitle("Highest income and SIMD")

high.plot + facet_grid(~ Sex)
```

</details>

## Peer problems and FI {.tabset}

```{r peer descriptive stats}
df.plot = dat |>
          group_by(across(sweep)) |>
          summarise(Age = mean(Age, na.rm = T),
                    Phenotype = mean(Dsdpr1, na.rm = T),
                    SD = sd(Dsdpr1, na.rm = T),
                    n = sum(!is.na(Dsdpr1))) |>
          mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
                 lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))
```

### No covariates

<details>
  <summary><b>Estimates</b></summary>

```{r}
fit = lmer(Dsdpr1 ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + I(age.cent^4)*MeFaff3lvl + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) |>
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>


<details>
  <summary><b>Contrasts</b></summary>

```{r}
emm_c = emmeans(fit, specs = ~ MeFaff3lvl*age.cent, 
              at = at_vals_c, 
              lmer.df = "satterthwaite")

#fit contrasts between MeFaff3lvl level at 3 timepoints
emm_comparisons = contrast(emm_c, method = contrast_grid, simple = "MeFaff3lvl") |> broom::tidy()

#replace with actual age values
emm_comparisons$Age = c(rep(age_vals_c[1], 3), rep(age_vals_c[2], 3), rep(age_vals_c[3], 3))

emm_comparisons |> relocate(Age) |> select(-age.cent, -term) |> kbl(digits=3) |> 
  kable_styling(full_width = F)
```

</details>

<details>
<summary><b>Plot</b></summary>

```{r}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + I(age.cent^4)*MeFaff3lvl, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) |> cbind(age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Peer")

emmeans.plot
```

</details>

### Covariates sex and income

<details>
  <summary><b>Estimates</b></summary>

```{r}
fit = lmer(Dsdpr1 ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + I(age.cent^4)*MeFaff3lvl + Sex + DeEqv5 + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) |>
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>


<details>
<summary><b>Plot</b></summary>

```{r}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + I(age.cent^4)*MeFaff3lvl + Sex + DeEqv5, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) |> cbind(age_vals)

#plot overall model 
emmeans.plot = pred |> filter(DeEqv5 == "1") |> ggplot() + 
  geom_line(aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Peer")

emmeans.plot + facet_grid(~ Sex)
```

</details>

### Covariates sex, income, maternal MH

<details>
  <summary><b>Estimates</b></summary>

```{r}
fit = lmer(Dsdpr1 ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + I(age.cent^4)*MeFaff3lvl + Sex + DeEqv5 + scale(DeSf12mn) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) |>
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>


<details>
<summary><b>Plot</b></summary>

```{r}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + I(age.cent^4)*MeFaff3lvl + Sex + DeEqv5 + scale(DeSf12mn), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) |> cbind(age_vals)


#plot overall model 
emmeans.plot = pred |> filter(DeEqv5 == "1") |> ggplot() + 
  geom_line( aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon( aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Peer")

emmeans.plot + facet_grid(~ Sex)
```

</details>

### Covariates sex, income, maternal MH, SIMD

<details>
  <summary><b>Estimates</b></summary>

```{r}
fit = lmer(Dsdpr1 ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + I(age.cent^4)*MeFaff3lvl + Sex + DeEqv5 + scale(DeSf12mn) + ALeSNim2 + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) |>
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>

<details>
  <summary><b>Contrasts</b></summary>

```{r}
emm_c = emmeans(fit, specs = ~ MeFaff3lvl*age.cent, 
              at = at_vals_c, 
              lmer.df = "satterthwaite")

#fit contrasts between MeFaff3lvl level at 3 timepoints
emm_comparisons = contrast(emm_c, method = contrast_grid, simple = "MeFaff3lvl") |> broom::tidy()

#replace with actual age values
emm_comparisons$Age = c(rep(age_vals_c[1], 3), rep(age_vals_c[2], 3), rep(age_vals_c[3], 3))

emm_comparisons |> relocate(Age) |> select(-age.cent, -term) |> kbl(digits=3) |> 
  kable_styling(full_width = F)
```

</details>

<details>
  <summary><b>Plot: Lowest level covariates</b></summary>

```{r}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + I(age.cent^4)*MeFaff3lvl + Sex + DeEqv5 + ALeSNim2 + scale(DeSf12mn), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) |> cbind(age_vals)

#plot overall model 
low.plot = pred |> filter(DeEqv5 == "1", ALeSNim2 == "1") |> ggplot() + 
  geom_line( aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon( aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Peer") + 
  ggtitle("Lowest income and SIMD")

low.plot + facet_grid(~ Sex)
```

</details>


<details>
  <summary><b>Plot: Highest level covariates</b></summary>

```{r}
high.plot = pred |> filter(DeEqv5 == "5", ALeSNim2 == "5") |> ggplot() + 
  geom_line(aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon( aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Peer") + 
  ggtitle("Highest income and SIMD")

high.plot + facet_grid(~ Sex)
```

</details>