---
title: "Social support and food insecurity"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, results = "asis", fig.width=10)
library(tidyverse)
library(lme4)
library(lmerTest)
library(emmeans)
library(kableExtra)
emm_options(lmerTest.limit = 20000, pbkrtest.limit = 20000)
```

```{r}
# function to print any singular fit and convergence issues warning messages.
check_fit <- function(m) {
  msg = summary(m)$optinfo$conv$lme4$messages %>% unlist()
  if (any(grepl("isSingular", msg))==T) {
    print("Singular fit")
  } else {print("No singular fit")}
  
  if (any(grepl("failed to converge", msg))==T) {
    print("Failed to converge")
  } else  {print("No convergence issues")}
  } 
```

```{r ggplot theme}
pal = c("#E69F00","#56B4E9","#009E73",
        "#F5C710","#0072B2","#D55E00",
        "#CC79A7","#999999","#000000")

# Set default ggplot colour palette to colourblind-friendly Okabe Ito (2008)
options(ggplot2.discrete.colour=pal, ggplot2.discrete.fill=pal)

# Set global theme for ggplot
my_theme <- function(base_size = 12, base_family = ""){
  theme_bw(base_size = base_size, base_family = base_family) %+replace%
    theme(
      panel.background = element_rect(fill = "transparent"),
      plot.background = element_rect(fill = "transparent", color = NA),
      panel.grid.major = element_line(colour = "grey88"),
      panel.grid.minor = element_line(colour = "grey99"),
      legend.background = element_rect(fill = "transparent"),
      legend.box.background = element_rect(fill = "transparent"),
      panel.ontop = FALSE
    )
}

theme_set(my_theme())
```

# SDQ trajectories by food insecurity x social support

```{r}
dat = readRDS("G://users/eileen/Food_Ins/DATA/wt_GUS_social.rds")

## dataframe for new predictions

age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent, DeEqv5 = levels(dat$DeEqv5), Sex = levels(dat$Sex))

# setup emmeans parameters for contrasts, age 5 - 16
age_vals_c = seq(5, 16, 1)
age_cent_c = age_vals_c - mean(dat$Age, na.rm = T)
at_vals_c = list(age.cent = age_cent_c, DeEqv5 = levels(dat$DeEqv5), Sex = levels(dat$Sex), ALeSNim2 = levels(dat$ALeSNim2))

# contrast grid to use for emmeans, comparing enough/not enough for each FI level
contrast_grid = list(
  "Not at all.Not enough vs Enough" = c(-1, 0, 0, 0, 0, 1),
  "A little.Not enough vs Enough" = c(0, -1, 1, 0, 0, 0),
  "A lot/fair amount.Not enough vs Enough" = c(0, 0, 0, -1, 1, 0)
)
```

Total sample (i.e. unique IDs) = `r length(unique(dat$Idnumber))` \
\
\
3-level food insecurity is combined with 2-level enough help to get a 6-level food*social support measure "food_help".\


```{r}
sumtable = dat |> 
  rename(SDQ_Emotion=Dsdem1,
         SDQ_Conduct=Dsdco1,
         SDQ_Hyper=Dsdhy1,
         SDQ_Peer=Dsdpr1) |> 
  pivot_longer(SDQ_Conduct:SDQ_Peer, values_to = "SDQ", names_to = "Subscale") |>
  group_by(Subscale,sweep) |> 
  summarise(N = n(),
           mean = mean(SDQ, na.rm = T),
           SD = sd(SDQ, na.rm = T),
           median = median(SDQ, na.rm = T),
           IQR = IQR(SDQ, na.rm = T)
          )

kbl(sumtable, digits = 3) |> kable_styling(full_width = F) |> scroll_box(height = "300px")
```

```{r}
table(dat$sweep, dat$food_help) |> kbl() |> kable_styling(full_width = F)
```


## Conduct problems {.tabset}


### No covariates

<details>
  <summary><b>Estimates</b></summary>
  
```{r}
fit = lmer(Dsdco1 ~ food_help*age.cent + food_help*I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>



<details>
  <summary><b>Contrasts</b></summary>

```{r}
emm_c = emmeans(fit, specs = ~ food_help*age.cent, 
              at = at_vals_c, 
              lmer.df = "satterthwaite")

emm_comparisons = contrast(emm_c, method = contrast_grid, simple = "food_help") |> broom::tidy()
#replace emm_comparisons age.cent column with actual age values
emm_comparisons$Age = age_vals_c[match(emm_comparisons$age.cent, age_cent_c)]

emm_comparisons |> relocate(Age) |> select(-age.cent, -term) |> kbl(digits=3) |> 
  kable_styling(full_width = F) |> scroll_box(height="300px")
```

</details>

<details>
<summary><b>Plot</b></summary>

```{r results='asis'}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help , 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = ggplot() +
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Conduct")
  
fig + facet_grid(. ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

</details>

### Covariates sex and income

<details>
  <summary><b>Estimates</b></summary>

```{r}
fit = lmer(Dsdco1 ~ food_help*age.cent + food_help*I(age.cent^2) + Sex + DeEqv5 +
             (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>


<details>
  <summary><b>Lowest income plot</b></summary>

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help + Sex + DeEqv5, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == "1") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Conduct")

fig + facet_grid(Sex ~factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

</details>

<details>
  <summary><b>Highest income plot</b></summary>

```{r}
fig = pred %>% filter(DeEqv5 == "5") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Conduct")

fig + facet_grid(Sex ~factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

</details>

### Sex, income, maternal MH

<details>
  <summary><b>Estimates</b></summary>

```{r}
fit = lmer(Dsdco1 ~ food_help*age.cent + food_help*I(age.cent^2) + Sex + DeEqv5 +
             scale(DeSf12mn) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>


<details>
  <summary><b>Lowest income plot</b></summary>

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help + Sex + DeEqv5 + scale(DeSf12mn), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == "1") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Conduct")

fig + facet_grid(Sex ~factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

</details>

<details>
  <summary><b>Highest income plot</b></summary>

```{r}
fig = pred %>% filter(DeEqv5 == "5") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Conduct")

fig + facet_grid(Sex ~factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

</details>

### Sex, income, maternal MH + SIMD

<details>
  <summary><b>Estimates</b></summary>

```{r}
fit = lmer(Dsdco1 ~ food_help*age.cent + food_help*I(age.cent^2) + Sex + DeEqv5 +
             scale(DeSf12mn) + ALeSNim2 + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>



<details>
  <summary><b>Contrasts</b></summary>

```{r}
emm_c = emmeans(fit, specs = ~ food_help*age.cent, 
              at = at_vals_c, 
              lmer.df = "satterthwaite")

#fit contrasts between MeFaff3lvl level at 3 timepoints
emm_comparisons = contrast(emm_c, method = contrast_grid, simple = "food_help") |> broom::tidy()
#replace emm_comparisons age.cent column with actual age values
emm_comparisons$Age = age_vals_c[match(emm_comparisons$age.cent, age_cent_c)]

emm_comparisons |> relocate(Age) |> select(-age.cent, -term) |> kbl(digits=3) |> 
  kable_styling(full_width = F) |> scroll_box(height="300px")
```

</details>

<details>
  <summary><b>Lowest income plot</b></summary>

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help + Sex + DeEqv5 + scale(DeSf12mn) + ALeSNim2, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == "1", ALeSNim2 == "1") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Conduct")

fig + facet_grid(Sex ~factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

</details>

<details>
  <summary><b>Highest income plot</b></summary>

```{r}
fig = pred %>% filter(DeEqv5 == "5", ALeSNim2 == "5") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Conduct")

fig + facet_grid(Sex ~factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

</details>

## Emotional problems {.tabset}

### No covariates

<details>
  <summary><b>Estimates</b></summary>

```{r}
fit = lmer(Dsdem1 ~ food_help*age.cent + food_help*I(age.cent^2) + food_help*I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>



<details>
  <summary><b>Contrasts</b></summary>

```{r}
emm_c = emmeans(fit, specs = ~ food_help*age.cent, 
              at = at_vals_c, 
              lmer.df = "satterthwaite")

#fit contrasts between MeFaff3lvl level at 3 timepoints
emm_comparisons = contrast(emm_c, method = contrast_grid, simple = "food_help") |> broom::tidy()
#replace emm_comparisons age.cent column with actual age values
emm_comparisons$Age = age_vals_c[match(emm_comparisons$age.cent, age_cent_c)]

emm_comparisons |> relocate(Age) |> select(-age.cent, -term) |> kbl(digits=3) |> 
  kable_styling(full_width = F) |> scroll_box(height="300px")
```

</details>

<details>
<summary><b>Plot</b></summary>

```{r results='asis'}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help + I(age.cent^3)*food_help, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = ggplot() +
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Emotional")
  
fig + facet_grid(. ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

</details>

### Covariates sex and income

<details>
  <summary><b>Estimates</b></summary>

```{r}
fit = lmer(Dsdem1 ~ food_help*age.cent + food_help*I(age.cent^2) + food_help*I(age.cent^3) + Sex + DeEqv5 +
             (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>


<details>
  <summary><b>Lowest income plot</b></summary>

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help + I(age.cent^3)*food_help  + Sex + DeEqv5, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == "1") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Emotional")

fig + facet_grid(Sex ~factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

</details>

<details>
  <summary><b>Highest income plot</b></summary>

```{r}
fig = pred %>% filter(DeEqv5 == "5") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Emotional")

fig + facet_grid(Sex ~factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

</details>

### Sex, income, maternal MH

<details>
  <summary><b>Estimates</b></summary>

```{r}
fit = lmer(Dsdem1 ~ food_help*age.cent + food_help*I(age.cent^2) + food_help*I(age.cent^3) + Sex + DeEqv5 + scale(DeSf12mn) +
             (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>


<details>
  <summary><b>Lowest income plot</b></summary>

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help + I(age.cent^3)*food_help  + Sex + DeEqv5 + scale(DeSf12mn), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == "1") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Emotional")

fig + facet_grid(Sex ~factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```


</details>

<details>
  <summary><b>Highest income plot</b></summary>


```{r}
fig = pred %>% filter(DeEqv5 == "5") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Emotional")

fig + facet_grid(Sex ~factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

</details>

### Sex, income, maternal MH, SIMD

<details>
  <summary><b>Estimates</b></summary>

```{r}
fit = lmer(Dsdem1 ~ food_help*age.cent + food_help*I(age.cent^2) + food_help*I(age.cent^3) + Sex + DeEqv5 + scale(DeSf12mn) + ALeSNim2 +
             (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>



<details>
  <summary><b>Contrasts</b></summary>

```{r}
emm_c = emmeans(fit, specs = ~ food_help*age.cent, 
              at = at_vals_c, 
              lmer.df = "satterthwaite")

#fit contrasts between MeFaff3lvl level at 3 timepoints
emm_comparisons = contrast(emm_c, method = contrast_grid, simple = "food_help") |> broom::tidy()
#replace emm_comparisons age.cent column with actual age values
emm_comparisons$Age = age_vals_c[match(emm_comparisons$age.cent, age_cent_c)]

emm_comparisons |> relocate(Age) |> select(-age.cent, -term) |> kbl(digits=3) |> 
  kable_styling(full_width = F) |> scroll_box(height="300px")
```

</details>

<details>
  <summary><b>Lowest income plot</b></summary>

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help + I(age.cent^3)*food_help  + Sex + DeEqv5 + scale(DeSf12mn) + ALeSNim2, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == "1", ALeSNim2 == "1") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Emotional")

fig + facet_grid(Sex ~factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```


</details>

<details>
  <summary><b>Highest income plot</b></summary>


```{r}
fig = pred %>% filter(DeEqv5 == "5", ALeSNim2 == "5") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Emotional")

fig + facet_grid(Sex ~factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

</details>

## Hyperactivity {.tabset}

### No covariates

<details>
  <summary><b>Estimates</b></summary>

```{r}
fit = lmer(Dsdhy1 ~ food_help*age.cent + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>



<details>
  <summary><b>Contrasts</b></summary>

```{r}
emm_c = emmeans(fit, specs = ~ food_help*age.cent, 
              at = at_vals_c, 
              lmer.df = "satterthwaite")

#fit contrasts between MeFaff3lvl level at 3 timepoints
emm_comparisons = contrast(emm_c, method = contrast_grid, simple = "food_help") |> broom::tidy()
#replace emm_comparisons age.cent column with actual age values
emm_comparisons$Age = age_vals_c[match(emm_comparisons$age.cent, age_cent_c)]

emm_comparisons |> relocate(Age) |> select(-age.cent, -term) |> kbl(digits=3) |> 
  kable_styling(full_width = F) |> scroll_box(height="300px")
```

</details>

<details>
<summary><b>Plot</b></summary>

```{r results='asis'}
emm = emmeans(fit, specs = ~ age.cent*food_help, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = ggplot() +
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Hyperactivity")
  
fig + facet_grid(. ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

</details>

### Covariates sex and income

<details>
  <summary><b>Estimates</b></summary>

```{r}
fit = lmer(Dsdhy1 ~ food_help*age.cent + 
             Sex + DeEqv5 + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>


<details>
  <summary><b>Lowest income plot</b></summary>

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help +
                Sex + DeEqv5, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == "1") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Hyperactivity")
  
fig + facet_grid(Sex ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```


</details>

<details>
  <summary><b>Highest income plot</b></summary>


```{r}
fig = pred %>% filter(DeEqv5 == "5") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Hyperactivity")
  
fig + facet_grid(Sex ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

</details>

### Sex, income, maternal MH

<details>
  <summary><b>Estimates</b></summary>

```{r}
fit = lmer(Dsdhy1 ~ food_help*age.cent + 
             Sex + DeEqv5 + scale(DeSf12mn) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>


<details>
  <summary><b>Lowest income plot</b></summary>

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help +
                Sex + DeEqv5 + scale(DeSf12mn), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == "1") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Hyperactivity")
  
fig + facet_grid(Sex ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```


</details>

<details>
  <summary><b>Highest income plot</b></summary>


```{r}
fig = pred %>% filter(DeEqv5 == "5") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Hyperactivity")
  
fig + facet_grid(Sex ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

</details>

### Sex, income, maternal MH + SIMD

<details>
  <summary><b>Estimates</b></summary>

```{r}
fit = lmer(Dsdhy1 ~ food_help*age.cent + 
             Sex + DeEqv5 + scale(DeSf12mn) + ALeSNim2 + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>


<details>
  <summary><b>Contrasts</b></summary>

```{r}
emm_c = emmeans(fit, specs = ~ food_help*age.cent, 
              at = at_vals_c, 
              lmer.df = "satterthwaite")

#fit contrasts between MeFaff3lvl level at 3 timepoints
emm_comparisons = contrast(emm_c, method = contrast_grid, simple = "food_help") |> broom::tidy()
#replace emm_comparisons age.cent column with actual age values
emm_comparisons$Age = age_vals_c[match(emm_comparisons$age.cent, age_cent_c)]

emm_comparisons |> relocate(Age) |> select(-age.cent, -term) |> kbl(digits=3) |> 
  kable_styling(full_width = F) |> scroll_box(height="300px")
```

</details>

<details>
  <summary><b>Lowest income plot</b></summary>

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help +
                Sex + DeEqv5 + scale(DeSf12mn) + ALeSNim2, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == "1", ALeSNim2 == "1") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Hyperactivity")
  
fig + facet_grid(Sex ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```


</details>

<details>
  <summary><b>Highest income plot</b></summary>


```{r}
fig = pred %>% filter(DeEqv5 == "5", ALeSNim2 == "5") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Hyperactivity")
  
fig + facet_grid(Sex ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

</details>

## Peer problems {.tabset}

### No Covariates

<details>
  <summary><b>Estimates</b></summary>

```{r}
fit = lmer(Dsdpr1 ~ food_help*age.cent + food_help*I(age.cent^2) + food_help*I(age.cent^3) + food_help*I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>



<details>
  <summary><b>Contrasts</b></summary>

```{r}
emm_c = emmeans(fit, specs = ~ food_help*age.cent, 
              at = at_vals_c, 
              lmer.df = "satterthwaite")

#fit contrasts between MeFaff3lvl level at 3 timepoints
emm_comparisons = contrast(emm_c, method = contrast_grid, simple = "food_help") |> broom::tidy()
#replace emm_comparisons age.cent column with actual age values
emm_comparisons$Age = age_vals_c[match(emm_comparisons$age.cent, age_cent_c)]

emm_comparisons |> relocate(Age) |> select(-age.cent, -term) |> kbl(digits=3) |> 
  kable_styling(full_width = F) |> scroll_box(height="300px")
```

</details>

<details>
<summary><b>Plot</b></summary>

```{r results='asis'}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help + I(age.cent^3)*food_help + food_help*I(age.cent^4), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = ggplot() +
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Peer Problems")
  
fig + facet_grid(. ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

</details>

### Covariates sex and income

<details>
  <summary><b>Estimates</b></summary>

```{r}
fit = lmer(Dsdpr1 ~ food_help*age.cent + food_help*I(age.cent^2) + food_help*I(age.cent^3) + food_help*I(age.cent^4) + Sex + DeEqv5 +
             (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>


<details>
  <summary><b>Lowest income plot</b></summary>

```{r results='asis'}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help + I(age.cent^3)*food_help + food_help*I(age.cent^4) + Sex + DeEqv5, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == "1") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Peer Problems")
  
fig + facet_grid(Sex ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```


</details>

<details>
  <summary><b>Highest income plot</b></summary>


```{r}
fig = pred %>% filter(DeEqv5 == "5") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Peer Problems")
  
fig + facet_grid(Sex ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

</details>

### Sex, income, maternal MH

<details>
  <summary><b>Estimates</b></summary>

```{r}
fit = lmer(Dsdpr1 ~ food_help*age.cent + food_help*I(age.cent^2) + food_help*I(age.cent^3) + food_help*I(age.cent^4) + Sex + DeEqv5 + scale(DeSf12mn) +
             (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>


<details>
  <summary><b>Lowest income plot</b></summary>

```{r results='asis'}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help + I(age.cent^3)*food_help + food_help*I(age.cent^4) + Sex + DeEqv5 + scale(DeSf12mn), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == "1") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Peer Problems")
  
fig + facet_grid(Sex ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```


</details>

<details>
  <summary><b>Highest income plot</b></summary>

```{r}
fig = pred %>% filter(DeEqv5 == "5") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Peer Problems")
  
fig + facet_grid(Sex ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

</details>

### Sex, income, maternal MH + SIMD

<details>
  <summary><b>Estimates</b></summary>

```{r}
fit = lmer(Dsdpr1 ~ food_help*age.cent + food_help*I(age.cent^2) + food_help*I(age.cent^3) + food_help*I(age.cent^4) + Sex + DeEqv5 + scale(DeSf12mn) + ALeSNim2 +
             (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit, show.se = T, show.std = T, show.stat = T, show.df = T)
```

</details>



<details>
  <summary><b>Contrasts</b></summary>

```{r}
emm_c = emmeans(fit, specs = ~ food_help*age.cent, 
              at = at_vals_c, 
              lmer.df = "satterthwaite")

#fit contrasts between MeFaff3lvl level at 3 timepoints
emm_comparisons = contrast(emm_c, method = contrast_grid, simple = "food_help") |> broom::tidy()
#replace emm_comparisons age.cent column with actual age values
emm_comparisons$Age = age_vals_c[match(emm_comparisons$age.cent, age_cent_c)]

emm_comparisons |> relocate(Age) |> select(-age.cent, -term) |> kbl(digits=3) |> 
  kable_styling(full_width = F) |> scroll_box(height="300px")
```

</details>

<details>
  <summary><b>Lowest income plot</b></summary>

```{r results='asis'}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help + I(age.cent^3)*food_help + food_help*I(age.cent^4) + Sex + DeEqv5 + scale(DeSf12mn) + ALeSNim2, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == "1", ALeSNim2 == "1") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Peer Problems")
  
fig + facet_grid(Sex ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

</details>

<details>
  <summary><b>Highest income plot</b></summary>

```{r}
fig = pred %>% filter(DeEqv5 == "5", ALeSNim2 == "5") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Peer Problems")
  
fig + facet_grid(Sex ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

</details>
