---
title: "Parental social support in GUS"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
library(tidyverse)
library(lme4)
library(lmerTest)
library(emmeans)
library(kableExtra)
emm_options(lmerTest.limit = 20000, pbkrtest.limit = 20000)
```

```{r}
# function to print any singular fit and convergence issues warning messages.
check_fit <- function(m) {
  msg = summary(m)$optinfo$conv$lme4$messages %>% unlist()
  if (any(grepl("isSingular", msg))==T) {
    print("Singular fit")
  } else {print("No singular fit")}
  
  if (any(grepl("failed to converge", msg))==T) {
    print("Failed to converge")
  } else  {print("No convergence issues")}
  } 
```

```{r ggplot theme}
pal = c("#E69F00","#56B4E9","#009E73",
        "#F5C710","#0072B2","#D55E00",
        "#CC79A7","#999999","#000000")

# Set default ggplot colour palette to colourblind-friendly Okabe Ito (2008)
options(ggplot2.discrete.colour=pal, ggplot2.discrete.fill=pal)

# Set global theme for ggplot
my_theme <- function(base_size = 12, base_family = ""){
  theme_bw(base_size = base_size, base_family = base_family) %+replace%
    theme(
      panel.background = element_rect(fill = "transparent"),
      plot.background = element_rect(fill = "transparent", color = NA),
      panel.grid.major = element_line(colour = "grey88"),
      panel.grid.minor = element_line(colour = "grey99"),
      legend.background = element_rect(fill = "transparent"),
      legend.box.background = element_rect(fill = "transparent"),
      panel.ontop = FALSE
    )
}

theme_set(my_theme())
```

## Parental social support as a protective factor

Trajectories of SDQ with parental support to investigate whether parental social support could be protective.

"MdSNpf10" - Not counting people who live with you, how many people do you have a close relationship with?  
  1: I have close relationships with lots of people  
  2: I have close relationships with some people  
  3: I have one or two close relationships  
  4: I don't have any close relationships  
  
"MdSNsp01" - Overall, how do you feel about the amount of support or help you get from friends or family living elsewhere?  
  1: I get enough help  
  2: I don't get enough help  
  3: I don't get any help  
  4: I don't need any help  

To avoid over-complicating the model and to better deal with the low sample size of those with no help, a binary variable will be created combining Not enough and No help. "Do not need help" will be removed too.

```{r descriptive, results='asis'}
dat = readRDS("G://users/eileen/Food_Ins/DATA/wt_GUS_social.rds")
dat_soc = readRDS("G://users/eileen/Food_Ins/DATA/wt_GUS_social_wide.rds")
dat_descr = dat_soc %>% select(MdSNpf10, MdSNsp01, help_bin, food_help)

summarytools::dfSummary(dat_descr, round.digits = 3,
  valid.col = F, varnumbers = F, labels.col = T,
  na.col = F, graph.col = F, style= "grid", headings = F, plain.ascii = F)
```

```{r results='asis'}
dat %>% group_by(sweep, help_bin) %>%
  summarise(
    N = n_distinct(Idnumber),
    Conduct = mean(Dsdco1, na.rm=T),
    Emot = mean(Dsdem1, na.rm=T),
    Hyper = mean(Dsdhy1, na.rm=T),
    Peer = mean(Dsdpr1, na.rm=T)
  ) %>% kbl(digits = 3) %>% kable_styling()
```

### Conduct problems {.tabset}

#### Close relationships

```{r}
fit = lmer(Dsdco1 ~ MdSNpf10*age.cent + MdSNpf10*I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r results='asis'}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*MdSNpf10 + I(age.cent^2)*MdSNpf10, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = MdSNpf10),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = MdSNpf10,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Conduct")

emmeans.plot
```

#### Enough help

```{r}
fit = lmer(Dsdco1 ~ MdSNsp01*age.cent + MdSNsp01*I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r results='asis'}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*MdSNsp01 + I(age.cent^2)*MdSNsp01, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = MdSNsp01),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = MdSNsp01,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Conduct")

emmeans.plot
```

#### Binary help

```{r}
fit = lmer(Dsdco1 ~ help_bin*age.cent + help_bin*I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r results='asis'}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*help_bin + I(age.cent^2)*help_bin, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = help_bin),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = help_bin,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Conduct")

emmeans.plot
```


### Emotional problems {.tabset}

#### Close relationships

```{r}
fit = lmer(Dsdem1 ~ MdSNpf10*age.cent + MdSNpf10*I(age.cent^2) + MdSNpf10*I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r results='asis'}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*MdSNpf10 + I(age.cent^2)*MdSNpf10 + I(age.cent^3)*MdSNpf10, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = MdSNpf10),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = MdSNpf10,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Emotional")

emmeans.plot
```

#### Enough help

```{r}
fit = lmer(Dsdem1 ~ MdSNsp01*age.cent + MdSNsp01*I(age.cent^2) + MdSNsp01*I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r results='asis'}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*MdSNsp01 + I(age.cent^2)*MdSNsp01 + I(age.cent^3)*MdSNsp01, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = MdSNsp01),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = MdSNsp01,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Emotional")

emmeans.plot
```

#### Binary help

```{r}
fit = lmer(Dsdem1 ~ help_bin*age.cent + help_bin*I(age.cent^2) + help_bin*I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r results='asis'}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*help_bin + I(age.cent^2)*help_bin + I(age.cent^3)*help_bin, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = help_bin),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = help_bin,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Emotional")

emmeans.plot
```


### Hyperactivity problems{.tabset}

#### Close relationships

```{r}
fit = lmer(Dsdhy1 ~ MdSNpf10*age.cent + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r results='asis'}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*MdSNpf10, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = MdSNpf10),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = MdSNpf10,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Hyperactivity")

emmeans.plot
```

#### Enough help

```{r}
fit = lmer(Dsdhy1 ~ MdSNsp01*age.cent + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r results='asis'}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*MdSNsp01, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = MdSNsp01),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = MdSNsp01,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Hyperactivity")

emmeans.plot
```

#### Binary help

```{r}
fit = lmer(Dsdhy1 ~ help_bin*age.cent + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r results='asis'}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*help_bin, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = help_bin),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = help_bin,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Hyperactivity")

emmeans.plot
```

### Peer problems {.tabset}

#### Close relationships


```{r}
fit = lmer(Dsdpr1 ~ MdSNpf10*age.cent + MdSNpf10*I(age.cent^2) + MdSNpf10*I(age.cent^3) + MdSNpf10*I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r results='asis'}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*MdSNpf10 + I(age.cent^2)*MdSNpf10 + I(age.cent^3)*MdSNpf10 + MdSNpf10*I(age.cent^4), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = MdSNpf10),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = MdSNpf10,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Peer Problems")

emmeans.plot
```

#### Enough help

```{r}
fit = lmer(Dsdpr1 ~ MdSNsp01*age.cent + MdSNsp01*I(age.cent^2) + MdSNsp01*I(age.cent^3) + MdSNsp01*I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r results='asis'}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*MdSNsp01 + I(age.cent^2)*MdSNsp01 + I(age.cent^3)*MdSNsp01 + MdSNsp01*I(age.cent^4), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = MdSNsp01),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = MdSNsp01,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Peer Problems")

emmeans.plot
```


#### Binary help

```{r}
fit = lmer(Dsdpr1 ~ help_bin*age.cent + help_bin*I(age.cent^2) + help_bin*I(age.cent^3) + help_bin*I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r results='asis'}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*help_bin + I(age.cent^2)*help_bin + I(age.cent^3)*help_bin, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = help_bin),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = help_bin,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Peer Problems")

emmeans.plot
```
