---
title: "SDQ trajectories"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
---

Identifying which polynomial terms to include in longitudinal models of SDQ domains for the whole sample and for males and females separately. This code fits multiple longitudinal models for each SDQ domain and performs model comparisons to compare fit metrics e.g. AIC, BIC.\
   
Linear model: SDQ ~ age.cent + (1 + age.cent | Idnumber)\
Quadratic model: SDQ ~ age.cent + age.cent^2 + (1 + age.cent | Idnumber)\
Cubic model:  SDQ ~ age.cent + age.cent^2 + age.cent^3 + (1 + age.cent | Idnumber)\
Quartic model:  SDQ ~ age.cent + age.cent^2 + age.cent^3 + age.cent^4 + (1 + age.cent | Idnumber)\
  
After identifying the best-fitting model, change the code in each "Plot model" to the corresponding trajectory model to plot the model and overlay the raw data.\
  
Input data (dat) should be in long format, with the following variables (at minimum):\

Idnumber - participant ID\
sweep - identifier for each timepoint\
Age - age\
age.cent - mean-centred age (helpful for reducing convergence issues)\
Sex - sex (could be sex at birth, could be gender identity - in this analysis it's a binary measure)\
Dsdco1 - SDQ conduct problems score\
Dsdem1 - SDQ emotional problems score\
Dsdhy1 - SDQ hyperactivity score\
Dsdpr1 - SDQ peer problems score\
Djwtbth2a - sample weight (delete the 'weights = Djwtbth2a,' line for each model if not using weights)\

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
```

```{r load packages}
library(lme4)
library(lmerTest)
library(tidyverse)
library(performance)
library(emmeans)
library(kableExtra)
emm_options(lmerTest.limit = 20000, pbkrtest.limit = 20000)
```

```{r}
# function to print any singular fit and convergence issues warning messages.
check_fit <- function(m) {
  msg = summary(m)$optinfo$conv$lme4$messages %>% unlist()
  if (any(grepl("isSingular", msg))==T) {
    print("Singular fit")
  } else {print("No singular fit")}
  
  if (any(grepl("failed to converge", msg))==T) {
    print("Failed to converge")
  } else  {print("No convergence issues")}
  } 
```

# Full sample {.tabset}

```{r read data, results='asis'}
dat = readRDS("G://users/eileen/Food_Ins/DATA/wt_GUS_long.rds")

sumtable = dat %>% group_by(across(sweep)) %>%
          summarise(N = n(),
                    age = mean(Age, na.rm = T),
                    ConductM = mean(Dsdco1, na.rm = T),
                    ConductSD = sd(Dsdco1, na.rm = T),
                    EmotM = mean(Dsdem1, na.rm = T),
                    EmotSD = sd(Dsdem1, na.rm = T),
                    HyperM = mean(Dsdhy1, na.rm=T),
                    HyperSD = sd(Dsdhy1, na.rm=T),
                    PeerM = mean(Dsdpr1, na.rm=T),
                    PeerSD = sd(Dsdpr1, na.rm=T)
          )

kbl(sumtable) %>%
  kable_styling(full_width = F)
```

## Conduct problems

### Fit models

```{r}
linfit = lmer(Dsdco1 ~ age.cent + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))


quadfit = lmer(Dsdco1 ~ age.cent + I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))


cubfit = lmer(Dsdco1 ~ age.cent + I(age.cent^2) + I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quartfit = lmer(Dsdco1 ~ age.cent + I(age.cent^2) + I(age.cent^3) +I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
print("Linear model")
check_fit(linfit)
print("Quadratic model")
check_fit(quadfit)
print("Cubic model")
check_fit(cubfit)
print("Quartic model")
check_fit(quartfit)

anova(linfit, quadfit, cubfit, quartfit) %>% as.data.frame() %>% 
  kbl() %>% kable_styling(full_width = F)
```


### Plot model (Quadratic; Cubic model as dashed line)

```{r}
rm(linfit, quartfit)

#---------- make df of original data ----------
df.plot = dat %>%
  group_by(across(sweep)) %>%
  summarise(Age = mean(Age, na.rm = T),
            Phenotype = mean(Dsdco1, na.rm = T),
            SD = sd(Dsdco1, na.rm = T),
            n = sum(!is.na(Dsdco1))) %>%
  mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
         lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))

#---------- plot ---------------
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model

emm = emmeans(quadfit, specs = ~ age.cent + I(age.cent^2) , 
              at = list(age.cent = age_cent), 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#--- original cubic model ----
emm2 = emmeans(cubfit, specs = ~ age.cent + I(age.cent^2) + I(age.cent^3), 
              at = list(age.cent = age_cent), 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred2 = as.data.frame(summary(emm2)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean),
            linewidth = 1.5, na.rm = T, colour = "#0072B2") + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T, fill = "#0072B2") +
  geom_line(data = pred2,
            aes(x = age_vals, y = emmean),
            linewidth = 1, na.rm = T, colour = "black", linetype="dashed") +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Conduct")

emmeans.plot
```


## Emotional problems

### Fit models

```{r}
linfit = lmer(Dsdem1 ~ age.cent + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quadfit = lmer(Dsdem1 ~ age.cent + I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

cubfit = lmer(Dsdem1 ~ age.cent + I(age.cent^2) + I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quartfit = lmer(Dsdem1 ~ age.cent + I(age.cent^2) + I(age.cent^3) +I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

print("Linear model")
check_fit(linfit)
print("Quadratic model")
check_fit(quadfit)
print("Cubic model")
check_fit(cubfit)
print("Quartic model")
check_fit(quartfit)

anova(linfit, quadfit, cubfit, quartfit) %>% as.data.frame() %>% 
  kbl() %>% kable_styling(full_width = F)
```

### Plot model (Cubic)

```{r}
rm(linfit, quadfit, quartfit)

#---------- make df of original data ----------
df.plot = dat %>%
  group_by(across(sweep)) %>%
  summarise(Age = mean(Age, na.rm = T),
            Phenotype = mean(Dsdem1, na.rm = T),
            SD = sd(Dsdem1, na.rm = T),
            n = sum(!is.na(Dsdem1))) %>%
  mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
         lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))

#---------- plot ---------------
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model

emm = emmeans(cubfit, specs = ~ age.cent + I(age.cent^2) + I(age.cent^3), 
              at = list(age.cent = age_cent), 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean),
            linewidth = 1.5, na.rm = T, colour = "#0072B2") + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T, fill = "#0072B2") +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Emotional")

emmeans.plot
```

## Hyperactivity

### Fit models

```{r}
linfit = lmer(Dsdhy1 ~ age.cent + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quadfit = lmer(Dsdhy1 ~ age.cent + I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

cubfit = lmer(Dsdhy1 ~ age.cent + I(age.cent^2) + I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quartfit = lmer(Dsdhy1 ~ age.cent + I(age.cent^2) + I(age.cent^3) +I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

print("Linear model")
check_fit(linfit)
print("Quadratic model")
check_fit(quadfit)
print("Cubic model")
check_fit(cubfit)
print("Quartic model")
check_fit(quartfit)

anova(linfit, quadfit, cubfit, quartfit) %>% as.data.frame() %>% 
  kbl() %>% kable_styling(full_width = F)
```

### Plot model (Linear)


```{r}
rm(quadfit, cubfit, quartfit)
#---------- make df of original data ----------
df.plot = dat %>%
  group_by(across(sweep)) %>%
  summarise(Age = mean(Age, na.rm = T),
            Phenotype = mean(Dsdhy1, na.rm = T),
            SD = sd(Dsdhy1, na.rm = T),
            n = sum(!is.na(Dsdhy1))) %>%
  mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
         lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))

#---------- plot ---------------
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model

emm = emmeans(linfit, specs = ~ age.cent, 
              at = list(age.cent = age_cent), 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean),
            linewidth = 1.5, na.rm = T, colour = "#0072B2") + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T, fill = "#0072B2") +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Hyperactivity")

emmeans.plot
```

## Peer problems

### Fit models

```{r}
linfit = lmer(Dsdpr1 ~ age.cent + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quadfit = lmer(Dsdpr1 ~ age.cent + I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

cubfit = lmer(Dsdpr1 ~ age.cent + I(age.cent^2) + I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quartfit = lmer(Dsdpr1 ~ age.cent + I(age.cent^2) + I(age.cent^3) +I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
print("Linear model")
check_fit(linfit)
print("Quadratic model")
check_fit(quadfit)
print("Cubic model")
check_fit(cubfit)
print("Quartic model")
check_fit(quartfit)

anova(linfit, quadfit, cubfit, quartfit) %>% as.data.frame() %>% 
  kbl() %>% kable_styling(full_width = F)
```

### Plot model (Quartic)


```{r}
rm(linfit, quadfit, cubfit)
#---------- make df of original data ----------
df.plot = dat %>%
  group_by(across(sweep)) %>%
  summarise(Age = mean(Age, na.rm = T),
            Phenotype = mean(Dsdpr1, na.rm = T),
            SD = sd(Dsdpr1, na.rm = T),
            n = sum(!is.na(Dsdpr1))) %>%
  mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
         lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))

#---------- plot ---------------
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model

emm = emmeans(quartfit, specs = ~ age.cent + I(age.cent^2) + I(age.cent^3) + I(age.cent^4), 
              at = list(age.cent = age_cent), 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean),
            linewidth = 1.5, na.rm = T, colour = "#0072B2") + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T, fill = "#0072B2") +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Peer Problems")

emmeans.plot
```


# Male only {.tabset}

```{r subset male}
rm(list = names(which(!unlist(eapply(.GlobalEnv, 
    \(x) inherits(x, what = "function"))))))

dat = readRDS("G://users/eileen/Food_Ins/DATA/wt_GUS_long.rds")
dat = dat %>% filter(Sex == "M")
```

## Conduct problems

### Fit models

```{r}
linfit = lmer(Dsdco1 ~ age.cent + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quadfit = lmer(Dsdco1 ~ age.cent + I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

cubfit = lmer(Dsdco1 ~ age.cent + I(age.cent^2) + I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quartfit = lmer(Dsdco1 ~ age.cent + I(age.cent^2) + I(age.cent^3) +I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

print("Linear model")
check_fit(linfit)
print("Quadratic model")
check_fit(quadfit)
print("Cubic model")
check_fit(cubfit)
print("Quartic model")
check_fit(quartfit)
anova(linfit, quadfit, cubfit, quartfit) %>% as.data.frame() %>% 
  kbl() %>% kable_styling(full_width = F)
```

### Plot model (Quadratic)

```{r}
rm(linfit, cubfit, quartfit)
#---------- make df of original data ----------
df.plot = dat %>%
  group_by(across(sweep)) %>%
  summarise(Age = mean(Age, na.rm = T),
            Phenotype = mean(Dsdco1, na.rm = T),
            SD = sd(Dsdco1, na.rm = T),
            n = sum(!is.na(Dsdco1))) %>%
  mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
         lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))

#---------- plot ---------------
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model

emm = emmeans(quadfit, specs = ~ age.cent + I(age.cent^2), 
              at = list(age.cent = age_cent), 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean),
            linewidth = 1.5, na.rm = T, colour = "#0072B2") + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T, fill = "#0072B2") +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Conduct")

emmeans.plot
```


## Emotional problems

### Fit models

```{r}
linfit = lmer(Dsdem1 ~ age.cent + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quadfit = lmer(Dsdem1 ~ age.cent + I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

cubfit = lmer(Dsdem1 ~ age.cent + I(age.cent^2) + I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quartfit = lmer(Dsdem1 ~ age.cent + I(age.cent^2) + I(age.cent^3) +I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

print("Linear model")
check_fit(linfit)
print("Quadratic model")
check_fit(quadfit)
print("Cubic model")
check_fit(cubfit)
print("Quartic model")
check_fit(quartfit)

anova(linfit, quadfit, cubfit, quartfit) %>% as.data.frame() %>% 
  kbl() %>% kable_styling(full_width = F)

```

### Plot model (Cubic)


```{r}
rm(linfit, quadfit, quartfit)
#---------- make df of original data ----------
df.plot = dat %>%
  group_by(across(sweep)) %>%
  summarise(Age = mean(Age, na.rm = T),
            Phenotype = mean(Dsdem1, na.rm = T),
            SD = sd(Dsdem1, na.rm = T),
            n = sum(!is.na(Dsdem1))) %>%
  mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
         lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))

#---------- plot ---------------
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model

emm = emmeans(cubfit, specs = ~ age.cent + I(age.cent^2) + I(age.cent^3), 
              at = list(age.cent = age_cent), 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean),
            linewidth = 1.5, na.rm = T, colour = "#0072B2") + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T, fill = "#0072B2") +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Emotional")

emmeans.plot
```

## Hyperactivity

Quartic is suggested by LRT, but from BIC the linear model is better (and simpler) so we go with linear.

### Fit models

```{r}
linfit = lmer(Dsdhy1 ~ age.cent + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quadfit = lmer(Dsdhy1 ~ age.cent + I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

cubfit = lmer(Dsdhy1 ~ age.cent + I(age.cent^2) + I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quartfit = lmer(Dsdhy1 ~ age.cent + I(age.cent^2) + I(age.cent^3) +I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
print("Linear model")
check_fit(linfit)
print("Quadratic model")
check_fit(quadfit)
print("Cubic model")
check_fit(cubfit)
print("Quartic model")
check_fit(quartfit)

anova(linfit, quadfit, cubfit, quartfit) %>% as.data.frame() %>% 
  kbl() %>% kable_styling(full_width = F)

```

### Plot model (Linear)


```{r}
rm(cubfit, quadfit, quartfit)
#---------- make df of original data ----------
df.plot = dat %>%
  group_by(across(sweep)) %>%
  summarise(Age = mean(Age, na.rm = T),
            Phenotype = mean(Dsdhy1, na.rm = T),
            SD = sd(Dsdhy1, na.rm = T),
            n = sum(!is.na(Dsdhy1))) %>%
  mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
         lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))

#---------- plot ---------------
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model

emm = emmeans(linfit, specs = ~ age.cent, 
              at = list(age.cent = age_cent), 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean),
            linewidth = 1.5, na.rm = T, colour = "#0072B2") + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T, fill = "#0072B2") +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Hyperactivity")

emmeans.plot
```

## Peer problems

### Fit models

```{r}
linfit = lmer(Dsdpr1 ~ age.cent + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quadfit = lmer(Dsdpr1 ~ age.cent + I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

cubfit = lmer(Dsdpr1 ~ age.cent + I(age.cent^2) + I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quartfit = lmer(Dsdpr1 ~ age.cent + I(age.cent^2) + I(age.cent^3) +I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
print("Linear model")
check_fit(linfit)
print("Quadratic model")
check_fit(quadfit)
print("Cubic model")
check_fit(cubfit)
print("Quartic model")
check_fit(quartfit)

anova(linfit, quadfit, cubfit, quartfit) %>% as.data.frame() %>% 
  kbl() %>% kable_styling(full_width = F)
```

### Plot model (Cubic)

```{r}

rm(linfit, quadfit, quartfit)
#---------- make df of original data ----------
df.plot = dat %>%
  group_by(across(sweep)) %>%
  summarise(Age = mean(Age, na.rm = T),
            Phenotype = mean(Dsdpr1, na.rm = T),
            SD = sd(Dsdpr1, na.rm = T),
            n = sum(!is.na(Dsdpr1))) %>%
  mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
         lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))

#---------- plot ---------------
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model

emm = emmeans(cubfit, specs = ~ age.cent + I(age.cent^2) + I(age.cent^3), 
              at = list(age.cent = age_cent), 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean),
            linewidth = 1.5, na.rm = T, colour = "#0072B2") + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T, fill = "#0072B2") +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Peer Problems")

emmeans.plot
```

# Female only {.tabset}

```{r}
rm(list = names(which(!unlist(eapply(.GlobalEnv, 
    \(x) inherits(x, what = "function"))))))

dat = readRDS("G://users/eileen/Food_Ins/DATA/wt_GUS_long.rds")
dat = dat %>% filter(Sex == "F")
```


## Conduct problems

Weighted analyses suggest quadratic model instead of cubic.

### Fit models

```{r}
linfit = lmer(Dsdco1 ~ age.cent + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quadfit = lmer(Dsdco1 ~ age.cent + I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

cubfit = lmer(Dsdco1 ~ age.cent + I(age.cent^2) + I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quartfit = lmer(Dsdco1 ~ age.cent + I(age.cent^2) + I(age.cent^3) +I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
print("Linear model")
check_fit(linfit)
print("Quadratic model")
check_fit(quadfit)
print("Cubic model")
check_fit(cubfit)
print("Quartic model")
check_fit(quartfit)

anova(linfit, quadfit, cubfit, quartfit) %>% as.data.frame() %>% 
  kbl() %>% kable_styling(full_width = F)
```

### Plot model (Quadratic; Cubic model as dashed line)


```{r}
rm(linfit, quartfit)

#---------- make df of original data ----------
df.plot = dat %>%
  group_by(across(sweep)) %>%
  summarise(Age = mean(Age, na.rm = T),
            Phenotype = mean(Dsdco1, na.rm = T),
            SD = sd(Dsdco1, na.rm = T),
            n = sum(!is.na(Dsdco1))) %>%
  mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
         lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))

#---------- plot ---------------
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model

emm = emmeans(quadfit, specs = ~ age.cent + I(age.cent^2) , 
              at = list(age.cent = age_cent), 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#--- original cubic model ----
emm2 = emmeans(cubfit, specs = ~ age.cent + I(age.cent^2) + I(age.cent^3), 
              at = list(age.cent = age_cent), 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred2 = as.data.frame(summary(emm2)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean),
            linewidth = 1.5, na.rm = T, colour = "#0072B2") + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T, fill = "#0072B2") +
  geom_line(data = pred2,
            aes(x = age_vals, y = emmean),
            linewidth = 1, na.rm = T, colour = "black", linetype="dashed") +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Conduct")

emmeans.plot
```


## Emotional problems

### Fit models

```{r}
linfit = lmer(Dsdem1 ~ age.cent + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quadfit = lmer(Dsdem1 ~ age.cent + I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

cubfit = lmer(Dsdem1 ~ age.cent + I(age.cent^2) + I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quartfit = lmer(Dsdem1 ~ age.cent + I(age.cent^2) + I(age.cent^3) +I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
print("Linear model")
check_fit(linfit)
print("Quadratic model")
check_fit(quadfit)
print("Cubic model")
check_fit(cubfit)
print("Quartic model")
check_fit(quartfit)

anova(linfit, quadfit, cubfit, quartfit) %>% as.data.frame() %>% 
  kbl() %>% kable_styling(full_width = F)
```

### Plot model (Linear)


```{r}
rm(quadfit, cubfit, quartfit)
#---------- make df of original data ----------
df.plot = dat %>%
  group_by(across(sweep)) %>%
  summarise(Age = mean(Age, na.rm = T),
            Phenotype = mean(Dsdem1, na.rm = T),
            SD = sd(Dsdem1, na.rm = T),
            n = sum(!is.na(Dsdem1))) %>%
  mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
         lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))

#---------- plot ---------------
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model

emm = emmeans(linfit, specs = ~ age.cent, 
              at = list(age.cent = age_cent), 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean),
            linewidth = 1.5, na.rm = T, colour = "#0072B2") + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T, fill = "#0072B2") +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Emotional")

emmeans.plot
```

## Hyperactivity

### Fit models

```{r}
linfit = lmer(Dsdhy1 ~ age.cent + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quadfit = lmer(Dsdhy1 ~ age.cent + I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

cubfit = lmer(Dsdhy1 ~ age.cent + I(age.cent^2) + I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quartfit = lmer(Dsdhy1 ~ age.cent + I(age.cent^2) + I(age.cent^3) +I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
print("Linear model")
check_fit(linfit)
print("Quadratic model")
check_fit(quadfit)
print("Cubic model")
check_fit(cubfit)
print("Quartic model")
check_fit(quartfit)
anova(linfit, quadfit, cubfit, quartfit) %>% as.data.frame() %>% 
  kbl() %>% kable_styling(full_width = F)

```

### Plot model (Quadratic)


```{r}
rm(linfit, cubfit, quartfit)
#---------- make df of original data ----------
df.plot = dat %>%
  group_by(across(sweep)) %>%
  summarise(Age = mean(Age, na.rm = T),
            Phenotype = mean(Dsdhy1, na.rm = T),
            SD = sd(Dsdhy1, na.rm = T),
            n = sum(!is.na(Dsdhy1))) %>%
  mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
         lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))

#---------- plot ---------------
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model

emm = emmeans(quadfit, specs = ~ age.cent + I(age.cent^2), 
              at = list(age.cent = age_cent), 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean),
            linewidth = 1.5, na.rm = T, colour = "#0072B2") + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T, fill = "#0072B2") +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Hyperactivity")

emmeans.plot
```

## Peer problems

### Fit models

```{r}
linfit = lmer(Dsdpr1 ~ age.cent + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quadfit = lmer(Dsdpr1 ~ age.cent + I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

cubfit = lmer(Dsdpr1 ~ age.cent + I(age.cent^2) + I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

quartfit = lmer(Dsdpr1 ~ age.cent + I(age.cent^2) + I(age.cent^3) +I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = FALSE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
print("Linear model")
check_fit(linfit)
print("Quadratic model")
check_fit(quadfit)
print("Cubic model")
check_fit(cubfit)
print("Quartic model")
check_fit(quartfit)
anova(linfit, quadfit, cubfit, quartfit) %>% as.data.frame() %>% 
  kbl() %>% kable_styling(full_width = F)
```

### Plot model (Quartic)

```{r}
rm(linfit, quadfit, cubfit)
#---------- make df of original data ----------
df.plot = dat %>%
  group_by(across(sweep)) %>%
  summarise(Age = mean(Age, na.rm = T),
            Phenotype = mean(Dsdpr1, na.rm = T),
            SD = sd(Dsdpr1, na.rm = T),
            n = sum(!is.na(Dsdpr1))) %>%
  mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
         lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))

#---------- plot ---------------
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model

emm = emmeans(quartfit, specs = ~ age.cent + I(age.cent^2) + I(age.cent^3) + I(age.cent^4), 
              at = list(age.cent = age_cent), 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean),
            linewidth = 1.5, na.rm = T, colour = "#0072B2") + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T, fill = "#0072B2") +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Peer Problems")

emmeans.plot
```