---
title: "ALSPAC_Diffs"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, results = "asis")
library(here)
i_am("ANALYSIS/ALSPAC/ALSPAC_FI.Rmd")
source(here("FUNS", "packages.R"))
```

```{r read data}
ALSPAC = readRDS(here("DATA", "ALSPAC_long.rds"))

FItab = table(ALSPAC$sweep, ALSPAC$foodDiff) |> as.matrix()
Agetab = ALSPAC |> group_by(across(sweep)) |> 
  summarise(N = n(), Age = age_ym(mean(Age, na.rm = T))) |> as.matrix()
cbind(Agetab, FItab) |> kbl() |> kable_styling(full_width = F)
```

# Compare SDQ scores in each sweep

## KQ {.tabset}

"Fairly difficult" and "Very difficult" groups differ in conduct problems, but not on any other SDQ subscales.

```{r}
kq = ALSPAC |> filter(sweep=="kq")
kq |> group_by(foodDiff) |> 
  summarise(conduct = m_sd(conduct),
            emot = m_sd(emot),
            hyper = m_sd(hyper),
            peer = m_sd(peer)) |> kable()

test = list("conduct"=kq$conduct, "emot"=kq$emot, 
            "hyper"=kq$hyper, "peer"=kq$peer) |> 
  map(\(x) pairwise.wilcox.test(x, kq$foodDiff)$p.value) # differences in conduct
```

### Conduct problems

```{r results='asis'}
test[1] |> kable()
```

### Emotional problems

```{r results='asis'}
test[2] |> kable()
```

### Hyperactivity problems

```{r results='asis'}
test[3] |> kable()
```

### Peer problems

```{r results='asis'}
test[4] |> kable()
```

## KU {.tabset}

"Fairly difficult" and "Very difficult" groups do not differ in score for any SDQ

```{r}
ku = ALSPAC |> filter(sweep=="ku")
ku |> group_by(foodDiff) |> 
  summarise(conduct = m_sd(conduct),
            emot = m_sd(emot),
            hyper = m_sd(hyper),
            peer = m_sd(peer)) |> kbl() |> kable_styling()

test = list("conduct"=ku$conduct, "emot"=ku$emot, 
            "hyper"=ku$hyper, "peer"=ku$peer) |> 
  map(\(x) pairwise.wilcox.test(x, ku$foodDiff)$p.value)
```

### Conduct problems

```{r results='asis'}
test[1] |> kable()
```

### Emotional problems

```{r results='asis'}
test[2] |> kable()
```

### Hyperactivity problems

```{r results='asis'}
test[3] |> kable()
```

### Peer problems

```{r results='asis'}
test[4] |> kable()
```

## KW {.tabset}

"Fairly difficult" and "Very difficult" groups do not differ

```{r}
kw = ALSPAC |> filter(sweep=="kw")
kw |> group_by(foodDiff) |> 
  summarise(conduct = m_sd(conduct),
            emot = m_sd(emot),
            hyper = m_sd(hyper),
            peer = m_sd(peer)) |> kbl() |> kable_styling()

test = list("conduct"=kw$conduct, "emot"=kw$emot, 
            "hyper"=kw$hyper, "peer"=kw$peer) |> 
  map(\(x) pairwise.wilcox.test(x, kw$foodDiff)$p.value)
```

### Conduct problems

```{r results='asis'}
test[1] |> kable()
```

### Emotional problems

```{r results='asis'}
test[2] |> kable()
```

### Hyperactivity problems

```{r results='asis'}
test[3] |> kable()
```

### Peer problems

```{r results='asis'}
test[4] |> kable()
```

## TA {.tabset}

"Fairly difficult" and "Very difficult" groups do not differ

```{r}
ta = ALSPAC |> filter(sweep=="ta")
ta |> group_by(foodDiff) |> 
  summarise(conduct = m_sd(conduct),
            emot = m_sd(emot),
            hyper = m_sd(hyper),
            peer = m_sd(peer)) |> kbl() |> kable_styling()

test = list("conduct"=ta$conduct, "emot"=ta$emot, 
            "hyper"=ta$hyper, "peer"=ta$peer) |> 
  map(\(x) pairwise.wilcox.test(x, ta$foodDiff)$p.value)
```

### Conduct problems

```{r results='asis'}
test[1] |> kable()
```

### Emotional problems

```{r results='asis'}
test[2] |> kable()
```

### Hyperactivity problems

```{r results='asis'}
test[3] |> kable()
```

### Peer problems

```{r results='asis'}
test[4] |> kable()
```

## TC {.tabset}

"Fairly difficult" and "Very difficult" groups do not differ

```{r}
tc = ALSPAC |> filter(sweep=="tc")
tc |> group_by(foodDiff) |> 
  summarise(conduct = m_sd(conduct),
            emot = m_sd(emot),
            hyper = m_sd(hyper),
            peer = m_sd(peer)) |> kbl() |> kable_styling()

test = list("conduct"=tc$conduct, "emot"=tc$emot, 
            "hyper"=tc$hyper, "peer"=tc$peer) |> 
  map(\(x) pairwise.wilcox.test(x, tc$foodDiff)$p.value)
```

### Conduct problems

```{r results='asis'}
test[1] |> kable()
```

### Emotional problems

```{r results='asis'}
test[2] |> kable()
```

### Hyperactivity problems

```{r results='asis'}
test[3] |> kable()
```

### Peer problems

```{r results='asis'}
test[4] |> kable()
```

## Compare covariates

### Sex: 

```{r}
covars = ALSPAC |> select(ID, foodDiff, sex, income, epds, IMD) |> 
  unique()

table(covars$sex, covars$foodDiff) |> kable()
```

### Income:

```{r}
table(covars$income, covars$foodDiff) |> kable()
```

### Maternal MH:

```{r}
covars |> group_by(foodDiff) |> 
  summarise(N = n(), SF12 = m_sd(epds)) |> kbl() |> kable_styling()
```

### SIMD (1 = least deprived):

```{r}
table(covars$IMD, covars$foodDiff) |> kable()
```
