---
title: "Food insecurity x social support, split by sex"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
---

Fitting models of SDQ trajectories with food insecurity x parental social support. This script is split by sex, the full sample analysis is in "wtFI_SocialSupport_FullSample.Rmd". The polynomial terms included here may need to be edited depending on what best fits the data.\


Input data (dat) should be in long format, with the following variables:\


**food_help - 6-level factor combining 3-level food insecurity and binary social support**\
Idnumber - participant ID\
sweep - identifier for each timepoint\
Age - age\
age.cent - mean-centred age (helpful for reducing convergence issues)\
Sex - sex (could be sex at birth, could be gender identity - in this analysis it's a binary measure)\
Dsdco1 - SDQ conduct problems score\
Dsdem1 - SDQ emotional problems score\
Dsdhy1 - SDQ hyperactivity score\
Dsdpr1 - SDQ peer problems score\
Djwtbth2a - sample weight (delete the 'weights = Djwtbth2a,' line for each model if not using weights)\
MeFaff3lvl - 3-level food insecurity measure\
DeEqv5 - household income quintiles, adjusted for household composition (see GUS documentation deriving this)\
DeSf12mn - continuous maternal mental health score from SF-12\
ALeSNim2 - SIMD quintiles\


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, results = "asis", fig.width = 10)
source("ANALYSIS/global.R")
```


```{r}
dat = readRDS("G://users/eileen/Food_Ins/DATA/wt_GUS_social.rds")

age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent, DeEqv5 = levels(dat$DeEqv5))
```


```{r}
dat %>% distinct(Idnumber, .keep_all = T) %>% group_by(Sex) %>% 
  summarise(N = n(),
            Food_none = sum(MeFaff3lvl=="Not at all"),
            Food_little = sum(MeFaff3lvl=="A little"),
            Food_lot = sum(MeFaff3lvl=="A lot/fair amount"),
            Help_enough = sum(help_bin=="Enough"),
            Help_not_enough = sum(help_bin=="Not enough"),
            Food_none_Help_enough = sum(food_help=="Not at all.Enough"),
            Food_little.Help_enough = sum(food_help=="A little.Enough"),
            Food_lot.Help_enough = sum(food_help=="A lot/fair amount.Enough"),
            Food_none.Help_not_enough = sum(food_help=="Not at all.Not enough"),
            Food_little.Help_not_enough = sum(food_help=="A little.Not enough"),
            Food_lot.Help_not_enough = sum(food_help=="A lot/fair amount.Not enough")
            ) %>% t() %>% kbl() %>% kable_styling()

```

## Female only {.tabset}

```{r}
datF = dat %>% filter(Sex=="F")
```

### Conduct problems {.tabset}

#### No covariates

```{r}
fit = lmer(Dsdco1 ~ food_help*age.cent + food_help*I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML =TRUE ,
                 data = datF ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = ggplot() +
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Conduct")
  
fig + facet_grid(. ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

#### Plus income

```{r}
fit = lmer(Dsdco1 ~ food_help*age.cent + food_help*I(age.cent^2) + DeEqv5 + (1 + age.cent |Idnumber),
                 REML =TRUE ,
                 data = datF ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot by income

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help + DeEqv5, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == c("1", "5")) %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Conduct")

fig + facet_grid(DeEqv5 ~factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

### Emotional problems {.tabset}

#### No covariates

```{r}
fit = lmer(Dsdem1 ~ food_help*age.cent + (1 + age.cent |Idnumber),
                 REML =TRUE ,
                 data = datF ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = ggplot() +
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Emotional ")
  
fig + facet_grid(. ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

#### Plus income

```{r}
fit = lmer(Dsdem1 ~ food_help*age.cent + DeEqv5 + (1 + age.cent |Idnumber),
                 REML =TRUE ,
                 data = datF ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot by income

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help + DeEqv5, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == c("1", "5")) %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Emotional")

fig + facet_grid(DeEqv5 ~factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

### Hyperactivity {.tabset}

#### No covariates

```{r}
fit = lmer(Dsdhy1 ~ food_help*age.cent + food_help*I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML =TRUE ,
                 data = datF ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Hyperactivity ")
  
fig + facet_grid(. ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

#### Plus income

```{r}
fit = lmer(Dsdhy1 ~ food_help*age.cent + food_help*I(age.cent^2) + DeEqv5 + (1 + age.cent |Idnumber),
                 REML =TRUE ,
                 data = datF ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot by income

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help + DeEqv5, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == c("1", "5")) %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Hyperactivity")
  
fig + facet_grid(DeEqv5 ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

### Peer problems {.tabset}

#### No covariates

```{r}
fit = lmer(Dsdpr1 ~ age.cent*food_help + I(age.cent^2)*food_help + I(age.cent^3)*food_help + I(age.cent^4)*food_help + (1 + age.cent |Idnumber),
                 REML =TRUE ,
                 data = datF ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help + I(age.cent^3)*food_help +I(age.cent^4)*food_help, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Peer Problems")
  
fig + facet_grid(. ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

#### Plus income

```{r}
fit = lmer(Dsdpr1 ~ age.cent*food_help + I(age.cent^2)*food_help + I(age.cent^3)*food_help +I(age.cent^4)*food_help + DeEqv5 + 
             (1 + age.cent |Idnumber),
                 REML =TRUE ,
                 data = datF ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot by income

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help + I(age.cent^3)*food_help +I(age.cent^4)*food_help + DeEqv5, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == c("1", "5")) %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Peer Problems")
  
fig + facet_grid(DeEqv5 ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```


## Male only {.tabset}

```{r}
datM = dat %>% filter(Sex=="M")
```

### Conduct problems {.tabset}

#### No covariates

```{r}
fit = lmer(Dsdco1 ~ food_help*age.cent + food_help*I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML =TRUE ,
                 data = datM ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = ggplot() +
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Conduct")
  
fig + facet_grid(. ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

#### Plus income

```{r}
fit = lmer(Dsdco1 ~ food_help*age.cent + food_help*I(age.cent^2) + DeEqv5 + (1 + age.cent |Idnumber),
                 REML =TRUE ,
                 data = datF ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot by income

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help + DeEqv5, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == c("1", "5")) %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Conduct")

fig + facet_grid(DeEqv5 ~factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

### Emotional problems {.tabset}

#### No covariates

```{r}
fit = lmer(Dsdem1 ~ food_help*age.cent + food_help*I(age.cent^2) + food_help*I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML =TRUE ,
                 data = datM ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot

```{r}
emm = emmeans(fit, specs = ~ food_help*age.cent + food_help*I(age.cent^2) + food_help*I(age.cent^3), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = ggplot() +
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Emotional ")
  
fig + facet_grid(. ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

#### Plus income

```{r}
fit = lmer(Dsdem1 ~ food_help*age.cent + food_help*I(age.cent^2) + food_help*I(age.cent^3) + DeEqv5 + (1 + age.cent |Idnumber),
                 REML =TRUE ,
                 data = datM ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot by income

```{r}
emm = emmeans(fit, specs = ~ food_help*age.cent + food_help*I(age.cent^2) + food_help*I(age.cent^3) + DeEqv5, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == c("1", "5")) %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Emotional")

fig + facet_grid(DeEqv5 ~factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

### Hyperactivity {.tabset}

#### No covariates

```{r}
fit = lmer(Dsdhy1 ~ food_help*age.cent + (1 + age.cent |Idnumber),
                 REML =TRUE ,
                 data = datM ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Hyperactivity ")
  
fig + facet_grid(. ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

#### Plus income

```{r}
fit = lmer(Dsdhy1 ~ food_help*age.cent + DeEqv5 + (1 + age.cent |Idnumber),
                 REML =TRUE ,
                 data = datM ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot by income

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help + DeEqv5, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == c("1", "5")) %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Hyperactivity")
  
fig + facet_grid(DeEqv5 ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

### Peer problems {.tabset}

#### No covariates

```{r}
fit = lmer(Dsdpr1 ~ age.cent*food_help + I(age.cent^2)*food_help + I(age.cent^3)*food_help + (1 + age.cent |Idnumber),
                 REML =TRUE ,
                 data = datM ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help + I(age.cent^3)*food_help, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Peer Problems")
  
fig + facet_grid(. ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

#### Plus income

```{r}
fit = lmer(Dsdpr1 ~ age.cent*food_help + I(age.cent^2)*food_help + I(age.cent^3)*food_help + DeEqv5 + 
             (1 + age.cent |Idnumber),
                 REML =TRUE ,
                 data = datM ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot by income

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help + I(age.cent^3)*food_help + DeEqv5, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == c("1", "5")) %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Peer Problems")
  
fig + facet_grid(DeEqv5 ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```