---
title: "ALSPAC SDQ trajectories (age only)"
output:
  github_document:
    toc: true
    toc_depth: 2
    df_print: "paged"
---

Identifying which polynomial terms to include in longitudinal models of SDQ domains for the whole sample and for males and females separately. This code fits 4 models for each SDQ domain and performs model comparisons to compare fit metrics e.g. AIC, BIC.\
   
Linear model: SDQ ~ age.cent + (1 + age.cent | ID)\
Quadratic model: SDQ ~ age.cent + age.cent^2 + (1 + age.cent | ID)\
Cubic model:  SDQ ~ age.cent + age.cent^2 + age.cent^3 + (1 + age.cent | ID)\
Quartic model:  SDQ ~ age.cent + age.cent^2 + age.cent^3 + age.cent^4 + (1 + age.cent | ID)\
  
Input data (dat) should be in long format, with the following variables (at minimum):\

- unique participant ID\
- identifier for each timepoint\
- age in years\
- mean-centred age (helpful for reducing convergence issues)\
- sex (could be sex at birth, could be gender identity - in this analysis it's a binary measure)\
- SDQ scores (conduct, emotional problems, hyperactivity, peer problems)\

Optionally, dat can include sample weights too.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
library(here)
i_am("ANALYSIS/ALSPAC/ALSPAC_Age_Only.Rmd")
source(here("FUNS", "packages.R"))
source(here("FUNS", "mods.R"))
source(here("FUNS", "plot.R"))
```

# Full sample {.tabset}

```{r read data, results='asis'}
dat = readRDS("G://users/eileen/Food_Ins/DATA/ALSPAC_long.rds")

sumtable = dat %>% group_by(across(sweep)) %>%
          summarise(N = n(),
                    age = m_sd(Age),
                    Conduct = m_sd(conduct),
                    Emot = m_sd(emot),
                    Hyper = m_sd(hyper),
                    Peer = m_sd(peer))

kbl(sumtable) %>%
  kable_styling(full_width = F)

modTypes = c("linear", "quadratic", "cubic", "quartic")
```

## Conduct problems

### Fit models

```{r}
conduct_fits = modTypes |> 
  map(\(x) fit_lmer(dat = dat, outcome ="conduct", age = "age.cent",
                  id = "ID", wt = dat$ipw, modType = x)) |> `names<-`(modTypes)

fits = conduct_fits |> list_transpose(template = "fit")  |>  unlist()

do.call(anova, unname(fits)) |>  as.data.frame() |>  
  `rownames<-`(modTypes) |> kbl()  |>  kable_styling(full_width = F)
```

### Plot model (Cubic)

```{r}
plotdat = plot_dfs(dat = dat, obj = conduct_fits$cubic, sw = "sweep", age_y = "Age")

emmeans.plot = traj_plot(plotdat) + scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Conduct")
emmeans.plot
```

## Emotional problems

### Fit models

```{r}
emot_fits = modTypes |> 
  map(\(x) fit_lmer(dat = dat, outcome ="emot", age = "age.cent",
                  id = "ID", wt = dat$ipw, modType = x)) |> `names<-`(modTypes)

fits = emot_fits |> list_transpose(template = "fit")  |>  unlist()

do.call(anova, unname(fits)) |>  as.data.frame() |>  
  `rownames<-`(modTypes) |> kbl()  |>  kable_styling(full_width = F)
```

### Plot model (Cubic)

```{r}
plotdat = plot_dfs(dat = dat, obj = emot_fits$cubic, sw = "sweep", age_y = "Age")

emmeans.plot = traj_plot(plotdat) + scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Emotional")
emmeans.plot
```


## Hyperactivity

### Fit models

```{r}
hyper_fits = modTypes |> 
  map(\(x) fit_lmer(dat = dat, outcome ="hyper", age = "age.cent",
                  id = "ID", wt = dat$ipw, modType = x)) |> `names<-`(modTypes)

fits = hyper_fits |> list_transpose(template = "fit")  |>  unlist()

do.call(anova, unname(fits)) |>  as.data.frame() |>  
  `rownames<-`(modTypes) |> kbl()  |>  kable_styling(full_width = F)
```


### Plot model (Quartic)

```{r}
plotdat = plot_dfs(dat = dat, obj = hyper_fits$quartic, sw = "sweep", age_y = "Age")

emmeans.plot = traj_plot(plotdat) + scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Hyperactivity")
emmeans.plot
```


## Peer problems

### Fit models

```{r}
peer_fits = modTypes |> 
  map(\(x) fit_lmer(dat = dat, outcome ="peer", age = "age.cent",
                  id = "ID", wt = dat$ipw, modType = x)) |> `names<-`(modTypes)

fits = peer_fits |> list_transpose(template = "fit")  |>  unlist()

do.call(anova, unname(fits)) |>  as.data.frame() |>  
  `rownames<-`(modTypes) |> kbl()  |>  kable_styling(full_width = F)
```

### Plot model (Quartic)

```{r}
plotdat = plot_dfs(dat = dat, obj = peer_fits$quartic, sw = "sweep", age_y = "Age")

emmeans.plot = traj_plot(plotdat) + scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Peer")
emmeans.plot
```


# Male only {.tabset}

```{r subset male}
dat.m = dat %>% filter(sex == "Male")
dat.m$age.cent = dat.m$Age - mean(dat.m$Age)
```

## Conduct problems

### Fit models

```{r}
conduct_fits = modTypes |> 
  map(\(x) fit_lmer(dat = dat.m, outcome ="conduct", age = "age.cent",
                  id = "ID", wt = dat.m$ipw, modType = x)) |> `names<-`(modTypes)

fits = conduct_fits |> list_transpose(template = "fit")  |>  unlist()

do.call(anova, unname(fits)) |>  as.data.frame() |>  
  `rownames<-`(modTypes) |> kbl()  |>  kable_styling(full_width = F)
```

### Plot model (Cubic)

```{r}
plotdat = plot_dfs(dat = dat.m, obj = conduct_fits$cubic, sw = "sweep", age_y = "Age")

emmeans.plot = traj_plot(plotdat) + scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Conduct")
emmeans.plot
```

## Emotional problems

### Fit models

```{r}
emot_fits = modTypes |> 
  map(\(x) fit_lmer(dat = dat.m, outcome ="emot", age = "age.cent",
                  id = "ID", wt = dat.m$ipw, modType = x)) |> `names<-`(modTypes)

fits = emot_fits |> list_transpose(template = "fit")  |>  unlist()

do.call(anova, unname(fits)) |>  as.data.frame() |>  
  `rownames<-`(modTypes) |> kbl()  |>  kable_styling(full_width = F)
```

### Plot model (Quadratic)

```{r}
plotdat = plot_dfs(dat = dat.m, obj = emot_fits$quadratic, sw = "sweep", age_y = "Age")

emmeans.plot = traj_plot(plotdat) + scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Emotional")
emmeans.plot
```

## Hyperactivity

### Fit models

```{r}
hyper_fits = modTypes |> 
  map(\(x) fit_lmer(dat = dat.m, outcome ="hyper", age = "age.cent",
                  id = "ID", wt = dat.m$ipw, modType = x)) |> `names<-`(modTypes)

fits = hyper_fits |> list_transpose(template = "fit")  |>  unlist()

do.call(anova, unname(fits)) |>  as.data.frame() |>  
  `rownames<-`(modTypes) |> kbl()  |>  kable_styling(full_width = F)
```

### Plot model (Cubic)

```{r}
plotdat = plot_dfs(dat = dat.m, obj = hyper_fits$cubic, sw = "sweep", age_y = "Age")

emmeans.plot = traj_plot(plotdat) + scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Hyperactivity")
emmeans.plot
```

## Peer problems

### Fit models

```{r}
peer_fits = modTypes |> 
  map(\(x) fit_lmer(dat = dat.m, outcome ="peer", age = "age.cent",
                  id = "ID", wt = dat.m$ipw, modType = x)) |> `names<-`(modTypes)

fits = peer_fits |> list_transpose(template = "fit")  |>  unlist()

do.call(anova, unname(fits)) |>  as.data.frame() |>  
  `rownames<-`(modTypes) |> kbl()  |>  kable_styling(full_width = F)
```

### Plot model (Quartic)

```{r}
plotdat = plot_dfs(dat = dat.m, obj = peer_fits$quartic, sw = "sweep", age_y = "Age")

emmeans.plot = traj_plot(plotdat) + scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Peer")
emmeans.plot
```

# Female only {.tabset}

```{r}
dat.f = dat %>% filter(sex == "Female")
dat.f$age.cent = dat.f$Age - mean(dat.f$Age)
```

## Conduct problems

### Fit models

```{r}
conduct_fits = modTypes |> 
  map(\(x) fit_lmer(dat = dat.f, outcome ="conduct", age = "age.cent",
                  id = "ID", wt = dat.f$ipw, modType = x)) |> `names<-`(modTypes)

fits = conduct_fits |> list_transpose(template = "fit")  |>  unlist()

do.call(anova, unname(fits)) |>  as.data.frame() |>  
  `rownames<-`(modTypes) |> kbl()  |>  kable_styling(full_width = F)
```

### Plot model (Cubic)

```{r}
plotdat = plot_dfs(dat = dat.f, obj = conduct_fits$cubic, sw = "sweep", age_y = "Age")

emmeans.plot = traj_plot(plotdat) + scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Conduct")
emmeans.plot
```


## Emotional problems

### Fit models

```{r}
emot_fits = modTypes |> 
  map(\(x) fit_lmer(dat = dat.f, outcome ="emot", age = "age.cent",
                  id = "ID", wt = dat.f$ipw, modType = x)) |> `names<-`(modTypes)

fits = emot_fits |> list_transpose(template = "fit")  |>  unlist()

do.call(anova, unname(fits)) |>  as.data.frame() |>  
  `rownames<-`(modTypes) |> kbl()  |>  kable_styling(full_width = F)
```

### Plot model (Cubic)

```{r}
plotdat = plot_dfs(dat = dat.f, obj = emot_fits$cubic, sw = "sweep", age_y = "Age")

emmeans.plot = traj_plot(plotdat) + scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Emotional")
emmeans.plot
```


## Hyperactivity

### Fit models

```{r}
hyper_fits = modTypes |> 
  map(\(x) fit_lmer(dat = dat.f, outcome ="hyper", age = "age.cent",
                  id = "ID", wt = dat.f$ipw, modType = x)) |> `names<-`(modTypes)

fits = hyper_fits |> list_transpose(template = "fit")  |>  unlist()

do.call(anova, unname(fits)) |>  as.data.frame() |>  
  `rownames<-`(modTypes) |> kbl()  |>  kable_styling(full_width = F)
```

### Plot model (Quartic)

```{r}
plotdat = plot_dfs(dat = dat.f, obj = hyper_fits$quartic, sw = "sweep", age_y = "Age")

emmeans.plot = traj_plot(plotdat) + scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Hyperactivity")
emmeans.plot
```


## Peer problems

### Fit models

```{r}
peer_fits = modTypes |> 
  map(\(x) fit_lmer(dat = dat.f, outcome ="peer", age = "age.cent",
                  id = "ID", wt = dat.f$ipw, modType = x)) |> `names<-`(modTypes)

fits = peer_fits |> list_transpose(template = "fit")  |>  unlist()

do.call(anova, unname(fits)) |>  as.data.frame() |>  
  `rownames<-`(modTypes) |> kbl()  |>  kable_styling(full_width = F)
```

### Plot model (Quadratic)

```{r}
plotdat = plot_dfs(dat = dat.f, obj = peer_fits$quadratic, sw = "sweep", age_y = "Age")

emmeans.plot = traj_plot(plotdat) + scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Peer")
emmeans.plot
```