---
title: "ALSPAC Food Insecurity and SDQ trajectories"
output:
  html_document:
    toc: true
    toc_depth: 2
    code_folding: hide
---

Fitting models of SDQ trajectories with food insecurity at age 5 as a 3-level factor. The polynomial terms included here may need to be edited depending on what best fits the data.\

Input data (dat) should be in long format, with the following variables (at minimum):\

Participant ID\
Identifier for each timepoint\
Age (in years)\
Mean-centred age (helpful for reducing convergence issues)\
Sex (could be sex at birth, could be gender identity - in this analysis it's a binary measure)\
SDQ conduct problems score\
SDQ emotional problems score\
SDQ hyperactivity score\
SDQ peer problems score\
Sample weight (delete the 'wt = ,' argument if not using weights)\
**3-level food insecurity measure**\
Household income\
Maternal MH score (continuous)\
IMD quintiles\

```{r, setup, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE, results = "asis")
library(here)
i_am("ANALYSIS/ALSPAC/ALSPAC_FI.Rmd")
source(here("FUNS", "packages.R"))
source(here("FUNS", "mods.R"))
source(here("FUNS", "plot.R"))
```

```{r read data}
dat = readRDS(here("DATA", "ALSPAC_long.rds"))

# setting reference levels
dat$income = factor(dat$income, ordered = FALSE) |> relevel(ref = ">400") # highest income as ref
dat$IMD = factor(dat$IMD, ordered=FALSE) |> relevel(ref = "1") #least deprived as ref

## setup for emmeans (emm_at)
# list of all categorical predictor levels to estimate. Maternal MH not included here as it's continuous and has a meaningful mean value so we can just get estimates for mean maternal MH score
emm_at = c(make_emm_at(age_y = dat$Age, agevar = "age.cent"), income = levels(dat$income), sex = levels(dat$sex), IMD = levels(dat$IMD)) 

## setup for model covariates
# 4 covariate structures
covars = list(NULL, c("sex", "income"), c("sex", "income", "epds"), c("sex", "income", "epds", "IMD"))

plot.unadjusted = list()
plot.adjusted = list()
```

**Mean age: `r mean(dat$Age)` years**

# Conduct problems {.tabset}

```{r}
conductfits = covars |> 
  map(\(x) fit_lmer(dat = dat, outcome ="conduct", age = "age.cent",
                  id = "ID", wt = dat$ipw, modType = "cubic",
                  grp = "foodDiff3", covs = x))
```

## No covariates

```{r results='asis'}
sjPlot::tab_model(conductfits[[1]]$fit)
print(conductfits[[1]]$diagnostics)

c.preds = get_preds(dat = dat, obj = conductfits[[1]], age_y = "Age", 
                    emm_at = emm_at, specs = c("age.cent", "foodDiff3"))

plot.unadjusted[["conduct"]] = traj_plot(c.preds, colour = "foodDiff3") + 
  scale_x_continuous(breaks = seq(6, 18, 3)) + ylab("SDQ Conduct") +
  xlab("Age (years)")

plot.unadjusted[["conduct"]]
```

## Covariates sex and income

```{r results='asis'}
sjPlot::tab_model(conductfits[[2]]$fit)
print(conductfits[[2]]$diagnostics)
```

## Covariates sex, income, maternal MH

```{r results='asis'}
sjPlot::tab_model(conductfits[[3]]$fit)
print(conductfits[[3]]$diagnostics)
```

## Covariates sex, income, maternal MH, IMD

```{r results='asis'}
sjPlot::tab_model(conductfits[[4]]$fit)
print(conductfits[[4]]$diagnostics)

c.adj = get_preds(dat = dat, obj = conductfits[[4]], age_y = "Age",
                specs = c("age.cent", "foodDiff3"), emm_at = emm_at,
                weights = "proportional")

plot.adjusted[["conduct"]] = traj_plot(pred.df = c.adj, colour = "foodDiff3") + 
  scale_x_continuous(breaks = seq(6, 18, 3)) + ylab("SDQ Conduct") +
  xlab("Age (years)")

plot.adjusted[["conduct"]]
```

# Emotional problems {.tabset}

```{r}
emotfits = covars |> 
  map(\(x) fit_lmer(dat = dat, outcome ="emot", age = "age.cent",
                  id = "ID", wt = dat$ipw, modType = "cubic",
                  grp = "foodDiff3", covs = x))
```

## No covariates

```{r results='asis'}
sjPlot::tab_model(emotfits[[1]]$fit)
print(emotfits[[1]]$diagnostics)

e.preds = get_preds(dat = dat, obj = emotfits[[1]], age_y = "Age", 
                    emm_at = emm_at, specs = c("age.cent", "foodDiff3"))

plot.unadjusted[["emot"]] = traj_plot(e.preds, colour = "foodDiff3") + 
  scale_x_continuous(breaks = seq(6, 18, 3)) + ylab("SDQ Emotional") +
  xlab("Age (years)")

plot.unadjusted[["emot"]]
```

## Covariates sex and income

```{r}
sjPlot::tab_model(emotfits[[2]]$fit)
print(emotfits[[2]]$diagnostics)
```

## Covariates sex, income, maternal MH

```{r}
sjPlot::tab_model(emotfits[[3]]$fit)
print(emotfits[[3]]$diagnostics)
```

## Covariates sex, income, maternal MH, IMD

```{r results='asis'}
sjPlot::tab_model(emotfits[[4]]$fit)
print(emotfits[[4]]$diagnostics)

e.adj = get_preds(dat = dat, obj = emotfits[[4]], age_y = "Age",
                specs = c("age.cent", "foodDiff3"), emm_at = emm_at,
                weights = "proportional")

plot.adjusted[["emot"]] = traj_plot(pred.df = e.adj, colour = "foodDiff3") + 
  scale_x_continuous(breaks = seq(6, 18, 3)) + ylab("SDQ Emotional") +
  xlab("Age (years)")

plot.adjusted[["emot"]]
```

# Hyperactivity {.tabset}

```{r}
hyperfits = covars |> 
  map(\(x) fit_lmer(dat = dat, outcome ="hyper", age = "age.cent",
                  id = "ID", wt = dat$ipw, modType = "quartic",
                  grp = "foodDiff3", covs = x))
```

## No covariates

```{r results='asis'}
sjPlot::tab_model(hyperfits[[1]]$fit)
print(hyperfits[[1]]$diagnostics)

h.preds = get_preds(dat = dat, obj = hyperfits[[1]], age_y = "Age", 
                    emm_at = emm_at, specs = c("age.cent", "foodDiff3"))

plot.unadjusted[["hyper"]] = traj_plot(h.preds, colour = "foodDiff3") + 
  scale_x_continuous(breaks = seq(6, 18, 3)) + ylab("SDQ Hyperactivity") +
  xlab("Age (years)")

plot.unadjusted[["hyper"]]
```

## Covariates sex and income

```{r}
sjPlot::tab_model(hyperfits[[2]]$fit)
print(hyperfits[[2]]$diagnostics)
```

## Covariates sex, income, maternal MH

```{r}
sjPlot::tab_model(hyperfits[[3]]$fit)
print(hyperfits[[3]]$diagnostics)
```

## Covariates sex, income, maternal MH, IMD

```{r results='asis'}
sjPlot::tab_model(hyperfits[[4]]$fit)
print(hyperfits[[4]]$diagnostics)

h.adj = get_preds(dat = dat, obj = hyperfits[[4]], age_y = "Age",
                specs = c("age.cent", "foodDiff3"), emm_at = emm_at,
                weights = "proportional")

plot.adjusted[["hyper"]] = traj_plot(pred.df = h.adj, colour = "foodDiff3") + 
  scale_x_continuous(breaks = seq(6, 18, 3)) + ylab("SDQ Hyperactivity") +
  xlab("Age (years)")

plot.adjusted[["hyper"]]
```

# Peer Problems {.tabset}

```{r}
peerfits = covars |> 
  map(\(x) fit_lmer(dat = dat, outcome ="peer", age = "age.cent",
                  id = "ID", wt = dat$ipw, modType = "cubic",
                  grp = "foodDiff3", covs = x))
```

## No covariates

```{r results='asis'}
sjPlot::tab_model(peerfits[[1]]$fit)
print(peerfits[[1]]$diagnostics)

p.preds = get_preds(dat = dat, obj = peerfits[[1]], age_y = "Age", 
                    emm_at = emm_at, specs = c("age.cent", "foodDiff3"))

plot.unadjusted[["peer"]] = traj_plot(p.preds, colour = "foodDiff3") + 
  scale_x_continuous(breaks = seq(6, 18, 3)) + ylab("SDQ Peer") +
  xlab("Age (years)")

plot.unadjusted[["peer"]]
```

## Covariates sex and income

```{r}
sjPlot::tab_model(peerfits[[2]]$fit)
print(peerfits[[2]]$diagnostics)
```

## Covariates sex, income, maternal MH

```{r}
sjPlot::tab_model(peerfits[[3]]$fit)
print(peerfits[[3]]$diagnostics)
```

## Covariates sex, income, maternal MH, IMD

```{r results='asis'}
sjPlot::tab_model(peerfits[[4]]$fit)
print(peerfits[[4]]$diagnostics)

p.adj = get_preds(dat = dat, obj = peerfits[[4]], age_y = "Age",
                specs = c("age.cent", "foodDiff3"), emm_at = emm_at,
                weights = "proportional")

plot.adjusted[["peer"]] = traj_plot(pred.df = p.adj, colour = "foodDiff3") + 
  scale_x_continuous(breaks = seq(6, 18, 3)) + ylab("SDQ Peer") +
  xlab("Age (years)")

plot.adjusted[["peer"]]
```

# Extract results dataframes

```{r}
# column with model covariates for renaming
modcovs = data.frame("covars" = covars |> map_chr(\(x) paste(x, collapse = "+")))

sdqmods = list("conduct" = conductfits, "emot" = emotfits, "hyper" = hyperfits, "peer" = peerfits)

# fit statistics
results.fitstats = sdqmods |> 
  map(\(x) get_fitstats(fitlist = x, modguide = modcovs))

# estimates
results.est = sdqmods |> 
  map(\(x) get_ests(x))

openxlsx::write.xlsx(results.est, here("OUTPUT/ALSPAC", "FI_Estimates.xlsx"))
openxlsx::write.xlsx(results.fitstats, here("OUTPUT/ALSPAC", "FI_FitStats.xlsx"))

save(list = c("c.preds", "e.preds", "h.preds", "p.preds"), file = here("OUTPUT/ALSPAC", "ALSPAC_plotdat.rda"))
save(list = c("c.adj", "e.adj", "h.adj", "p.adj"), file = here("OUTPUT/ALSPAC", "ALSPAC_plotdat_adjusted.rda"))
```

```{r}
lapply(results.fitstats, function(x) kable(x, digits= 3))
```

# Scores at ages and contrasts

```{r}
# fit contrasts for the fully-adjusted models only
contrmods = list("conduct" = conductfits[[4]], "emot" = emotfits[[4]], "hyper" = hyperfits[[4]], "peer" = peerfits[[4]])

# fit contrasts at age 7, 9, 11, 13, 15
emm_at$age.cent = c(7, 9, 11, 13, 15) - mean(dat$Age)

# get the emmeans output object - has predicted values but also some more stuff
emm.list = contrmods |> 
  map(\(x) get_emm(dat = dat, obj = x, emm_at = emm_at, age_y = "Age", 
                   specs = c("age.cent", "foodDiff3"), weights = "proportional"))

# set contrast grid so that it's always more FI vs less FI
contrast_alspac = list(
  "Slightly - Not difficult" = c(-1, 0, 1),
  "(Fairly/Very) - Not difficult" = c(-1, 1, 0),
  "(Fairly/Very) - Slightly" = c(0, 1, -1)
)

# run the contrasts bit
results.contr = emm.list |> 
  map(\(x) mod_contrasts(emm = x, simple = "foodDiff3", age_m = mean(dat$Age),
                         method = contrast_alspac, adjust = "fdr"))

openxlsx::write.xlsx(results.contr, here("OUTPUT/ALSPAC", "FI_Contrasts.xlsx"))

# save the predicted scores at each age
results.scores = emm.list |> 
  map(\(x) broom::tidy(x, conf.int = T)) |> 
  map(\(x) mutate(x, Age = age.cent + mean(dat$Age))) |> 
  map(\(x) relocate(x, Age))

openxlsx::write.xlsx(results.scores, here("OUTPUT/ALSPAC", "FI_Scores.xlsx"))
```

```{r}
lapply(results.contr, function(x) kable(x, digits = 3))
```

```{r}
lapply(results.scores, function(x) kable(x, digits = 3))
```
