---
title: "Social support and food insecurity"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
---
# SDQ trajectories by food insecurity x social support

3-level food insecurity is combined with 2-level enough help to get a 6-level food*social support measure "food_help"
The polynomial terms included here may need to be edited depending on what best fits the data.\

Input data (dat) should be in long format, with the following variables:\

**food_help - 6-level factor combining 3-level food insecurity and binary social support**\

Idnumber - participant ID\
sweep - identifier for each timepoint\
Age - age\
age.cent - mean-centred age (helpful for reducing convergence issues)\
Sex - sex (could be sex at birth, could be gender identity - in this analysis it's a binary measure)\
Dsdco1 - SDQ conduct problems score\
Dsdem1 - SDQ emotional problems score\
Dsdhy1 - SDQ hyperactivity score\
Dsdpr1 - SDQ peer problems score\
Djwtbth2a - sample weight (delete the 'weights = Djwtbth2a,' line for each model if not using weights)\
MeFaff3lvl - 3-level food insecurity measure\
DeEqv5 - household income quintiles, adjusted for household composition (see GUS documentation deriving this)\
DeSf12mn - continuous maternal mental health score from SF-12\
ALeSNim2 - SIMD quintiles\


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, results = "asis", fig.width=10)
library(tidyverse)
library(lme4)
library(lmerTest)
library(emmeans)
library(kableExtra)
emm_options(lmerTest.limit = 20000, pbkrtest.limit = 20000)
```

```{r}
# function to print any singular fit and convergence issues warning messages.
check_fit <- function(m) {
  msg = summary(m)$optinfo$conv$lme4$messages %>% unlist()
  if (any(grepl("isSingular", msg))==T) {
    print("Singular fit")
  } else {print("No singular fit")}
  
  if (any(grepl("failed to converge", msg))==T) {
    print("Failed to converge")
  } else  {print("No convergence issues")}
  } 
```

```{r ggplot theme}
pal = c("#E69F00","#56B4E9","#009E73",
        "#F5C710","#0072B2","#D55E00",
        "#CC79A7","#999999","#000000")

# Set default ggplot colour palette to colourblind-friendly Okabe Ito (2008)
options(ggplot2.discrete.colour=pal, ggplot2.discrete.fill=pal)

# Set global theme for ggplot
my_theme <- function(base_size = 12, base_family = ""){
  theme_bw(base_size = base_size, base_family = base_family) %+replace%
    theme(
      panel.background = element_rect(fill = "transparent"),
      plot.background = element_rect(fill = "transparent", color = NA),
      panel.grid.major = element_line(colour = "grey88"),
      panel.grid.minor = element_line(colour = "grey99"),
      legend.background = element_rect(fill = "transparent"),
      legend.box.background = element_rect(fill = "transparent"),
      panel.ontop = FALSE
    )
}

theme_set(my_theme())
```


```{r}
dat = readRDS("G://users/eileen/Food_Ins/DATA/wt_GUS_social.rds")

## dataframe for new predictions
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent, DeEqv5 = levels(dat$DeEqv5), Sex = levels(dat$Sex))
```

## Conduct problems {.tabset}

### No covariates {.tabset}

#### Model

```{r}
fit = lmer(Dsdco1 ~ food_help*age.cent + food_help*I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot

```{r results='asis'}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help , 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = ggplot() +
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Conduct")
  
fig + facet_grid(. ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

### Covariates sex and income {.tabset}

#### Model

```{r}
fit = lmer(Dsdco1 ~ food_help*age.cent + food_help*I(age.cent^2) + Sex + DeEqv5 +
             (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Lowest income plot

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help + Sex + DeEqv5, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == "1") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Conduct")

fig + facet_grid(Sex ~factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

#### Highest income plot

```{r}
fig = pred %>% filter(DeEqv5 == "5") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Conduct")

fig + facet_grid(Sex ~factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

### Sex, income, maternal MH {.tabset}

#### Model

```{r}
fit = lmer(Dsdco1 ~ food_help*age.cent + food_help*I(age.cent^2) + Sex + DeEqv5 +
             scale(DeSf12mn) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Lowest income plot

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help + Sex + DeEqv5 + scale(DeSf12mn), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == "1") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Conduct")

fig + facet_grid(Sex ~factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

#### Highest income plot

```{r}
fig = pred %>% filter(DeEqv5 == "5") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Conduct")

fig + facet_grid(Sex ~factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

### Sex, income, maternal MH + SIMD {.tabset}

#### Model

```{r}
fit = lmer(Dsdco1 ~ food_help*age.cent + food_help*I(age.cent^2) + Sex + DeEqv5 +
             scale(DeSf12mn) + ALeSNim2 + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Lowest income plot

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help + Sex + DeEqv5 + scale(DeSf12mn) + ALeSNim2, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == "1", ALeSNim2 == "1") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Conduct")

fig + facet_grid(Sex ~factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

#### Highest income plot

```{r}
fig = pred %>% filter(DeEqv5 == "5", ALeSNim2 == "5") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Conduct")

fig + facet_grid(Sex ~factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

## Emotional problems {.tabset}

### No covariates {.tabset}

#### Model

```{r}
fit = lmer(Dsdem1 ~ food_help*age.cent + food_help*I(age.cent^2) + food_help*I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot

```{r results='asis'}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help + I(age.cent^3)*food_help, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = ggplot() +
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Emotional")
  
fig + facet_grid(. ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

### Covariates sex and income {.tabset}

#### Model

```{r}
fit = lmer(Dsdem1 ~ food_help*age.cent + food_help*I(age.cent^2) + food_help*I(age.cent^3) + Sex + DeEqv5 +
             (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Lowest income plot

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help + I(age.cent^3)*food_help  + Sex + DeEqv5, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == "1") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Emotional")

fig + facet_grid(Sex ~factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

#### Highest income plot

```{r}
fig = pred %>% filter(DeEqv5 == "5") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Emotional")

fig + facet_grid(Sex ~factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

### Sex, income, maternal MH {.tabset}

#### Model

```{r}
fit = lmer(Dsdem1 ~ food_help*age.cent + food_help*I(age.cent^2) + food_help*I(age.cent^3) + Sex + DeEqv5 + scale(DeSf12mn) +
             (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Lowest income plot

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help + I(age.cent^3)*food_help  + Sex + DeEqv5 + scale(DeSf12mn), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == "1") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Emotional")

fig + facet_grid(Sex ~factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

#### Highest income plot

```{r}
fig = pred %>% filter(DeEqv5 == "5") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Emotional")

fig + facet_grid(Sex ~factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

### Sex, income, maternal MH, SIMD {.tabset}

#### Model

```{r}
fit = lmer(Dsdem1 ~ food_help*age.cent + food_help*I(age.cent^2) + food_help*I(age.cent^3) + Sex + DeEqv5 + scale(DeSf12mn) + ALeSNim2 +
             (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Lowest income plot

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help + I(age.cent^3)*food_help  + Sex + DeEqv5 + scale(DeSf12mn) + ALeSNim2, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == "1", ALeSNim2 == "1") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Emotional")

fig + facet_grid(Sex ~factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

#### Highest income plot

```{r}
fig = pred %>% filter(DeEqv5 == "5", ALeSNim2 == "5") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Emotional")

fig + facet_grid(Sex ~factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

## Hyperactivity {.tabset}

### No covariates {.tabset}

#### Model

```{r}
fit = lmer(Dsdhy1 ~ food_help*age.cent + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot

```{r results='asis'}
emm = emmeans(fit, specs = ~ age.cent*food_help, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = ggplot() +
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Hyperactivity")
  
fig + facet_grid(. ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

### Covariates sex and income {.tabset}

#### Model

```{r}
fit = lmer(Dsdhy1 ~ food_help*age.cent + 
             Sex + DeEqv5 + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Lowest income plot

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help +
                Sex + DeEqv5, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == "1") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Hyperactivity")
  
fig + facet_grid(Sex ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

#### Highest income plot

```{r}
fig = pred %>% filter(DeEqv5 == "5") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Hyperactivity")
  
fig + facet_grid(Sex ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

### Sex, income, maternal MH {.tabset}

#### Model

```{r}
fit = lmer(Dsdhy1 ~ food_help*age.cent + 
             Sex + DeEqv5 + scale(DeSf12mn) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Lowest income plot

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help +
                Sex + DeEqv5 + scale(DeSf12mn), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == "1") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Hyperactivity")
  
fig + facet_grid(Sex ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

#### Highest income plot

```{r}
fig = pred %>% filter(DeEqv5 == "5") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Hyperactivity")
  
fig + facet_grid(Sex ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

### Sex, income, maternal MH + SIMD {.tabset}

#### Model

```{r}
fit = lmer(Dsdhy1 ~ food_help*age.cent + 
             Sex + DeEqv5 + scale(DeSf12mn) + ALeSNim2 + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Lowest income plot

```{r}
emm = emmeans(fit, specs = ~ age.cent*food_help +
                Sex + DeEqv5 + scale(DeSf12mn) + ALeSNim2, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == "1", ALeSNim2 == "1") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Hyperactivity")
  
fig + facet_grid(Sex ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

#### Highest income plot

```{r}
fig = pred %>% filter(DeEqv5 == "5", ALeSNim2 == "5") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Hyperactivity")
  
fig + facet_grid(Sex ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

## Peer problems {.tabset}

### No Covariates {.tabset}

#### Model

```{r}
fit = lmer(Dsdpr1 ~ food_help*age.cent + food_help*I(age.cent^2) + food_help*I(age.cent^3) + food_help*I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot

```{r results='asis'}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help + I(age.cent^3)*food_help + food_help*I(age.cent^4), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = ggplot() +
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Peer Problems")
  
fig + facet_grid(. ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```


### Covariates sex and income {.tabset}

#### Model

```{r}
fit = lmer(Dsdpr1 ~ food_help*age.cent + food_help*I(age.cent^2) + food_help*I(age.cent^3) + food_help*I(age.cent^4) + Sex + DeEqv5 +
             (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Lowest income plot

```{r results='asis'}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help + I(age.cent^3)*food_help + food_help*I(age.cent^4) + Sex + DeEqv5, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == "1") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Peer Problems")
  
fig + facet_grid(Sex ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

#### Highest income plot

```{r}
fig = pred %>% filter(DeEqv5 == "5") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Peer Problems")
  
fig + facet_grid(Sex ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

### Sex, income, maternal MH {.tabset}

#### Model

```{r}
fit = lmer(Dsdpr1 ~ food_help*age.cent + food_help*I(age.cent^2) + food_help*I(age.cent^3) + food_help*I(age.cent^4) + Sex + DeEqv5 + scale(DeSf12mn) +
             (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Lowest income plot

```{r results='asis'}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help + I(age.cent^3)*food_help + food_help*I(age.cent^4) + Sex + DeEqv5 + scale(DeSf12mn), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == "1") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Peer Problems")
  
fig + facet_grid(Sex ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

#### Highest income plot

```{r}
fig = pred %>% filter(DeEqv5 == "5") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Peer Problems")
  
fig + facet_grid(Sex ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

### Sex, income, maternal MH + SIMD {.tabset}

#### Model

```{r}
fit = lmer(Dsdpr1 ~ food_help*age.cent + food_help*I(age.cent^2) + food_help*I(age.cent^3) + food_help*I(age.cent^4) + Sex + DeEqv5 + scale(DeSf12mn) + ALeSNim2 +
             (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Lowest income plot

```{r results='asis'}
emm = emmeans(fit, specs = ~ age.cent*food_help + I(age.cent^2)*food_help + I(age.cent^3)*food_help + food_help*I(age.cent^4) + Sex + DeEqv5 + scale(DeSf12mn) + ALeSNim2, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)  %>%
  mutate(
    food = stringr::str_split_i(string = food_help, "\\.", i = 1),
    help = stringr::str_split_i(string = food_help, "\\.", i = 2)
  )

fig = pred %>% filter(DeEqv5 == "1", ALeSNim2 == "1") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Peer Problems")
  
fig + facet_grid(Sex ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```

#### Highest income plot

```{r}
fig = pred %>% filter(DeEqv5 == "5", ALeSNim2 == "5") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = help),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = help,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Peer Problems")
  
fig + facet_grid(Sex ~ factor(food, levels = c("A lot/fair amount", "A little", "Not at all")))
```