---
title: "Food Insecurity and SDQ trajectories"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
---

Fitting models of SDQ trajectories with food insecurity at age 5 as a 3-level factor. The polynomial terms included here may need to be edited depending on what best fits the data.\

Input data (dat) should be in long format, with the following variables (at minimum):\

Participant ID\
Identifier for each timepoint\
Age (in years)\
Mean-centred age (helpful for reducing convergence issues)\
Sex (could be sex at birth, could be gender identity - in this analysis it's a binary measure)\
SDQ conduct problems score\
SDQ emotional problems score\
SDQ hyperactivity score\
SDQ peer problems score\
Sample weight (delete the 'wt = ,' argument if not using weights)\
3-level food insecurity measure\
Household income\
Maternal MH score (continuous)\
IMD quintiles\

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, results = "asis")
source("ANALYSIS/global.R")
```

```{r read data}
dat = readRDS("G://users/eileen/Food_Ins/DATA/ALSPAC_long.rds")

## miscellaneous setup

dat$income = factor(dat$income, ordered = FALSE) |> relevel(ref = ">400") #highest income as ref
dat$IMD = factor(dat$IMD, ordered=FALSE) |> relevel(ref = "1") #least deprived as ref

## setup for emmeans
age_vals = seq(round(min(dat$Age)), round(max(dat$Age)), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
emm_at = list(age.cent = age_cent, income = levels(dat$income), sex = levels(dat$sex), IMD = levels(dat$IMD)) #list of all categorical predictor levels to estimate. Maternal MH not included here as it's continuous and has a meaningful mean value so we can just get estimates for mean maternal MH score

## setup for model covariates
# 4 covariate structures
covars = list(NULL, c("sex", "income"), c("sex", "income", "epds"), c("sex", "income", "epds", "IMD"))
# column with model covariates
modcovs = data.frame("covars" = covars |> map_chr(\(x) paste(x, collapse = "+")))

results.fitstats = list()
results.est = list()
emm.list = list()
```

# Conduct problems {.tabset}

```{r}
conductfits = covars |> 
  map(\(x) fit_lmer(dat = dat, outcome ="conduct", age = "age.cent",
                  id = "ID", wt = dat$ipw, modType = "cubic",
                  grp = "foodDiff3", covs = x))

# extract fit statistics
results.fitstats[["conduct"]] = conductfits |> 
  map(\(x) glance(x$fit)) |> reduce(rbind) |> cbind(modcovs) |> relocate(covars)

results.est[["conduct"]] = conductfits |> 
  map(\(x) tidy(x$fit, effects="fixed", conf.int = T, conf.level = 0.95)) |> reduce(rbind)
```

## No covariates

```{r results='asis'}
sjPlot::tab_model(conductfits[[1]]$fit)
print(conductfits[[1]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = conductfits[[1]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)

emmeans.plot = traj_plot(plotdat, colour = "foodDiff3") + 
  xlab("Age") + ylab("SDQ Conduct")

emmeans.plot
```

## Covariates sex and income 

```{r results='asis'}
sjPlot::tab_model(conductfits[[2]]$fit)
print(conductfits[[2]]$diagnostics)
```

## Covariates sex, income, maternal MH

```{r results='asis'}
sjPlot::tab_model(conductfits[[3]]$fit)
print(conductfits[[3]]$diagnostics)
```

## Covariates sex, income, maternal MH, SIMD {.tabset}

```{r results='asis'}
sjPlot::tab_model(conductfits[[4]]$fit)
print(conductfits[[4]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = conductfits[[4]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)

emm.list[["conduct"]] = plotdat$emm

pred.low = list(raw.df = plotdat$raw.df, 
                pred.df = plotdat$pred.df |>
                  filter(IMD=="5"&income=="<100"))
pred.hi = list(raw.df = plotdat$raw.df, 
               pred.df = plotdat$pred.df |>
                 filter(IMD=="1"&income==">400"))
```

### Lowest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.low, colour = "foodDiff3") + 
  xlab("Age") + ylab("SDQ Conduct")

emmeans.plot + facet_wrap(~sex)
```

### Highest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.hi, colour = "foodDiff3") + 
  xlab("Age") + ylab("SDQ Conduct")

emmeans.plot + facet_wrap(~sex)
```

# Emotional problems {.tabset}

```{r}
emotfits = covars |> 
  map(\(x) fit_lmer(dat = dat, outcome ="emot", age = "age.cent",
                  id = "ID", wt = dat$ipw, modType = "cubic",
                  grp = "foodDiff3", covs = x))

# extract fit statistics
results.fitstats[["emot"]] = emotfits |> 
  map(\(x) glance(x$fit)) |> reduce(rbind) |> cbind(modcovs) |> relocate(covars)

results.est[["emot"]] = emotfits |> 
  map(\(x) tidy(x$fit, effects="fixed", conf.int = T, conf.level = 0.95)) |> reduce(rbind)
```

## No covariates 

```{r results='asis'}
sjPlot::tab_model(emotfits[[1]]$fit)
print(emotfits[[1]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = emotfits[[1]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)

emmeans.plot = traj_plot(plotdat, colour = "foodDiff3") + 
  xlab("Age") + ylab("SDQ Emotional")

emmeans.plot
```

## Covariates sex and income

```{r}
sjPlot::tab_model(emotfits[[2]]$fit)
print(emotfits[[2]]$diagnostics)
```

## Covariates sex, income, maternal MH

```{r}
sjPlot::tab_model(emotfits[[3]]$fit)
print(emotfits[[3]]$diagnostics)
```

## Covariates sex, income, maternal MH, SIMD {.tabset}

```{r results='asis'}
sjPlot::tab_model(emotfits[[4]]$fit)
print(emotfits[[4]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = emotfits[[4]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)

emm.list[["emot"]] = plotdat$emm

pred.low = list(raw.df = plotdat$raw.df, 
                pred.df = plotdat$pred.df |>
                  filter(IMD=="5"&income=="<100"))
pred.hi = list(raw.df = plotdat$raw.df, 
               pred.df = plotdat$pred.df |>
                 filter(IMD=="1"&income==">400"))
```

### Lowest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.low, colour = "foodDiff3") + 
  xlab("Age") + ylab("SDQ Emotional")

emmeans.plot + facet_wrap(~sex)
```

### Highest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.hi, colour = "foodDiff3") + 
  xlab("Age") + ylab("SDQ Emotional")

emmeans.plot + facet_wrap(~sex)
```

# Hyperactivity {.tabset}

```{r}
hyperfits = covars |> 
  map(\(x) fit_lmer(dat = dat, outcome ="hyper", age = "age.cent",
                  id = "ID", wt = dat$ipw, modType = "quartic",
                  grp = "foodDiff3", covs = x))

# extract fit statistics
results.fitstats[["hyper"]] = hyperfits |> 
  map(\(x) glance(x$fit)) |> reduce(rbind) |> cbind(modcovs) |> relocate(covars)

results.est[["hyper"]] = hyperfits |> 
  map(\(x) tidy(x$fit, effects="fixed", conf.int = T, conf.level = 0.95)) |> reduce(rbind)
```

## No covariates 

```{r results='asis'}
sjPlot::tab_model(hyperfits[[1]]$fit)
print(hyperfits[[1]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = hyperfits[[1]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)

emmeans.plot = traj_plot(plotdat, colour = "foodDiff3") + 
  xlab("Age") + ylab("SDQ Hyperactivity")

emmeans.plot
```

## Covariates sex and income

```{r}
sjPlot::tab_model(hyperfits[[2]]$fit)
print(hyperfits[[2]]$diagnostics)
```

## Covariates sex, income, maternal MH

```{r}
sjPlot::tab_model(hyperfits[[3]]$fit)
print(hyperfits[[3]]$diagnostics)
```

## Covariates sex, income, maternal MH, SIMD {.tabset}

```{r results='asis'}
sjPlot::tab_model(hyperfits[[4]]$fit)
print(hyperfits[[4]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = hyperfits[[4]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)

emm.list[["hyper"]] = plotdat$emm

pred.low = list(raw.df = plotdat$raw.df, 
                pred.df = plotdat$pred.df |>
                  filter(IMD=="5"&income=="<100"))
pred.hi = list(raw.df = plotdat$raw.df, 
               pred.df = plotdat$pred.df |>
                 filter(IMD=="1"&income==">400"))
```

### Lowest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.low, colour = "foodDiff3") + 
  xlab("Age") + ylab("SDQ Hyperactivity")

emmeans.plot + facet_wrap(~sex)
```

### Highest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.hi, colour = "foodDiff3") + 
  xlab("Age") + ylab("SDQ Hyperactivity")

emmeans.plot + facet_wrap(~sex)
```

# Peer Problems {.tabset}

```{r}
peerfits = covars |> 
  map(\(x) fit_lmer(dat = dat, outcome ="peer", age = "age.cent",
                  id = "ID", wt = dat$ipw, modType = "quartic",
                  grp = "foodDiff3", covs = x))

# extract fit statistics
results.fitstats[["peer"]] = peerfits |> 
  map(\(x) glance(x$fit)) |> reduce(rbind) |> cbind(modcovs) |> relocate(covars)

results.est[["peer"]] = peerfits |> 
  map(\(x) tidy(x$fit, effects="fixed", conf.int = T, conf.level = 0.95)) |> reduce(rbind)
```

## No covariates 

```{r results='asis'}
sjPlot::tab_model(peerfits[[1]]$fit)
print(peerfits[[1]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = peerfits[[1]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)

emmeans.plot = traj_plot(plotdat, colour = "foodDiff3") + 
  xlab("Age") + ylab("SDQ Peer")

emmeans.plot
```

## Covariates sex and income

```{r}
sjPlot::tab_model(peerfits[[2]]$fit)
print(peerfits[[2]]$diagnostics)
```

## Covariates sex, income, maternal MH

```{r}
sjPlot::tab_model(peerfits[[3]]$fit)
print(peerfits[[3]]$diagnostics)
```

## Covariates sex, income, maternal MH, SIMD {.tabset}

```{r results='asis'}
sjPlot::tab_model(peerfits[[4]]$fit)
print(peerfits[[4]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = peerfits[[4]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)

emm.list[["peer"]] = plotdat$emm

pred.low = list(raw.df = plotdat$raw.df, 
                pred.df = plotdat$pred.df |>
                  filter(IMD=="5"&income=="<100"))
pred.hi = list(raw.df = plotdat$raw.df, 
               pred.df = plotdat$pred.df |>
                 filter(IMD=="1"&income==">400"))
```

### Lowest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.low, colour = "foodDiff3") + 
  xlab("Age") + ylab("SDQ Peer")

emmeans.plot + facet_wrap(~sex)
```

### Highest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.hi, colour = "foodDiff3") + 
  xlab("Age") + ylab("SDQ Peer")

emmeans.plot + facet_wrap(~sex)
```


# Fit contrasts and save all results

```{r}
## setup for contrasts
# set contrast grid so that it's always more FI vs less FI
contrast_alspac = list(
  "Slightly vs Not difficult" = c(-1, 0, 1),
  "Fairly/Very vs Not difficult" = c(-1, 1, 0),
  "Fairly/Very amount vs Slightly" = c(0, 1, -1)
)

results.contr = emm.list |> 
  map(\(x) mod_contrasts(emm = x, simple = "foodDiff3", age_m = mean(dat$Age), emm_at = emm_at, c_grid = contrast_alspac))

openxlsx::write.xlsx(results.est, "C://Users/eilee/Desktop/PhD/Year 3/Food Insecurity/FI_Trajectories/OUTPUT/FI_FullSample_Estimates.xlsx")

openxlsx::write.xlsx(results.fitstats, "C://Users/eilee/Desktop/PhD/Year 3/Food Insecurity/FI_Trajectories/OUTPUT/FI_FullSample_FitStats.xlsx")

openxlsx::write.xlsx(results.contr, "C://Users/eilee/Desktop/PhD/Year 3/Food Insecurity/FI_Trajectories/OUTPUT/FI_FullSample_Contrasts.xlsx")
```

