---
title: "Food Insecurity and SDQ trajectories"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
---

Fitting models of SDQ trajectories with food insecurity at age 5 as a 3-level factor. The polynomial terms included here may need to be edited depending on what best fits the data.\


Input data (dat) should be in long format, with the following variables (at minimum):\

Idnumber - participant ID\
sweep - identifier for each timepoint\
Age - age\
age.cent - mean-centred age (helpful for reducing convergence issues)\
Sex - sex (could be sex at birth, could be gender identity - in this analysis it's a binary measure)\
Dsdco1 - SDQ conduct problems score\
Dsdem1 - SDQ emotional problems score\
Dsdhy1 - SDQ hyperactivity score\
Dsdpr1 - SDQ peer problems score\
Djwtbth2a - sample weight (delete the 'weights = Djwtbth2a,' line for each model if not using weights)\
MeFaff3lvl - 3-level food insecurity measure\
DeEqv5 - household income quintiles, adjusted for household composition (see GUS documentation deriving this)\
DeSf12mn - continuous maternal mental health score from SF-12\
ALeSNim2 - SIMD qunitiles\


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, results = "asis")
source("ANALYSIS/global.R")
```

```{r read data}
dat = readRDS("G://users/eileen/Food_Ins/DATA/wt_GUS_long.rds")

age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent, DeEqv5 = levels(dat$DeEqv5), Sex = levels(dat$Sex), ALeSNim2 = levels(dat$ALeSNim2)) #list of all categorical predictor levels to estimate. Maternal MH not included here as it's continuous and has a meaningful mean value so we can just get estimates for mean maternal MH score
```

## Conduct problems {.tabset}

### Summary by sweep

```{r}
sumtable = dat %>% group_by(across(sweep)) %>%
          summarise(N = sum(!is.na(Dsdco1)),
                    mean = mean(Dsdco1, na.rm = T),
                    SD = sd(Dsdco1, na.rm = T),
                    median = median(Dsdco1, na.rm = T),
                    IQR = IQR(Dsdco1, na.rm = T)
          )

kbl(sumtable) %>%
  kable_styling(full_width = F)

# make dataframe for adding original data as a layer to trajectory plots
df.plot = dat %>%
          group_by(across(sweep)) %>%
          summarise(Age = mean(Age, na.rm = T),
                    Phenotype = mean(Dsdco1, na.rm = T),
                    SD = sd(Dsdco1, na.rm = T),
                    n = sum(!is.na(Dsdco1))) %>%
          mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
                 lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))
```

### No covariates {.tabset}

#### Model

```{r results='asis'}
fit = lmer(Dsdco1 ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot

```{r results='asis'}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = pred %>% ggplot() + 
  geom_line(aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Conduct")

emmeans.plot
```

### Covariates sex and income {.tabset}

#### Model

```{r results='asis'}
fit = lmer(Dsdco1 ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + Sex + DeEqv5 + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot

```{r results='asis'}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + Sex + DeEqv5, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = pred %>% filter(DeEqv5 == "1") %>% ggplot() +
  geom_line(aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Conduct")

emmeans.plot + facet_grid(~ Sex)
```

### Covariates sex, income, maternal MH {.tabset}

#### Model

```{r results='asis'}
fit = lmer(Dsdco1 ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + Sex + DeEqv5 + scale(DeSf12mn) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot

```{r results='asis'}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + Sex + DeEqv5 + scale(DeSf12mn), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)


#plot overall model 
emmeans.plot = pred %>% filter(DeEqv5 == "1") %>% ggplot() + 
  geom_line(aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Conduct")

emmeans.plot + facet_grid(~ Sex)
```


### Covariates sex, income, maternal MH, SIMD {.tabset}

#### Model

```{r results='asis'}
fit = lmer(Dsdco1 ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + Sex + DeEqv5 + scale(DeSf12mn) + ALeSNim2 + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```


#### Lowest level covariates

```{r results='asis'}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + Sex + DeEqv5 + ALeSNim2 + scale(DeSf12mn), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = pred %>% filter(DeEqv5 == "1", ALeSNim2 == "1") %>% ggplot() + 
  geom_line(aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Conduct") + 
  ggtitle("Lowest income and SIMD")

emmeans.plot + facet_grid(~ Sex)
```


#### Highest level covariates

```{r results='asis'}
emmeans.plot = pred %>% filter(DeEqv5 == "5", ALeSNim2 == "5") %>% ggplot() + 
  geom_line(aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Conduct") + 
  ggtitle("Highest income and SIMD")

emmeans.plot + facet_grid(~ Sex)
```

## Emotional problems {.tabset}

### Summary by sweep

```{r}
sumtable = dat %>% group_by(across(sweep)) %>%
          summarise(N = sum(!is.na(Dsdem1)),
                    mean = mean(Dsdem1, na.rm = T),
                    SD = sd(Dsdem1, na.rm = T),
                    median = median(Dsdem1, na.rm = T),
                    IQR = IQR(Dsdem1, na.rm = T)
          )

kbl(sumtable) %>%
  kable_styling(full_width = F)

# make dataframe for adding original data as a layer to trajectory plots
df.plot = dat %>%
          group_by(across(sweep)) %>%
          summarise(Age = mean(Age, na.rm = T),
                    Phenotype = mean(Dsdem1, na.rm = T),
                    SD = sd(Dsdem1, na.rm = T),
                    n = sum(!is.na(Dsdem1))) %>%
          mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
                 lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))
```

### No covariates {.tabset}

#### Model


```{r results='asis'}
fit = lmer(Dsdem1 ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot

```{r results='asis'}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Emotional")

emmeans.plot
```

### Covariates sex and income {.tabset}

#### Model

```{r results='asis'}
fit = lmer(Dsdem1 ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + Sex + DeEqv5 + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot

```{r results='asis', fig.width=10}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + Sex + DeEqv5, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = pred %>% filter(DeEqv5 == "1") %>% ggplot() + 
  geom_line(aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Emotional")

emmeans.plot + facet_grid(~ Sex)
```

### Covariates sex, income, maternal MH {.tabset}

#### Model

```{r results='asis'}
fit = lmer(Dsdem1 ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + Sex + DeEqv5 + scale(DeSf12mn) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot

```{r results='asis', fig.width=10}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + Sex + DeEqv5 + scale(DeSf12mn), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = pred %>% filter(DeEqv5 == "1") %>% ggplot() + 
  geom_line(aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Emotional")

emmeans.plot + facet_grid(~ Sex)
```

### Covariates sex, income, maternal MH, SIMD  {.tabset}

#### Model

```{r results='asis'}
fit = lmer(Dsdem1 ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + Sex + DeEqv5 + scale(DeSf12mn) + ALeSNim2 + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Lowest level covariates

```{r results='asis', fig.width=10}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + Sex + DeEqv5 + ALeSNim2 + scale(DeSf12mn), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = pred %>% filter(DeEqv5 == "1", ALeSNim2 == "1") %>% ggplot() + 
  geom_line(aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Emotional") + 
  ggtitle("Lowest income and SIMD")

emmeans.plot + facet_grid(~ Sex)
```

#### Highest level covariate plot

```{r results='asis', fig.width=10}
#plot overall model 
emmeans.plot = pred %>% filter(DeEqv5 == "5", ALeSNim2 == "5") %>% ggplot() + 
  geom_line(aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Emotional") + 
  ggtitle("Highest income and SIMD")

emmeans.plot + facet_grid(~ Sex)
```

## Hyperactivity {.tabset}

### Summary by sweep

```{r}
sumtable = dat %>% group_by(across(sweep)) %>%
          summarise(N = sum(!is.na(Dsdhy1)),
                    mean = mean(Dsdhy1, na.rm = T),
                    SD = sd(Dsdhy1, na.rm = T),
                    median = median(Dsdhy1, na.rm = T),
                    IQR = IQR(Dsdhy1, na.rm = T)
          )

kbl(sumtable) %>%
  kable_styling(full_width = F)

df.plot = dat %>%
          group_by(across(sweep)) %>%
          summarise(Age = mean(Age, na.rm = T),
                    Phenotype = mean(Dsdhy1, na.rm = T),
                    SD = sd(Dsdhy1, na.rm = T),
                    n = sum(!is.na(Dsdhy1))) %>%
          mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
                 lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))
```

### No covariates {.tabset}

#### Model

```{r results='asis'}
fit = lmer(Dsdhy1 ~ age.cent*MeFaff3lvl + 
             (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot

```{r results='asis'}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = pred %>% ggplot() + 
  geom_line(
            aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(
              aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Hyperactivity")

emmeans.plot
```

### Covariates sex and income {.tabset}

#### Model

```{r results='asis'}
fit = lmer(Dsdhy1 ~ age.cent*MeFaff3lvl +
             Sex + DeEqv5 + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot

```{r results='asis', fig.width=10}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + 
                Sex + DeEqv5, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = pred %>% filter(DeEqv5 == "1") %>% ggplot() + 
  geom_line(aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Hyperactivity")

emmeans.plot + facet_grid(~ Sex)
```

### Covariates sex, income, maternal MH {.tabset}

#### Model


```{r results='asis'}
fit = lmer(Dsdhy1 ~ age.cent*MeFaff3lvl + 
             Sex + DeEqv5 + scale(DeSf12mn) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot

```{r results='asis', fig.width=10}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + 
                Sex + DeEqv5 + scale(DeSf12mn), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)


#plot overall model 
emmeans.plot =  pred %>% filter(DeEqv5 == "1") %>% ggplot() + 
  geom_line(aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Hyperactivity")

emmeans.plot + facet_grid(~ Sex)
```

### Covariates sex, income, maternal MH, SIMD  {.tabset}

#### Model

```{r results='asis'}
fit = lmer(Dsdhy1 ~ age.cent*MeFaff3lvl + 
             Sex + DeEqv5 + scale(DeSf12mn) + ALeSNim2 + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```


#### Lowest level covariates

```{r results='asis', fig.width=10}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl +
                Sex + DeEqv5 + ALeSNim2 + scale(DeSf12mn), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
low.plot = pred %>% filter(DeEqv5 == "1", ALeSNim2 == "1") %>% ggplot() + 
  geom_line(
            aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(
              aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Hyperactivity") + 
  ggtitle("Lowest income and SIMD")

low.plot + facet_grid(~ Sex)
```

#### Highest level covariates plot

```{r results='asis', fig.width=10}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl +
                Sex + DeEqv5 + ALeSNim2 + scale(DeSf12mn), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
high.plot = pred %>% filter(DeEqv5 == "5", ALeSNim2 == "5") %>% ggplot() + 
  geom_line(
            aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(
              aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Hyperactivity") + 
  ggtitle("Highest income and SIMD")

high.plot + facet_grid(~ Sex)
```

## Peer Problems {.tabset}

### Summary by sweep

```{r}
sumtable = dat %>% group_by(across(sweep)) %>%
          summarise(N = sum(!is.na(Dsdpr1)),
                    mean = mean(Dsdpr1, na.rm = T),
                    SD = sd(Dsdpr1, na.rm = T),
                    median = median(Dsdpr1, na.rm = T),
                    IQR = IQR(Dsdpr1, na.rm = T)
          )

kbl(sumtable) %>%
  kable_styling(full_width = F)

df.plot = dat %>%
          group_by(across(sweep)) %>%
          summarise(Age = mean(Age, na.rm = T),
                    Phenotype = mean(Dsdpr1, na.rm = T),
                    SD = sd(Dsdpr1, na.rm = T),
                    n = sum(!is.na(Dsdpr1))) %>%
          mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
                 lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))
```

### No covariates {.tabset}

#### Model

```{r results='asis'}
fit = lmer(Dsdpr1 ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + I(age.cent^4)*MeFaff3lvl + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot

```{r results='asis'}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + I(age.cent^4)*MeFaff3lvl, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Peer")

emmeans.plot
```

### Covariates sex and income {.tabset}

#### Model

```{r results='asis'}
fit = lmer(Dsdpr1 ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + I(age.cent^4)*MeFaff3lvl + Sex + DeEqv5 + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot

```{r results='asis', fig.width=10}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + I(age.cent^4)*MeFaff3lvl + Sex + DeEqv5, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = pred %>% filter(DeEqv5 == "1") %>% ggplot() + 
  geom_line(aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Peer")

emmeans.plot + facet_grid(~ Sex)
```

### Covariates sex, income, maternal MH {.tabset}

#### Model

```{r results='asis'}
fit = lmer(Dsdpr1 ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + I(age.cent^4)*MeFaff3lvl + Sex + DeEqv5 + scale(DeSf12mn) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Plot

```{r results='asis', fig.width=10}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + I(age.cent^4)*MeFaff3lvl + Sex + DeEqv5 + scale(DeSf12mn), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)


#plot overall model 
emmeans.plot = pred %>% filter(DeEqv5 == "1") %>% ggplot() + 
  geom_line( aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon( aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Peer")

emmeans.plot + facet_grid(~ Sex)
```

### Covariates sex, income, maternal MH, SIMD {.tabset}

#### Model

```{r results='asis'}
fit = lmer(Dsdpr1 ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + I(age.cent^4)*MeFaff3lvl + Sex + DeEqv5 + scale(DeSf12mn) + ALeSNim2 + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

#### Lowest level covariates

```{r results='asis', fig.width=10}
emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + I(age.cent^4)*MeFaff3lvl + Sex + DeEqv5 + ALeSNim2 + scale(DeSf12mn), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
low.plot = pred %>% filter(DeEqv5 == "1", ALeSNim2 == "1") %>% ggplot() + 
  geom_line( aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon( aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Peer") + 
  ggtitle("Lowest income and SIMD")

low.plot + facet_grid(~ Sex)
```

#### Highest level covariate plot 

```{r results='asis', fig.width=10}
high.plot = pred %>% filter(DeEqv5 == "5", ALeSNim2 == "5") %>% ggplot() + 
  geom_line(aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon( aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Peer") + 
  ggtitle("Highest income and SIMD")

high.plot + facet_grid(~ Sex)
```


