---
title: "Parental social support"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
editor_options: 
  chunk_output_type: console
---

# Parental social support as a protective factor

Trajectories of SDQ with parental support to investigate whether parental social support could be protective.\

**MdSNpf10 - Close relationships:**\
Not counting people who live with you, how many people do you have a close relationship with?\
  1: I have close relationships with lots of people\
  2: I have close relationships with some people\
  3: I have one or two close relationships\
  4: I don't have any close relationships\

**MdSNsp01 - Enough help:**\
Overall, how do you feel about the amount of support or help you get from friends or family living elsewhere?\
  1: I get enough help\
  2: I don't get enough help\
  3: I don't get any help\
  4: I don't need any help\

To avoid over-complicating the model and to better deal with the low sample size of those with no help, a binary variable will be created combining Not enough and No help **(help_bin)**. "Do not need help" will be removed too. Although not tested in this script, a 6-level FI x Social Support **(food_help)** is included when making the summary table.\


The polynomial terms included here may need to be edited depending on what best fits the data.\

In addition to the above, the input data (dat) should be in long format, with the following variables:\

Idnumber - participant ID\
sweep - identifier for each timepoint\
Age - age\
age.cent - mean-centred age (helpful for reducing convergence issues)\
Sex - sex (could be sex at birth, could be gender identity - in this analysis it's a binary measure)\
Dsdco1 - SDQ conduct problems score\
Dsdem1 - SDQ emotional problems score\
Dsdhy1 - SDQ hyperactivity score\
Dsdpr1 - SDQ peer problems score\
Djwtbth2a - sample weight (delete the 'weights = Djwtbth2a,' line for each model if not using weights)\
MeFaff3lvl - 3-level food insecurity measure\
DeEqv5 - household income quintiles, adjusted for household composition (see GUS documentation deriving this)\
DeSf12mn - continuous maternal mental health score from SF-12\
ALeSNim2 - SIMD quintiles\

I also use **dat_soc** which contains the same social support variables mentioned above - since these are only measured at one sweep it's convenient to have this for summary tables/descriptive statistics.\

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
source("ANALYSIS/global.R")
```

```{r descriptive, results='asis'}
dat = readRDS("G://users/eileen/Food_Ins/DATA/wt_GUS_social.rds")
dat_soc = readRDS("G://users/eileen/Food_Ins/DATA/wt_GUS_social_wide.rds")
dat_descr = dat_soc %>% select(MdSNpf10, MdSNsp01, help_bin, food_help)

summarytools::dfSummary(dat_descr, round.digits = 3,
  valid.col = F, varnumbers = F, labels.col = T,
  na.col = F, graph.col = F, style= "grid", headings = F, plain.ascii = F)
```

```{r results='asis'}
dat %>% group_by(sweep, help_bin) %>%
  summarise(
    N = n_distinct(Idnumber),
    Conduct = mean(Dsdco1, na.rm=T),
    Emot = mean(Dsdem1, na.rm=T),
    Hyper = mean(Dsdhy1, na.rm=T),
    Peer = mean(Dsdpr1, na.rm=T)
  ) %>% kbl(digits = 3) %>% kable_styling()
```

### Conduct problems {.tabset}

#### Close relationships

```{r}
fit = lmer(Dsdco1 ~ MdSNpf10*age.cent + MdSNpf10*I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r results='asis'}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*MdSNpf10 + I(age.cent^2)*MdSNpf10, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = MdSNpf10),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = MdSNpf10,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Conduct")

emmeans.plot
```

#### Enough help

```{r}
fit = lmer(Dsdco1 ~ MdSNsp01*age.cent + MdSNsp01*I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r results='asis'}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*MdSNsp01 + I(age.cent^2)*MdSNsp01, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = MdSNsp01),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = MdSNsp01,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Conduct")

emmeans.plot
```

#### Binary help

```{r}
fit = lmer(Dsdco1 ~ help_bin*age.cent + help_bin*I(age.cent^2) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r results='asis'}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*help_bin + I(age.cent^2)*help_bin, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = help_bin),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = help_bin,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Conduct")

emmeans.plot
```


### Emotional problems {.tabset}

#### Close relationships

```{r}
fit = lmer(Dsdem1 ~ MdSNpf10*age.cent + MdSNpf10*I(age.cent^2) + MdSNpf10*I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r results='asis'}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*MdSNpf10 + I(age.cent^2)*MdSNpf10 + I(age.cent^3)*MdSNpf10, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = MdSNpf10),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = MdSNpf10,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Emotional")

emmeans.plot
```

#### Enough help

```{r}
fit = lmer(Dsdem1 ~ MdSNsp01*age.cent + MdSNsp01*I(age.cent^2) + MdSNsp01*I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r results='asis'}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*MdSNsp01 + I(age.cent^2)*MdSNsp01 + I(age.cent^3)*MdSNsp01, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = MdSNsp01),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = MdSNsp01,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Emotional")

emmeans.plot
```

#### Binary help

```{r}
fit = lmer(Dsdem1 ~ help_bin*age.cent + help_bin*I(age.cent^2) + help_bin*I(age.cent^3) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r results='asis'}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*help_bin + I(age.cent^2)*help_bin + I(age.cent^3)*help_bin, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = help_bin),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = help_bin,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Emotional")

emmeans.plot
```


### Hyperactivity problems{.tabset}

#### Close relationships

```{r}
fit = lmer(Dsdhy1 ~ MdSNpf10*age.cent + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r results='asis'}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*MdSNpf10, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = MdSNpf10),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = MdSNpf10,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Hyperactivity")

emmeans.plot
```

#### Enough help

```{r}
fit = lmer(Dsdhy1 ~ MdSNsp01*age.cent + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r results='asis'}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*MdSNsp01, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = MdSNsp01),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = MdSNsp01,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Hyperactivity")

emmeans.plot
```

#### Binary help

```{r}
fit = lmer(Dsdhy1 ~ help_bin*age.cent + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r results='asis'}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*help_bin, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = help_bin),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = help_bin,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Hyperactivity")

emmeans.plot
```

### Peer problems {.tabset}

#### Close relationships


```{r}
fit = lmer(Dsdpr1 ~ MdSNpf10*age.cent + MdSNpf10*I(age.cent^2) + MdSNpf10*I(age.cent^3) + MdSNpf10*I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r results='asis'}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*MdSNpf10 + I(age.cent^2)*MdSNpf10 + I(age.cent^3)*MdSNpf10 + MdSNpf10*I(age.cent^4), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = MdSNpf10),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = MdSNpf10,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Peer Problems")

emmeans.plot
```

#### Enough help

```{r}
fit = lmer(Dsdpr1 ~ MdSNsp01*age.cent + MdSNsp01*I(age.cent^2) + MdSNsp01*I(age.cent^3) + MdSNsp01*I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r results='asis'}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*MdSNsp01 + I(age.cent^2)*MdSNsp01 + I(age.cent^3)*MdSNsp01 + MdSNsp01*I(age.cent^4), 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = MdSNsp01),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = MdSNsp01,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Peer Problems")

emmeans.plot
```


#### Binary help

```{r}
fit = lmer(Dsdpr1 ~ help_bin*age.cent + help_bin*I(age.cent^2) + help_bin*I(age.cent^3) + help_bin*I(age.cent^4) + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r results='asis'}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*help_bin + I(age.cent^2)*help_bin + I(age.cent^3)*help_bin, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = help_bin),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = help_bin,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Peer Problems")

emmeans.plot
```
