---
title: "Food insecurity and parental social support, split by sex in ALSPAC"
output:
  github_document:
    toc: true
    toc_depth: 2
    df_print: "paged"
---


The polynomial terms included here may need to be edited depending on what best fits the data.\
Input data (dat) should be in long format and contain the same variables as the Food Insecurity script, with the addition of:\

**food_help - a 6-level factor combining 3-level food insecurity and binary social support**\

```{r, setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, results = "asis")
library(here)
i_am("ANALYSIS/ALSPAC/ALSPAC_Social.Rmd")
source(here("FUNS", "packages.R"))
source(here("FUNS", "mods.R"))
source(here("FUNS", "plot.R"))
```

```{r read data}
dat = readRDS("G://users/eileen/Food_Ins/DATA/ALSPAC_long.rds")
```

# 3-level Food Insecurity

## Males {.tabset}

```{r}
dat.m = dat %>% filter(sex == "Male")
dat.m$age.cent = dat.m$Age - mean(dat.m$Age)

sdq = c("conduct" = "conduct", "emot" = "emot","hyper"= "hyper","peer"= "peer")
modtypes = c("conduct"="cubic","emot" ="quadratic","hyper"= "cubic","peer"= "quartic")

modfits = map2(sdq, modtypes, 
               \(x, y) fit_lmer(dat = dat.m, outcome = x, age = "age.cent",
                  id = "ID", wt = dat.m$ipw, modType = y,
                  grp = "foodDiff3"))

modguide = data.frame("Outcome" = c("conduct", "emot", "hyper", "peer"))
m.fitstats = get_fitstats(modfits, modguide = modguide)
m.est = get_ests(modfits)
outcome = data.frame("Outcome" = c(rep("conduct", 12), rep("emot", 9), 
                                   rep("hyper", 12), rep("peer", 15)))
m.est = cbind(outcome, m.est) |> relocate(Outcome)
```

### Conduct

```{r results='asis'}
sjPlot::tab_model(modfits$conduct$fit)
print(modfits$conduct$diagnostics)

plotdat = plot_dfs(dat = dat.m, obj = modfits$conduct, sw = "sweep",
                   age_y = "Age")

emmeans.plot = traj_plot(plotdat, colour = "foodDiff3") + 
  scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Conduct")

emmeans.plot
```


### Emotional

```{r results='asis'}
sjPlot::tab_model(modfits$emot$fit)
print(modfits$emot$diagnostics)

plotdat = plot_dfs(dat = dat.m, obj = modfits$emot, sw = "sweep",
                   age_y = "Age")

emmeans.plot = traj_plot(plotdat, colour = "foodDiff3") + 
  scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Emotional")

emmeans.plot
```

### Hyperactivity

```{r results='asis'}
sjPlot::tab_model(modfits$hyper$fit)
print(modfits$hyper$diagnostics)

plotdat = plot_dfs(dat = dat.m, obj = modfits$hyper, sw = "sweep",
                   age_y = "Age")

emmeans.plot = traj_plot(plotdat, colour = "foodDiff3") + 
  scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Hyper")

emmeans.plot
```

### Peer Prob

```{r results='asis'}
sjPlot::tab_model(modfits$peer$fit)
print(modfits$peer$diagnostics)

plotdat = plot_dfs(dat = dat.m, obj = modfits$peer, sw = "sweep",
                   age_y = "Age")

emmeans.plot = traj_plot(plotdat, colour = "foodDiff3") + 
  scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Peer")

emmeans.plot
```


## Females {.tabset}

```{r}
dat.f = dat %>% filter(sex == "Female")
dat.f$age.cent = dat.f$Age - mean(dat.f$Age)

sdq = c("conduct" = "conduct", "emot" = "emot","hyper"= "hyper","peer"= "peer")
modtypes = c("conduct"="cubic","emot" ="cubic","hyper"= "quartic","peer"= "quadratic")

modfits = map2(sdq, modtypes, 
               \(x, y) fit_lmer(dat = dat.f, outcome = x, age = "age.cent",
                  id = "ID", wt = dat.f$ipw, modType = y,
                  grp = "foodDiff3"))

modguide = data.frame("Outcome" = c("conduct", "emot", "hyper", "peer"))
f.fitstats = get_fitstats(modfits, modguide = modguide)
f.est = get_ests(modfits)
outcome = data.frame("Outcome" = c(rep("conduct", 12), rep("emot", 12), 
                                   rep("hyper", 15), rep("peer", 9)))
f.est = cbind(outcome, f.est) |> relocate(Outcome)
```

### Conduct

```{r results='asis'}
sjPlot::tab_model(modfits$conduct$fit)
print(modfits$conduct$diagnostics)

plotdat = plot_dfs(dat = dat.f, obj = modfits$conduct, sw = "sweep",
                   age_y = "Age")

emmeans.plot = traj_plot(plotdat, colour = "foodDiff3") + 
  scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Conduct")

emmeans.plot
```


### Emotional

```{r results='asis'}
sjPlot::tab_model(modfits$emot$fit)
print(modfits$emot$diagnostics)

plotdat = plot_dfs(dat = dat.f, obj = modfits$emot, sw = "sweep",
                   age_y = "Age")

emmeans.plot = traj_plot(plotdat, colour = "foodDiff3") + 
  scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Emotional")

emmeans.plot
```

### Hyperactivity

```{r results='asis'}
sjPlot::tab_model(modfits$hyper$fit)
print(modfits$hyper$diagnostics)

plotdat = plot_dfs(dat = dat.f, obj = modfits$hyper, sw = "sweep",
                   age_y = "Age")

emmeans.plot = traj_plot(plotdat, colour = "foodDiff3") + 
  scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Hyper")

emmeans.plot
```

### Peer Prob

```{r results='asis'}
sjPlot::tab_model(modfits$peer$fit)
print(modfits$peer$diagnostics)

plotdat = plot_dfs(dat = dat.f, obj = modfits$peer, sw = "sweep",
                   age_y = "Age")

emmeans.plot = traj_plot(plotdat, colour = "foodDiff3") + 
  scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Peer")

emmeans.plot
```


```{r}
m.fitstats.fi = m.fitstats
f.fitstats.fi = f.fitstats
m.est.fi = m.est
f.est.fi = f.est
```

# 6-level FI x Amount of help w/ child

## Males {.tabset}

```{r}
dat.m = dat %>% filter(sex == "Male")
dat.m$age.cent = dat.m$Age - mean(dat.m$Age)

sdq = c("conduct" = "conduct", "emot" = "emot","hyper"= "hyper","peer"= "peer")
modtypes = c("conduct"="cubic","emot" ="quadratic","hyper"= "cubic","peer"= "quartic")

modfits = map2(sdq, modtypes, 
               \(x, y) fit_lmer(dat = dat.m, outcome = x, age = "age.cent",
                  id = "ID", wt = dat.m$ipw, modType = y,
                  grp = "food_help"))

modguide = data.frame("Outcome" = c("conduct", "emot", "hyper", "peer"))
m.fitstats = get_fitstats(modfits, modguide = modguide)
m.est = get_ests(modfits)
outcome = data.frame("Outcome" = c(rep("conduct", 8), rep("emot", 6), 
                                   rep("hyper", 8), rep("peer", 10)))
m.est = cbind(outcome, m.est) |> relocate(Outcome)
```

### Conduct

```{r results='asis'}
sjPlot::tab_model(modfits$conduct$fit)
print(modfits$conduct$diagnostics)

plotdat = plot_dfs(dat = dat.m, obj = modfits$conduct, sw = "sweep",
                   age_y = "Age")

emmeans.plot = traj_plot(plotdat, colour = "food_help") + 
  scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Conduct")

emmeans.plot
```


### Emotional

```{r results='asis'}
sjPlot::tab_model(modfits$emot$fit)
print(modfits$emot$diagnostics)

plotdat = plot_dfs(dat = dat.m, obj = modfits$emot, sw = "sweep",
                   age_y = "Age")

emmeans.plot = traj_plot(plotdat, colour = "food_help") + 
  scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Emotional")

emmeans.plot
```

### Hyperactivity

```{r results='asis'}
sjPlot::tab_model(modfits$hyper$fit)
print(modfits$hyper$diagnostics)

plotdat = plot_dfs(dat = dat.m, obj = modfits$hyper, sw = "sweep",
                   age_y = "Age")

emmeans.plot = traj_plot(plotdat, colour = "food_help") + 
  scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Hyper")

emmeans.plot
```

### Peer Prob

```{r results='asis'}
sjPlot::tab_model(modfits$peer$fit)
print(modfits$peer$diagnostics)

plotdat = plot_dfs(dat = dat.m, obj = modfits$peer, sw = "sweep",
                   age_y = "Age")

emmeans.plot = traj_plot(plotdat, colour = "food_help") + 
  scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Peer")

emmeans.plot
```


## Females {.tabset}

```{r}
dat.f = dat %>% filter(sex == "Female")
dat.f$age.cent = dat.f$Age - mean(dat.f$Age)

sdq = c("conduct" = "conduct", "emot" = "emot","hyper"= "hyper","peer"= "peer")
modtypes = c("conduct"="cubic","emot" ="cubic","hyper"= "quartic","peer"= "quadratic")

modfits = map2(sdq, modtypes, 
               \(x, y) fit_lmer(dat = dat.f, outcome = x, age = "age.cent",
                  id = "ID", wt = dat.f$ipw, modType = y,
                  grp = "food_help"))

modguide = data.frame("Outcome" = c("conduct", "emot", "hyper", "peer"))
f.fitstats = get_fitstats(modfits, modguide = modguide)
f.est = get_ests(modfits)
outcome = data.frame("Outcome" = c(rep("conduct", 24), rep("emot", 24), 
                                   rep("hyper", 30), rep("peer", 18)))
f.est = cbind(outcome, f.est) |> relocate(Outcome)
```

### Conduct

```{r results='asis'}
sjPlot::tab_model(modfits$conduct$fit)
print(modfits$conduct$diagnostics)

plotdat = plot_dfs(dat = dat.f, obj = modfits$conduct, sw = "sweep",
                   age_y = "Age")

emmeans.plot = traj_plot(plotdat, colour = "food_help") + 
  scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Conduct")

emmeans.plot
```


### Emotional

```{r results='asis'}
sjPlot::tab_model(modfits$emot$fit)
print(modfits$emot$diagnostics)

plotdat = plot_dfs(dat = dat.f, obj = modfits$emot, sw = "sweep",
                   age_y = "Age")

emmeans.plot = traj_plot(plotdat, colour = "food_help") + 
  scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Emotional")

emmeans.plot
```

### Hyperactivity

```{r results='asis'}
sjPlot::tab_model(modfits$hyper$fit)
print(modfits$hyper$diagnostics)

plotdat = plot_dfs(dat = dat.f, obj = modfits$hyper, sw = "sweep",
                   age_y = "Age")

emmeans.plot = traj_plot(plotdat, colour = "food_help") + 
  scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Hyper")

emmeans.plot
```

### Peer Prob

```{r results='asis'}
sjPlot::tab_model(modfits$peer$fit)
print(modfits$peer$diagnostics)

plotdat = plot_dfs(dat = dat.f, obj = modfits$peer, sw = "sweep",
                   age_y = "Age")

emmeans.plot = traj_plot(plotdat, colour = "food_help") + 
  scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Peer")

emmeans.plot
```


```{r}
results.est = list("FI Male" = m.est.fi, "FI Female" = f.est.fi, "FIxSocial Male" = m.est, "FIxSocial Female" = f.est)
results.fitstats = list("FI Male" = m.fitstats.fi, "FI Female" = f.fitstats.fi, "FIxSocial Male" = m.fitstats, "FIxSocial Female" = f.fitstats)

openxlsx::write.xlsx(results.est, here("OUTPUT/ALSPAC", "FI_Social_Estimates_bySex.xlsx"))
openxlsx::write.xlsx(results.fitstats, here("OUTPUT/ALSPAC", "FI_Social_FitStats.xlsx"))
```