---
title: "Parental social support x food insecurity in ALSPAC"
output:
  github_document:
    toc: true
    toc_depth: 2
    df_print: "paged"
---

# SDQ trajectories by food insecurity x social support

The polynomial terms included here may need to be edited depending on what best fits the data.\
Input data (dat) should be in long format and contain the same variables as the Food Insecurity script, with the addition of:\

**food_help - a 6-level factor combining 3-level food insecurity and binary social support**\

```{r, setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, results = "asis")
library(here)
i_am("ANALYSIS/ALSPAC/ALSPAC_FI.Rmd")
source(here("FUNS", "packages.R"))
source(here("FUNS", "mods.R"))
source(here("FUNS", "plot.R"))
```

```{r read data}
dat = readRDS("G://users/eileen/Food_Ins/DATA/ALSPAC_long.rds")
## miscellaneous setup

dat$income = factor(dat$income, ordered = FALSE) |> relevel(ref = ">400") #highest income as ref
dat$IMD = factor(dat$IMD, ordered=FALSE) |> relevel(ref = "1") #least deprived as ref

## setup for emmeans (emm_at)
#list of all categorical predictor levels to estimate. Maternal MH not included here as it's continuous and has a meaningful mean value so we can just get estimates for mean maternal MH score
emm_at = c(make_emm_at(age_y = dat$Age, agevar = "age.cent"), income = levels(dat$income), sex = levels(dat$sex), IMD = levels(dat$IMD)) 

## setup for model covariates
# 4 covariate structures
covars = list(NULL, c("sex", "income"), c("sex", "income", "epds"), c("sex", "income", "epds", "IMD"))
```

# Conduct problems {.tabset}

```{r}
conductfits = covars |> 
  map(\(x) fit_lmer(dat = dat, outcome ="conduct", age = "age.cent",
                  id = "ID", wt = dat$ipw, modType = "cubic",
                  grp = "food_help", covs = x))
```

## No covariates

```{r results='asis'}
sjPlot::tab_model(conductfits[[1]]$fit)
print(conductfits[[1]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = conductfits[[1]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)
plotdat$pred.df = pred_add(plotdat$pred.df, string = "food_help", v1 = "Food", v2 = "Help")

emmeans.plot = traj_plot(plotdat, colour = "Help") + 
  scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Conduct") + labs(fill = "Help w/ child", colour = "Help w/ child")

emmeans.plot + facet_grid(. ~ factor(Food, levels = c("Not difficult",                                           "Fairly/Very", "Slightly")))
```

## Covariates sex and income 

```{r results='asis'}
sjPlot::tab_model(conductfits[[2]]$fit)
print(conductfits[[2]]$diagnostics)
```

## Covariates sex, income, maternal MH

```{r results='asis'}
sjPlot::tab_model(conductfits[[3]]$fit)
print(conductfits[[3]]$diagnostics)
```

## Covariates sex, income, maternal MH, SIMD {.tabset}

```{r results='asis'}
sjPlot::tab_model(conductfits[[4]]$fit)
print(conductfits[[4]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = conductfits[[4]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)
plotdat$pred.df = pred_add(plotdat$pred.df, string = "food_help", v1 = "Food", v2 = "Help")

pred.low = list(raw.df = plotdat$raw.df, 
                pred.df = plotdat$pred.df |>
                  filter(IMD=="5"&income=="<100"))
pred.hi = list(raw.df = plotdat$raw.df, 
               pred.df = plotdat$pred.df |>
                 filter(IMD=="1"&income==">400"))
```

### Lowest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.low, colour = "Help") + 
  scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Conduct") + labs(fill = "Help w/ child", colour = "Help w/ child")

emmeans.plot + facet_grid(sex ~ factor(Food, levels = c("Not difficult",                                           "Fairly/Very", "Slightly")))
```

### Highest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.hi, colour = "food_help") + 
  scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Conduct") + labs(fill = "Help w/ child", colour = "Help w/ child")

emmeans.plot + facet_grid(sex ~ factor(Food, levels = c("Not difficult",                                           "Fairly/Very", "Slightly"))) 
```

# Emotional problems {.tabset}

```{r}
emotfits = covars |> 
  map(\(x) fit_lmer(dat = dat, outcome ="emot", age = "age.cent",
                  id = "ID", wt = dat$ipw, modType = "cubic",
                  grp = "food_help", covs = x))
```

## No covariates 

```{r results='asis'}
sjPlot::tab_model(emotfits[[1]]$fit)
print(emotfits[[1]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = emotfits[[1]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)
plotdat$pred.df = pred_add(plotdat$pred.df, string = "food_help", v1 = "Food", v2 = "Help")

emmeans.plot = traj_plot(plotdat, colour = "food_help") + 
  scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Emotional") + labs(fill = "Help w/ child", colour = "Help w/ child")

emmeans.plot + facet_grid(. ~ factor(Food, levels = c("Not difficult",                                           "Fairly/Very", "Slightly")))
```

## Covariates sex and income

```{r}
sjPlot::tab_model(emotfits[[2]]$fit)
print(emotfits[[2]]$diagnostics)
```

## Covariates sex, income, maternal MH

```{r}
sjPlot::tab_model(emotfits[[3]]$fit)
print(emotfits[[3]]$diagnostics)
```

## Covariates sex, income, maternal MH, SIMD {.tabset}

```{r results='asis'}
sjPlot::tab_model(emotfits[[4]]$fit)
print(emotfits[[4]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = emotfits[[4]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)
plotdat$pred.df = pred_add(plotdat$pred.df, string = "food_help", v1 = "Food", v2 = "Help")

pred.low = list(raw.df = plotdat$raw.df, 
                pred.df = plotdat$pred.df |>
                  filter(IMD=="5"&income=="<100"))
pred.hi = list(raw.df = plotdat$raw.df, 
               pred.df = plotdat$pred.df |>
                 filter(IMD=="1"&income==">400"))
```

### Lowest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.low, colour = "food_help") + 
  scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Emotional") + labs(fill = "Help w/ child", colour = "Help w/ child")

emmeans.plot + facet_grid(. ~ factor(Food, levels = c("Not difficult",                                           "Fairly/Very", "Slightly")))
```

### Highest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.hi, colour = "food_help") + 
  scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Emotional") + labs(fill = "Help w/ child", colour = "Help w/ child")

emmeans.plot + facet_grid(. ~ factor(Food, levels = c("Not difficult",                                           "Fairly/Very", "Slightly")))
```

# Hyperactivity {.tabset}

```{r}
hyperfits = covars |> 
  map(\(x) fit_lmer(dat = dat, outcome ="hyper", age = "age.cent",
                  id = "ID", wt = dat$ipw, modType = "quartic",
                  grp = "food_help", covs = x))
```

## No covariates 

```{r results='asis'}
sjPlot::tab_model(hyperfits[[1]]$fit)
print(hyperfits[[1]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = hyperfits[[1]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)
plotdat$pred.df = pred_add(plotdat$pred.df, string = "food_help", v1 = "Food", v2 = "Help")

emmeans.plot = traj_plot(plotdat, colour = "food_help") + 
  scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Hyperactivity") + labs(fill = "Help w/ child", colour = "Help w/ child")

emmeans.plot + facet_grid(. ~ factor(Food, levels = c("Not difficult",                                           "Fairly/Very", "Slightly")))
```

## Covariates sex and income

```{r}
sjPlot::tab_model(hyperfits[[2]]$fit)
print(hyperfits[[2]]$diagnostics)
```

## Covariates sex, income, maternal MH

```{r}
sjPlot::tab_model(hyperfits[[3]]$fit)
print(hyperfits[[3]]$diagnostics)
```

## Covariates sex, income, maternal MH, SIMD {.tabset}

```{r results='asis'}
sjPlot::tab_model(hyperfits[[4]]$fit)
print(hyperfits[[4]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = hyperfits[[4]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)
plotdat$pred.df = pred_add(plotdat$pred.df, string = "food_help", v1 = "Food", v2 = "Help")

pred.low = list(raw.df = plotdat$raw.df, 
                pred.df = plotdat$pred.df |>
                  filter(IMD=="5"&income=="<100"))
pred.hi = list(raw.df = plotdat$raw.df, 
               pred.df = plotdat$pred.df |>
                 filter(IMD=="1"&income==">400"))
```

### Lowest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.low, colour = "food_help") + 
  scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Hyperactivity") + labs(fill = "Help w/ child", colour = "Help w/ child")

emmeans.plot + facet_grid(. ~ factor(Food, levels = c("Not difficult",                                           "Fairly/Very", "Slightly")))
```

### Highest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.hi, colour = "food_help") + 
  scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Hyperactivity") + labs(fill = "Help w/ child", colour = "Help w/ child")

emmeans.plot + facet_grid(. ~ factor(Food, levels = c("Not difficult",                                           "Fairly/Very", "Slightly")))
```

# Peer Problems {.tabset}

```{r}
peerfits = covars |> 
  map(\(x) fit_lmer(dat = dat, outcome ="peer", age = "age.cent",
                  id = "ID", wt = dat$ipw, modType = "quartic",
                  grp = "food_help", covs = x))
```

## No covariates 

```{r results='asis'}
sjPlot::tab_model(peerfits[[1]]$fit)
print(peerfits[[1]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = peerfits[[1]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)
plotdat$pred.df = pred_add(plotdat$pred.df, string = "food_help", v1 = "Food", v2 = "Help")

emmeans.plot = traj_plot(plotdat, colour = "food_help") + 
  scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Peer") + labs(fill = "Help w/ child", colour = "Help w/ child")

emmeans.plot + facet_grid(. ~ factor(Food, levels = c("Not difficult",                                           "Fairly/Very", "Slightly")))
```

## Covariates sex and income

```{r}
sjPlot::tab_model(peerfits[[2]]$fit)
print(peerfits[[2]]$diagnostics)
```

## Covariates sex, income, maternal MH

```{r}
sjPlot::tab_model(peerfits[[3]]$fit)
print(peerfits[[3]]$diagnostics)
```

## Covariates sex, income, maternal MH, SIMD {.tabset}

```{r results='asis'}
sjPlot::tab_model(peerfits[[4]]$fit)
print(peerfits[[4]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = peerfits[[4]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)
plotdat$pred.df = pred_add(plotdat$pred.df, string = "food_help", v1 = "Food", v2 = "Help")

pred.low = list(raw.df = plotdat$raw.df, 
                pred.df = plotdat$pred.df |>
                  filter(IMD=="5"&income=="<100"))
pred.hi = list(raw.df = plotdat$raw.df, 
               pred.df = plotdat$pred.df |>
                 filter(IMD=="1"&income==">400"))
```

### Lowest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.low, colour = "food_help") + 
  scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Peer") + labs(fill = "Help w/ child", colour = "Help w/ child")

emmeans.plot + facet_grid(. ~ factor(Food, levels = c("Not difficult",                                           "Fairly/Very", "Slightly")))
```

### Highest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.hi, colour = "food_help") + 
  scale_x_continuous(name = "Age", breaks = seq(6, 18, 3)) + ylab("SDQ Peer") + labs(fill = "Help w/ child", colour = "Help w/ child")

emmeans.plot + facet_grid(. ~ factor(Food, levels = c("Not difficult",                                           "Fairly/Very", "Slightly")))
```


# Extract results dataframes

```{r}
# column with model covariates for renaming
modcovs = data.frame("covars" = covars |> map_chr(\(x) paste(x, collapse = "+")))

sdqmods = list("conduct" = conductfits, "emot" = emotfits, "hyper" = hyperfits, "peer" = peerfits)

results.fitstats = sdqmods |> 
  map(\(x) get_fitstats(fitlist = x, modguide = modcovs))
results.est = sdqmods |> 
  map(\(x) get_ests(x))

openxlsx::write.xlsx(results.est, here("OUTPUT/ALSPAC", "FI_Social_Estimates.xlsx"))
openxlsx::write.xlsx(results.fitstats, here("OUTPUT/ALSPAC", "FI_Social_FitStats.xlsx"))
```


# Fit contrasts

```{r}
# fit contrasts for the fully-adjusted models only
contrmods = list("conduct" = conductfits[[4]], "emot" = emotfits[[4]], "hyper" = hyperfits[[4]], "peer" = peerfits[[4]])

# fit contrasts at age 7, 9, 11, 13, 15, 18
emm_at$age.cent = c(7, 9, 11, 13, 15, 18) - mean(dat$Age)

emm_at = list(age.cent = c(7, 9, 11, 13, 15, 18) - mean(dat$Age), sex = "Female", income = "<100", IMD = "5")

# get the emmeans output object - has predicted values but also some more stuff
emm.list = contrmods |> 
  map(\(x) get_emm(dat = dat, obj = x, emm_at = emm_at))

# contrast grid comparing enough/not enough for each FI level
contrast_alspac = list(
  "Not difficult: Not enough vs Enough" = c(-1, 0, 0, 1, 0, 0),
  "Slightly: Not enough vs Enough" = c(0, 0, 0, 0, -1, 1),
  "Fairly/Very: Not enough vs Enough" = c(0, -1, 1, 0, 0, 0)
)

# run the contrasts bit
results.contr = emm.list |> 
  map(\(x) mod_contrasts(emm = x, simple = "food_help", age_m = mean(dat$Age), emm_at = emm_at, c_grid = contrast_alspac))

openxlsx::write.xlsx(results.contr, here("OUTPUT/ALSPAC", "FI_Social_Contrasts.xlsx"))
```