---
title: "Parental social support and FI in GUS"
output:
  html_document:
    toc: true
    toc_float: true
    keep_md: true
---

# SDQ trajectories by food insecurity x social support

The polynomial terms included here may need to be edited depending on what best fits the data.\
Input data (dat) should be in long format and contain the same variables as the Food Insecurity script, with the addition of:\

**food_help - a 6-level factor combining 3-level food insecurity and binary social support**\

```{r, setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, results = "asis")
library(here)
i_am("ANALYSIS/GUS/GUS_FI.Rmd")
source(here("FUNS", "packages.R"))
source(here("FUNS", "mods.R"))
source(here("FUNS", "plot.R"))
```

```{r read data}
dat = readRDS("G://users/eileen/Food_Ins/DATA/GUS_long.rds")
## setup for emmeans (emm_at)
#list of all categorical predictor levels to estimate. Maternal MH not included here as it's continuous and has a meaningful mean value so we can just get estimates for mean maternal MH score
emm_at = c(make_emm_at(age_y = dat$Age, agevar = "age.cent"), DeEqv5 = levels(dat$DeEqv5), sex = levels(dat$Sex), ALeSNim2 = levels(dat$ALeSNim2)) 

## setup for model covariates
# 4 covariate structures
covars = list(NULL, c("Sex", "DeEqv5"), c("Sex", "DeEqv5", "DeSf12mn"), c("Sex", "DeEqv5", "DeSf12mn", "ALeSNim2"))
```

# Conduct problems {.tabset}

```{r}
conductfits = covars |> 
  map(\(x) fit_lmer(dat = dat, outcome ="Dsdco1", age = "age.cent",
                  id = "Idnumber", wt = dat$WTbth2, modType = "cubic",
                  grp = "food_help", covs = x))
```

## No covariates

```{r results='asis'}
sjPlot::tab_model(conductfits[[1]]$fit)
print(conductfits[[1]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = conductfits[[1]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)
plotdat$pred.df = pred_add(plotdat$pred.df, string = "food_help", v1 = "Food", v2 = "Help")

emmeans.plot = traj_plot(plotdat, colour = "Help") + 
  xlab("Age") + ylab("SDQ Conduct") + labs(fill = "Amount of help", colour = "Amount of help")

emmeans.plot + facet_grid(. ~ factor(Food, levels = c("Not at all",                                           "A lot/fair amount", "A little")))
```

## Covariates sex and income 

```{r results='asis'}
sjPlot::tab_model(conductfits[[2]]$fit)
print(conductfits[[2]]$diagnostics)
```

## Covariates sex, income, maternal MH

```{r results='asis'}
sjPlot::tab_model(conductfits[[3]]$fit)
print(conductfits[[3]]$diagnostics)
```

## Covariates sex, income, maternal MH, SIMD {.tabset}

```{r results='asis'}
sjPlot::tab_model(conductfits[[4]]$fit)
print(conductfits[[4]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = conductfits[[4]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)
plotdat$pred.df = pred_add(plotdat$pred.df, string = "food_help", v1 = "Food", v2 = "Help")

pred.low = list(raw.df = plotdat$raw.df, 
                pred.df = plotdat$pred.df |>
                  filter(ALeSNim2=="1"&DeEqv5=="1"))
pred.hi = list(raw.df = plotdat$raw.df, 
               pred.df = plotdat$pred.df |>
                 filter(ALeSNim2=="5"&DeEqv5=="5"))
```

### Lowest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.low, colour = "Help") + 
  xlab("Age") + ylab("SDQ Conduct") + labs(fill = "Amount of help", colour = "Amount of help")

emmeans.plot + facet_grid(. ~ factor(Food, levels = c("Not at all",                                           "A lot/fair amount", "A little")))
```

### Highest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.hi, colour = "food_help") + 
  xlab("Age") + ylab("SDQ Conduct") + labs(fill = "Amount of help", colour = "Amount of help")

emmeans.plot + facet_grid(. ~ factor(Food, levels = c("Not at all",                                           "A lot/fair amount", "A little")))
```

# Emotional problems {.tabset}

```{r}
emotfits = covars |> 
  map(\(x) fit_lmer(dat = dat, outcome ="Dsdem1", age = "age.cent",
                  id = "Idnumber", wt = dat$WTbth2, modType = "cubic",
                  grp = "food_help", covs = x))
```

## No covariates 

```{r results='asis'}
sjPlot::tab_model(emotfits[[1]]$fit)
print(emotfits[[1]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = emotfits[[1]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)
plotdat$pred.df = pred_add(plotdat$pred.df, string = "food_help", v1 = "Food", v2 = "Help")

emmeans.plot = traj_plot(plotdat, colour = "food_help") + 
  xlab("Age") + ylab("SDQ Emotional") + labs(fill = "Amount of help", colour = "Amount of help")

emmeans.plot + facet_grid(. ~ factor(Food, levels = c("Not at all",                                           "A lot/fair amount", "A little")))
```

## Covariates sex and income

```{r}
sjPlot::tab_model(emotfits[[2]]$fit)
print(emotfits[[2]]$diagnostics)
```

## Covariates sex, income, maternal MH

```{r}
sjPlot::tab_model(emotfits[[3]]$fit)
print(emotfits[[3]]$diagnostics)
```

## Covariates sex, income, maternal MH, SIMD {.tabset}

```{r results='asis'}
sjPlot::tab_model(emotfits[[4]]$fit)
print(emotfits[[4]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = emotfits[[4]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)
plotdat$pred.df = pred_add(plotdat$pred.df, string = "food_help", v1 = "Food", v2 = "Help")

pred.low = list(raw.df = plotdat$raw.df, 
                pred.df = plotdat$pred.df |>
                  filter(ALeSNim2=="1"&DeEqv5=="1"))
pred.hi = list(raw.df = plotdat$raw.df, 
               pred.df = plotdat$pred.df |>
                 filter(ALeSNim2=="5"&DeEqv5=="5"))
```

### Lowest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.low, colour = "food_help") + 
  xlab("Age") + ylab("SDQ Emotional") + labs(fill = "Amount of help", colour = "Amount of help")

emmeans.plot + facet_grid(. ~ factor(Food, levels = c("Not at all",                                           "A lot/fair amount", "A little")))
```

### Highest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.hi, colour = "food_help") + 
  xlab("Age") + ylab("SDQ Emotional") + labs(fill = "Amount of help", colour = "Amount of help")

emmeans.plot + facet_grid(. ~ factor(Food, levels = c("Not at all",                                           "A lot/fair amount", "A little")))
```

# Hyperactivity {.tabset}

```{r}
hyperfits = covars |> 
  map(\(x) fit_lmer(dat = dat, outcome ="Dsdhy1", age = "age.cent",
                  id = "Idnumber", wt = dat$WTbth2, modType = "linear",
                  grp = "food_help", covs = x))
```

## No covariates 

```{r results='asis'}
sjPlot::tab_model(hyperfits[[1]]$fit)
print(hyperfits[[1]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = hyperfits[[1]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)
plotdat$pred.df = pred_add(plotdat$pred.df, string = "food_help", v1 = "Food", v2 = "Help")

emmeans.plot = traj_plot(plotdat, colour = "food_help") + 
  xlab("Age") + ylab("SDQ Hyperactivity") + labs(fill = "Amount of help", colour = "Amount of help")

emmeans.plot + facet_grid(. ~ factor(Food, levels = c("Not at all",                                           "A lot/fair amount", "A little")))
```

## Covariates sex and income

```{r}
sjPlot::tab_model(hyperfits[[2]]$fit)
print(hyperfits[[2]]$diagnostics)
```

## Covariates sex, income, maternal MH

```{r}
sjPlot::tab_model(hyperfits[[3]]$fit)
print(hyperfits[[3]]$diagnostics)
```

## Covariates sex, income, maternal MH, SIMD {.tabset}

```{r results='asis'}
sjPlot::tab_model(hyperfits[[4]]$fit)
print(hyperfits[[4]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = hyperfits[[4]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)
plotdat$pred.df = pred_add(plotdat$pred.df, string = "food_help", v1 = "Food", v2 = "Help")

pred.low = list(raw.df = plotdat$raw.df, 
                pred.df = plotdat$pred.df |>
                  filter(ALeSNim2=="1"&DeEqv5=="1"))
pred.hi = list(raw.df = plotdat$raw.df, 
               pred.df = plotdat$pred.df |>
                 filter(ALeSNim2=="5"&DeEqv5=="5"))
```

### Lowest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.low, colour = "food_help") + 
  xlab("Age") + ylab("SDQ Hyperactivity") + labs(fill = "Amount of help", colour = "Amount of help")

emmeans.plot + facet_grid(. ~ factor(Food, levels = c("Not at all",                                           "A lot/fair amount", "A little")))
```

### Highest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.hi, colour = "food_help") + 
  xlab("Age") + ylab("SDQ Hyperactivity") + labs(fill = "Amount of help", colour = "Amount of help")

emmeans.plot + facet_grid(. ~ factor(Food, levels = c("Not at all",                                           "A lot/fair amount", "A little")))
```

# Peer Problems {.tabset}

```{r}
peerfits = covars |> 
  map(\(x) fit_lmer(dat = dat, outcome ="Dsdpr1", age = "age.cent",
                  id = "Idnumber", wt = dat$WTbth2, modType = "quartic",
                  grp = "food_help", covs = x))
```

## No covariates 

```{r results='asis'}
sjPlot::tab_model(peerfits[[1]]$fit)
print(peerfits[[1]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = peerfits[[1]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)
plotdat$pred.df = pred_add(plotdat$pred.df, string = "food_help", v1 = "Food", v2 = "Help")

emmeans.plot = traj_plot(plotdat, colour = "food_help") + 
  xlab("Age") + ylab("SDQ Peer") + labs(fill = "Amount of help", colour = "Amount of help")

emmeans.plot + facet_grid(. ~ factor(Food, levels = c("Not at all",                                           "A lot/fair amount", "A little")))
```

## Covariates sex and income

```{r}
sjPlot::tab_model(peerfits[[2]]$fit)
print(peerfits[[2]]$diagnostics)
```

## Covariates sex, income, maternal MH

```{r}
sjPlot::tab_model(peerfits[[3]]$fit)
print(peerfits[[3]]$diagnostics)
```

## Covariates sex, income, maternal MH, SIMD {.tabset}

```{r results='asis'}
sjPlot::tab_model(peerfits[[4]]$fit)
print(peerfits[[4]]$diagnostics)

plotdat = plot_dfs(dat = dat, obj = peerfits[[4]], sw = "sweep",
                   age_y = "Age", emm_at = emm_at)
plotdat$pred.df = pred_add(plotdat$pred.df, string = "food_help", v1 = "Food", v2 = "Help")

pred.low = list(raw.df = plotdat$raw.df, 
                pred.df = plotdat$pred.df |>
                  filter(ALeSNim2=="1"&DeEqv5=="1"))
pred.hi = list(raw.df = plotdat$raw.df, 
               pred.df = plotdat$pred.df |>
                 filter(ALeSNim2=="5"&DeEqv5=="5"))
```

### Lowest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.low, colour = "food_help") + 
  xlab("Age") + ylab("SDQ Peer") + labs(fill = "Amount of help", colour = "Amount of help")

emmeans.plot + facet_grid(. ~ factor(Food, levels = c("Not at all",                                           "A lot/fair amount", "A little")))
```

### Highest level covariates

```{r results='asis'}
emmeans.plot = traj_plot(pred.hi, colour = "food_help") + 
  xlab("Age") + ylab("SDQ Peer") + labs(fill = "Amount of help", colour = "Amount of help")

emmeans.plot + facet_grid(. ~ factor(Food, levels = c("Not at all",                                           "A lot/fair amount", "A little")))
```


# Extract results dataframes

```{r}
# column with model covariates for renaming
modcovs = data.frame("covars" = covars |> map_chr(\(x) paste(x, collapse = "+")))

sdqmods = list("conduct" = conductfits, "emot" = emotfits, "hyper" = hyperfits, "peer" = peerfits)

results.fitstats = sdqmods |> 
  map(\(x) get_fitstats(fitlist = x, modguide = modcovs))
results.est = sdqmods |> 
  map(\(x) get_ests(x))

openxlsx::write.xlsx(results.est, here("OUTPUT/GUS", "FI_Social_Estimates.xlsx"))
openxlsx::write.xlsx(results.fitstats, here("OUTPUT/GUS", "FI_Social_FitStats.xlsx"))
```


# Fit contrasts

```{r}
# fit contrasts for the fully-adjusted models only
contrmods = list("conduct" = conductfits[[4]], "emot" = emotfits[[4]], "hyper" = hyperfits[[4]], "peer" = peerfits[[4]])

# fit contrasts at age 5, 7, 9, 11, 13, 16
emm_at$age.cent = c(5, 7, 9, 11, 13, 16) - mean(dat$Age)

# get the emmeans output object - has predicted values but also some more stuff
emm.list = contrmods |> 
  map(\(x) get_emm(dat = dat, obj = x, emm_at = emm_at))

# contrast grid comparing enough/not enough for each FI level
contrast_gus = list(
  "Not at all: Not enough vs Enough" = c(-1, 0, 0, 0, 0, 1),
  "A little: Not enough vs Enough" = c(0, -1, 1, 0, 0, 0),
  "Fairly/Very: Not enough vs Enough" = c(0, 0, 0, -1, 1, 0)
)

# run the contrasts bit
results.contr = emm.list |> 
  map(\(x) mod_contrasts(emm = x, simple = "food_help", age_m = mean(dat$Age), emm_at = emm_at, c_grid = contrast_gus))

openxlsx::write.xlsx(results.contr, here("OUTPUT/GUS", "FI_Social_Contrasts.xlsx"))
```