---
title: "Sex-stratified SDQ trajectories in GUS"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, results = "asis")
```

```{r load packages}
library(lme4)
library(lmerTest)
library(kableExtra)
library(tidyverse)
library(emmeans)
library(summarytools)
emm_options(lmerTest.limit = 20000, pbkrtest.limit = 20000)
```

```{r}
# function to print any singular fit and convergence issues warning messages.
check_fit <- function(m) {
  msg = summary(m)$optinfo$conv$lme4$messages |> unlist()
  if (any(grepl("isSingular", msg))==T) {
    print("Singular fit")
  } else {print("No singular fit")}
  
  if (any(grepl("failed to converge", msg))==T) {
    print("Failed to converge")
  } else  {print("No convergence issues")}
  } 
```

```{r ggplot theme}
pal = c("#E69F00","#56B4E9","#009E73",
        "#F5C710","#0072B2","#D55E00",
        "#CC79A7","#999999","#000000")

# Set default ggplot colour palette to colourblind-friendly Okabe Ito (2008)
options(ggplot2.discrete.colour=pal, ggplot2.discrete.fill=pal)

# Set global theme for ggplot
my_theme <- function(base_size = 12, base_family = ""){
  theme_bw(base_size = base_size, base_family = base_family) %+replace%
    theme(
      panel.background = element_rect(fill = "transparent"),
      plot.background = element_rect(fill = "transparent", color = NA),
      panel.grid.major = element_line(colour = "grey88"),
      panel.grid.minor = element_line(colour = "grey99"),
      legend.background = element_rect(fill = "transparent"),
      legend.box.background = element_rect(fill = "transparent"),
      panel.ontop = FALSE
    )
}

theme_set(my_theme())
```

## Descriptives tables by sex

```{r read in data}
dat = readRDS("G://users/eileen/Food_Ins/DATA/wt_GUS_long.rds")
included_ID = dat$Idnumber |> unique()

sw5 = readRDS("G://users/eileen/Food_Ins/DATA/sw5_demog.rds")
sw5 = sw5[which(sw5$Idnumber %in% included_ID),-1] |> 
  select(Sex, MeFaff04, MatEdu, EqvIncome, ALeSNim2, 
                     PtnrEdu, MatEmploy, MatEthnicity, DeSf12mn)

#for model plots
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 
```

```{r summary demogs}
grouptables = sw5 |> group_by(Sex) |> 
  dfSummary(round.digits = 3,
  valid.col = F, varnumbers = F, labels.col = T,
  na.col = F, graph.magnif = 0.8, style= "grid", headings = F, plain.ascii = F)
```

<details>
<summary><b>Descriptives: Males</b></summary>

```{r}
print(grouptables[[1]], max.tbl.height = 300, method = "render")
```

</details>
\
\
<details>
<summary><b>Descriptives: Females</b></summary>

```{r}
print(grouptables[[2]], max.tbl.height = 300, method = "render")
```

</details>
\

## Group differences in categorical variables

```{r}
MeFaff04 = dat |> filter(sweep == "De") |>
  summarise(Var = "MeFaff04",
            X = chisq.test(Sex, MeFaff04)$statistic,
            df = chisq.test(Sex, MeFaff04)$parameter,
            p = chisq.test(Sex, MeFaff04)$p.value)

MeFaff3lvl = dat |> filter(sweep == "De") |>
  summarise(Var = "MeFaff3lvl",
            X = chisq.test(Sex, MeFaff3lvl)$statistic,
            df = chisq.test(Sex, MeFaff3lvl)$parameter,
            p = chisq.test(Sex, MeFaff3lvl)$p.value)

Food = dat |> filter(sweep == "De") |>
  summarise(Var = "Food",
            X = chisq.test(Sex, Food)$statistic,
            df = chisq.test(Sex, Food)$parameter,
            p = chisq.test(Sex, Food)$p.value)
            
Medu = dat |> filter(sweep == "De") |>
  summarise(Var = "DeMedu03",
            X = chisq.test(Sex, DeMedu03)$statistic,
            df = chisq.test(Sex, DeMedu03)$parameter,
            p = chisq.test(Sex, DeMedu03)$p.value)

Eqv5 = dat |> filter(sweep == "De") |>
  summarise(Var = "DeEqv5",
            X = chisq.test(Sex, DeEqv5)$statistic,
            df = chisq.test(Sex, DeEqv5)$parameter,
            p = chisq.test(Sex, DeEqv5)$p.value)
            
SIMD = dat |> filter(sweep == "De") |>
  summarise(Var = "SIMD",
            X = chisq.test(Sex, ALeSNim2)$statistic,
            df = chisq.test(Sex, ALeSNim2)$parameter,
            p = chisq.test(Sex, ALeSNim2)$p.value)

rbind(MeFaff04, MeFaff3lvl, Food, Medu, Eqv5, SIMD) |> 
  kbl() |> kable_styling(full_width = F)   
```

# Age-only trajectories split by sex {.tabset}

## Conduct problems

```{r}
options(digits = 3)

dat %>% group_by(across(sweep)) %>%
  summarise(Age = mean(Age, na.rm = T),
            t = t.test(Dsdco1 ~ Sex)$statistic,
            df = t.test(Dsdco1 ~ Sex)$parameter,
            CI_low = t.test(Dsdco1 ~ Sex)$conf.int[1] %>% round(2),
            CI_high = t.test(Dsdco1 ~ Sex)$conf.int[2] %>% round(2),
            p = t.test(Dsdco1 ~ Sex)$p.value,
            meanM = t.test(Dsdco1 ~ Sex)$estimate[1],
            meanF = t.test(Dsdco1 ~ Sex)$estimate[2]
) %>% kbl() %>% kable_styling(full_width = F)
```

Original data, split by sex.

```{r}
male = dat %>% filter(Sex=="M") %>%
          group_by(across(sweep)) %>%
          summarise(Age = mean(Age, na.rm = T),
                    Phenotype = mean(Dsdco1, na.rm = T),
                    SD = sd(Dsdco1, na.rm = T),
                    n = sum(!is.na(Dsdco1))) %>%
          mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
                 lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ),
                 Sex = "M")

female = dat %>% filter(Sex=="F") %>%
          group_by(across(sweep)) %>%
          summarise(Age = mean(Age, na.rm = T),
                    Phenotype = mean(Dsdco1, na.rm = T),
                    SD = sd(Dsdco1, na.rm = T),
                    n = sum(!is.na(Dsdco1))) %>%
          mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
                 lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ),
                 Sex = "F")

df.plot = rbind(male, female)

plot = ggplot() +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype, shape = Sex))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype, linetype = Sex)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper, group = Sex)) +
  xlab("Age") + ylab("SDQ Conduct")

plot
```

Quadratic ~~Cubic~~ model with age*sex interactions.

```{r}
fit = lmer(Dsdco1 ~ age.cent*Sex + I(age.cent^2)*Sex + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```


```{r results='asis'}
emm = emmeans(fit, specs = ~ age.cent*Sex + I(age.cent^2)*Sex,
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
traj.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = Sex),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = Sex,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Conduct")

traj.plot
```


## Emotional problems

```{r}
options(digits = 3)

dat %>% group_by(across(sweep)) %>%
  summarise(Age = mean(Age, na.rm = T),
            t = t.test(Dsdem1 ~ Sex)$statistic,
            df = t.test(Dsdem1 ~ Sex)$parameter,
            CI_low = t.test(Dsdem1 ~ Sex)$conf.int[1] %>% round(2),
            CI_high = t.test(Dsdem1 ~ Sex)$conf.int[2] %>% round(2),
            p = t.test(Dsdem1 ~ Sex)$p.value,
            meanM = t.test(Dsdem1 ~ Sex)$estimate[1],
            meanF = t.test(Dsdem1 ~ Sex)$estimate[2]
) %>% kbl() %>% kable_styling(full_width = F)
```

Original data, split by sex.

```{r}
male = dat %>% filter(Sex=="M") %>%
          group_by(across(sweep)) %>%
          summarise(Age = mean(Age, na.rm = T),
                    Phenotype = mean(Dsdem1, na.rm = T),
                    SD = sd(Dsdem1, na.rm = T),
                    n = sum(!is.na(Dsdem1))) %>%
          mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
                 lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ),
                 Sex = "M")

female = dat %>% filter(Sex=="F") %>%
          group_by(across(sweep)) %>%
          summarise(Age = mean(Age, na.rm = T),
                    Phenotype = mean(Dsdem1, na.rm = T),
                    SD = sd(Dsdem1, na.rm = T),
                    n = sum(!is.na(Dsdem1))) %>%
          mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
                 lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ),
                 Sex = "F")

df.plot = rbind(male, female)

plot = ggplot() +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype, shape = Sex))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype, linetype = Sex)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper, group = Sex)) +
  xlab("Age") + ylab("SDQ Emotional")

plot
```

Cubic model with age*sex interactions.

```{r}
fit = lmer(Dsdem1 ~ age.cent*Sex + I(age.cent^2)*Sex + I(age.cent^3)*Sex + (1 + age.cent|Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```


```{r results='asis'}
emm = emmeans(fit, specs = ~ age.cent*Sex + I(age.cent^2)*Sex + I(age.cent^3)*Sex,
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
traj.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = Sex),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = Sex,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Emotional")

traj.plot
```


## Hyperactivity

```{r}
options(digits = 3)

dat %>% group_by(across(sweep)) %>%
  summarise(Age = mean(Age, na.rm = T),
            t = t.test(Dsdhy1 ~ Sex)$statistic,
            df = t.test(Dsdhy1 ~ Sex)$parameter,
            CI_low = t.test(Dsdhy1 ~ Sex)$conf.int[1] %>% round(2),
            CI_high = t.test(Dsdhy1 ~ Sex)$conf.int[2] %>% round(2),
            p = t.test(Dsdhy1 ~ Sex)$p.value,
            meanM = t.test(Dsdhy1 ~ Sex)$estimate[1],
            meanF = t.test(Dsdhy1 ~ Sex)$estimate[2]
) %>% kbl() %>% kable_styling(full_width = F)
```

Original data, split by sex.

```{r}
male = dat %>% filter(Sex=="M") %>%
          group_by(across(sweep)) %>%
          summarise(Age = mean(Age, na.rm = T),
                    Phenotype = mean(Dsdhy1, na.rm = T),
                    SD = sd(Dsdhy1, na.rm = T),
                    n = sum(!is.na(Dsdhy1))) %>%
          mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
                 lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ),
                 Sex = "M")

female = dat %>% filter(Sex=="F") %>%
          group_by(across(sweep)) %>%
          summarise(Age = mean(Age, na.rm = T),
                    Phenotype = mean(Dsdhy1, na.rm = T),
                    SD = sd(Dsdhy1, na.rm = T),
                    n = sum(!is.na(Dsdhy1))) %>%
          mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
                 lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ),
                 Sex = "F")

df.plot = rbind(male, female)

plot = ggplot() +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype, shape = Sex))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype, linetype = Sex)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper, group = Sex)) +
  xlab("Age") + ylab("SDQ Hyperactivity")

plot
```

Quadratic model with age*sex interactions.

```{r}
fit = lmer(Dsdhy1 ~ age.cent*Sex + I(age.cent^2)*Sex + (1 + age.cent|Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```


```{r results='asis'}
emm = emmeans(fit, specs = ~ age.cent*Sex + I(age.cent^2)*Sex,
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
traj.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = Sex),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = Sex,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Hyperactivity")

traj.plot
```

## Peer problems

```{r}
options(digits = 3)

dat %>% group_by(across(sweep)) %>%
  summarise(Age = mean(Age, na.rm = T),
            t = t.test(Dsdpr1 ~ Sex)$statistic,
            df = t.test(Dsdpr1 ~ Sex)$parameter,
            CI_low = t.test(Dsdpr1 ~ Sex)$conf.int[1] %>% round(2),
            CI_high = t.test(Dsdpr1 ~ Sex)$conf.int[2] %>% round(2),
            p = t.test(Dsdpr1 ~ Sex)$p.value,
            meanM = t.test(Dsdpr1 ~ Sex)$estimate[1],
            meanF = t.test(Dsdpr1 ~ Sex)$estimate[2]
) %>% kbl() %>% kable_styling(full_width = F)

```

Original data, split by sex.

```{r}
male = dat %>% filter(Sex=="M") %>%
          group_by(across(sweep)) %>%
          summarise(Age = mean(Age, na.rm = T),
                    Phenotype = mean(Dsdpr1, na.rm = T),
                    SD = sd(Dsdpr1, na.rm = T),
                    n = sum(!is.na(Dsdpr1))) %>%
          mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
                 lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ),
                 Sex = "M")

female = dat %>% filter(Sex=="F") %>%
          group_by(across(sweep)) %>%
          summarise(Age = mean(Age, na.rm = T),
                    Phenotype = mean(Dsdpr1, na.rm = T),
                    SD = sd(Dsdpr1, na.rm = T),
                    n = sum(!is.na(Dsdpr1))) %>%
          mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
                 lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ),
                 Sex = "F")

df.plot = rbind(male, female)

plot = ggplot() +
  geom_point(data = df.plot, aes(x=Age, y=Phenotype, shape = Sex))+
  geom_line(data = df.plot, aes(x=Age, y=Phenotype, linetype = Sex)) +
  geom_errorbar(data = df.plot, aes(x=Age, ymin = lower, ymax = upper, group = Sex)) +
  xlab("Age") + ylab("SDQ Peer Problems")

plot
```

Cubic model with age*sex interactions.

```{r}
fit = lmer(Dsdpr1 ~ age.cent*Sex + I(age.cent^2)*Sex + I(age.cent^3)*Sex + (1 + age.cent|Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))

check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) %>%
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```


```{r results='asis'}
emm = emmeans(fit, specs = ~ age.cent*Sex + I(age.cent^2)*Sex + I(age.cent^3)*Sex,
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) %>% cbind(., age_vals)

#plot overall model 
traj.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = Sex),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = Sex,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  xlab("Age") + ylab("SDQ Peer Problems")

traj.plot
```

# 3-level FI trajectories by sex

## Male only {.tabset}

GUS SDQ scores by sweep, male only. Mean (SD) \

```{r m data summary}
dat = readRDS("G://users/eileen/Food_Ins/DATA/wt_GUS_long.rds")
dat = dat |> filter(Sex=="M")

dat |> group_by(sweep) |> summarise(
  N = n(),
  Age = paste0(round(mean(Age), 2), " (", round(sd(Age), 2), ")"),
  Conduct = paste0(round(mean(Dsdco1), 2), " (", round(sd(Dsdco1), 2), ")"),
  Emotional = paste0(round(mean(Dsdem1), 2), " (", round(sd(Dsdem1), 2), ")"),
  Hyperactivity = paste0(round(mean(Dsdhy1), 2), " (", round(sd(Dsdhy1), 2), ")"),
  Peer_Problem = paste0(round(mean(Dsdpr1), 2), " (", round(sd(Dsdpr1), 2), ")")
) |> kbl() |> kable_styling()
```


```{r m df.plot}
sdq = c("Dsdco1", "Dsdem1", "Dsdhy1", "Dsdpr1")
df.plot = list()

for (phe in sdq) {
    df = dat |>
      group_by(across(sweep)) |>
          summarise(Age = mean(Age, na.rm = T),
                    Phenotype = mean(get(phe), na.rm = T),
                    SD = sd(get(phe), na.rm = T),
                    n = sum(!is.na(get(phe)))) |>
          mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
                 lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))
    df.plot[[phe]] = df
    }    
```

### Conduct problems

```{r m binary conduct 3}
fit = lmer(Dsdco1 ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) |>
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r m conduct plot 3}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) |> cbind(age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot$Dsdco1, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot$Dsdco1, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot$Dsdco1, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Conduct")

emmeans.plot
```

### Emotional problems

```{r m binary emot 3}
fit = lmer(Dsdem1 ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) |>
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r m emot plot 3}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) |> cbind(age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot$Dsdem1, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot$Dsdem1, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot$Dsdem1, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Emotion")

emmeans.plot
```

### Hyperactivity

```{r m binary hyperactivity 3}
fit = lmer(Dsdhy1 ~ age.cent*MeFaff3lvl + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) |>
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r m hyper plot 3}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) |> cbind(age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot$Dsdhy1, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot$Dsdhy1, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot$Dsdhy1, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Hyperactivity")

emmeans.plot
```

### Peer problems

```{r m binary peer 3}
fit = lmer(Dsdpr1 ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) |>
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r m peer plot 3}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) |> cbind(age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot$Dsdpr1, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot$Dsdpr1, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot$Dsdpr1, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Peer Problems")

emmeans.plot
```

## Female only {.tabset}

GUS SDQ scores by sweep, female only. Mean (SD) \

```{r f data summary}
dat = readRDS("G://users/eileen/Food_Ins/DATA/wt_GUS_long.rds")
dat = dat |> filter(Sex=="F")

dat |> group_by(sweep) |> summarise(
  N = n(),
  Age = paste0(round(mean(Age), 2), " (", round(sd(Age), 2), ")"),
  Conduct = paste0(round(mean(Dsdco1), 2), " (", round(sd(Dsdco1), 2), ")"),
  Emotional = paste0(round(mean(Dsdem1), 2), " (", round(sd(Dsdem1), 2), ")"),
  Hyperactivity = paste0(round(mean(Dsdhy1), 2), " (", round(sd(Dsdhy1), 2), ")"),
  Peer_Problem = paste0(round(mean(Dsdpr1), 2), " (", round(sd(Dsdpr1), 2), ")")
) |> kbl() |> kable_styling()
```



```{r f df.plot}
sdq = c("Dsdco1", "Dsdem1", "Dsdhy1", "Dsdpr1")
df.plot = list()

for (phe in sdq) {
    df = dat |>
      group_by(across(sweep)) |>
          summarise(Age = mean(Age, na.rm = T),
                    Phenotype = mean(get(phe), na.rm = T),
                    SD = sd(get(phe), na.rm = T),
                    n = sum(!is.na(get(phe)))) |>
          mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
                 lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))
    df.plot[[phe]] = df
    }    
```

### Conduct problems

```{r f binary conduct 3}
fit = lmer(Dsdco1 ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) |>
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r f conduct plot 3}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) |> cbind(age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot$Dsdco1, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot$Dsdco1, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot$Dsdco1, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Conduct")

emmeans.plot
```

### Emotional problems

```{r f binary emot 3}
fit = lmer(Dsdem1 ~ age.cent*MeFaff3lvl + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) |>
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r f emot plot 3}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) |> cbind(age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot$Dsdem1, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot$Dsdem1, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot$Dsdem1, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Emotion")

emmeans.plot
```

### Hyperactivity

```{r f binary hyperactivity 3}
fit = lmer(Dsdhy1 ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) |>
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r f hyper plot 3}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) |> cbind(age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot$Dsdhy1, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot$Dsdhy1, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot$Dsdhy1, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Hyperactivity")

emmeans.plot
```

### Peer problems

```{r f binary peer 3}
fit = lmer(Dsdpr1 ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + I(age.cent^4)*MeFaff3lvl + (1 + age.cent |Idnumber),
                 REML = TRUE ,
                 data = dat ,
                 weights = Djwtbth2a,
                 control = lmerControl(optimizer="bobyqa",
                                      optCtrl=list(maxfun=2e5)))
check_fit(fit)
kbl(t(summary(fit)[["AICtab"]])) |>
  kable_styling(full_width = F)
sjPlot::tab_model(fit)
```

```{r f peer plot 3}
age_vals = seq(min(dat$Age), max(dat$Age), 0.5) #list of ages to make scores for
age_cent = age_vals - mean(dat$Age, na.rm = T) #mean center to fit with the model
at_vals = list(age.cent = age_cent) 

emm = emmeans(fit, specs = ~ age.cent*MeFaff3lvl + I(age.cent^2)*MeFaff3lvl + I(age.cent^3)*MeFaff3lvl + I(age.cent^4)*MeFaff3lvl, 
              at = at_vals, 
              lmer.df = "satterthwaite")

# add a column with the original age values
pred = as.data.frame(summary(emm)) |> cbind(age_vals)

#plot overall model 
emmeans.plot = ggplot() + 
  geom_line(data = pred,
            aes(x = age_vals, y = emmean, colour = MeFaff3lvl),
            linewidth = 1.5, na.rm = T) + 
  geom_ribbon(data = pred,
              aes(x = age_vals, y = emmean, fill = MeFaff3lvl,
                  ymin = lower.CL, ymax = upper.CL),
              alpha = 0.2, na.rm = T) +
  geom_point(data = df.plot$Dsdpr1, aes(x=Age, y=Phenotype))+
  geom_line(data = df.plot$Dsdpr1, aes(x=Age, y=Phenotype)) +
  geom_errorbar(data = df.plot$Dsdpr1, aes(x=Age, ymin = lower, ymax = upper)) +
  xlab("Age") + ylab("SDQ Peer Problems")

emmeans.plot
```